\begin{center}
\normalsize \begin{center}\normalsize SATURDAYS OF LENT\\
\end{center}
\end{center}

\begin{flushleft}\normalsize LAUDS\\\end{flushleft}

\hangindent=\parindent \small{INVITATORY}
\begin{center}
\textit{The man of God welcomes the light.\\}
\textit{- So that all may see that his deeds are true.\\}
\end{center}

\hangindent=\parindent \small READING
\begin{description}[labelindent=\parindent, leftmargin=*]
\item [Saturday after Ash Wednesday \& Weeks 1-4:]     Is 1:16-18 \textbf{    }
\item [Week 5:]     Is 65:1b-3a \textbf{    }
\end{description}

\hangindent=\parindent \small BENEDICTUS
\begin{description}[labelindent=\parindent, noitemsep, leftmargin=*]
\item [Saturday after Ash Wednesday:] 	Store up for yourselves treasures in heaven where neither rust nor moth can destroy.
\item [Week 1:] 	If you want to be true children of your heavenly Father, then you must pray for those who persecute you and speak all kinds of evil against you, says the Lord.
\item [Week 2:] 	Father, I have sinned against heaven and against you; I no longer deserve to be called your son; treat me as one of your servants.
\item [Week 3:] 	The tax collector stood far away and would not even raise his eyes to heaven. He struck his breast and prayed: God, have mercy on me, a sinner.
\item [Week 4:] 	Never before has anyone spoken like this man.
\item [Week 5:] 	Jesus died to gather into one family all the scattered children of God.
\end{description}

\hangindent=\parindent \small PRAYERS
\begin{description}[labelindent=\parindent, noitemsep, leftmargin=*]
\item [Saturday after Ash Wednesday:] 	Almighty ever-living God, look with compassion on our weakness and ensure us your protection by stretching forth the right hand of your majesty. Through our Lord Jesus Christ, your Son, who lives and reigns with you in the unity of the Holy Spirit, one God, for ever and ever.
\item [Week 1:] 	Turn our hearts to you, eternal Father, and grant that, seeking always the one thing necessary and carrying out works of charity, we may be dedicated to your worship. Through our Lord Jesus Christ, your Son, who lives and reigns with you in the unity of the Holy Spirit, one God, for ever and ever.
\item [Week 2:] 	O God, who grant us y glorious healing remedies while still on earth to be partakers of the things of heaven, guide us, we pray, through this present life and bring us to that lifht in which you dwell. Through our Lord Jesus Christ, your Son, who lives and reigns with you in the unity of the Holy Spirit, one God, for ever and ever.
\item [Week 3:] 	Rejoicing in this annual celbration of our Lenten observance, we pray, O Lord, that, with our hearts set on the paschal mysteries, we may be gladdned by their full effects. Through our Lord Jesus Christ, your Son, who lives and reigns with you in the unity of the Holy Spirit, one God, for ever and ever.
\item [Week 4:] 	May the working of your mercy, O Lord, we pray, direct our hearts aright, for without your grace we cannot find favor in your sight. Through our Lord Jesus Christ, your Son, who lives and reigns with you in the unity of the Holy Spirit, one God, for ever and ever.
\item [Week 5:] 	O God, who have made all those reborn in Christ a chosen race and a royal priesthood, grant us, we pray, the grace to will and to do what you command, that the people called to eternal life may be one in faith of their hearts and the homage of their deeds. Through our Lord Jesus Christ, your Son, who lives and reigns with you in the unity of the Holy Spirit, one God, for ever and ever.
\end{description}

\begin{flushleft}\normalsize SEXT\\\end{flushleft}

\hangindent=\parindent \small READING
\begin{description}[labelindent=\parindent, leftmargin=*]
\item [Saturday after Ash Wednesday \& Weeks 1-4:]     Is 44:21-22 \textbf{    }
\item [Week 5:]     1 Jn 2:1b-2 \textbf{    }
\end{description}


\begin{center}
\textit{Response same as Sunday\\
-the rest}
\end{center}

