\begin{center}
\normalsize WEDNESDAYS OF LENT
\end{center}

\begin{flushleft}\normalsize{\uppercase{LAUDS\\}}\end{flushleft}
\small{\uppercase{INVITATORY:}}\normalsize
\begin{center}
\textit{Turn back to the Lord and do penance.\\}
\textit{- Be renewed in heart and spirit.\\}
\end{center}
\noindent\small READING
\begin{description}[labelindent=\parindent, leftmargin=*]
\item [Ash Wednesday \& Weeks 1-4:]     Deut 7:6, 8-9 \textbf{    For you are a people holy to the LORD, your God; the LORD, your God, has chosen you from all the peoples on the face of the earth to be a people specially his own. It was because the LORD loved you and because of his fidelity to the oath he had sworn to your ancestors, that the LORD brought you out with a strong hand and redeemed you from the house of slavery, from the hand of Pharaoh, king of Egypt. Know, then, that the LORD, your God, is God: the faithful God who keeps covenant mercy to the thousandth generation toward those who love him and keep his commandments.\\}
\item [Week 5:]    Is 50:4b-7    \textbf{Morning after morning\\
he wakens my ear to hear as disciples do;\\
The Lord GOD opened my ear;\\
I did not refuse,\\
did not turn away.\\
I gave my back to those who beat me,\\
my cheeks to those who tore out my beard;\\
My face I did not hide\\
from insults and spitting.\\
The Lord GOD is my help,\\
therefore I am not disgraced;\\
Therefore I have set my face like flint,\\
knowing that I shall not be put to shame.}
\end{description}

\noindent\small BENEDICTUS
\begin{description}[labelindent=\parindent, leftmargin=*]
\item [Ash Wednesday:] 	When you fast, do not put on a gloomy face, like the hypocrites.
\item [Week 1:] 	This evil and faithless generation asks for a sign, but no sign will be given it except the sign of the prophet Jonah.
\item [Week 2:] 	The Son of Man did not come to be served but to serve, and to give his life as a ransom for many.
\item [Week 3:] 	The Lord said: Do not think that I have come to abolish the law and the prophets; I have come not to abolish but to fulfill them.
\item [Week 4:] 	Whoever hears my words, says the Lord, and believes in him who sent me, has eternal life.
\item [Week 5:] 	If you are faithful to my teaching, says the Lord, you will indeed be my disciples. You will know the truth and the truth will make you free.
\end{description}

\noindent\small PRAYERS
\begin{description}[labelindent=\parindent, leftmargin=*]
\item [Ash Wednesday:] 	Grant, O Lord, that we may begin with holy fasting this campaign of Christian service, so that, as we take up battle against spiritual evils, we may be armed with weapons of self-restraint. Through our Lord Jesus Christ, your Son, who lives and reigns with you in the unity of the Holy Spirit, one God, for ever and ever.
\item [Week 1:] 	Look kindly, Lord, we pray, on the devotion of your people, that those who by self-denial are restrained in body may by the fruit of good works be renewed in mind. Through our Lord Jesus Christ, your Son, who lives and reigns with you in the unity of the Holy Spirit, one God, for ever and ever.
\item [Week 2:] 	Keep your family, O Lord, schooled always in good works, and so comfort them with your protection here as to lead them graciously to gifts on high. Through our Lord Jesus Christ, your Son, who lives and reigns with you in the unity of the Holy Spirit, one God, for ever and ever.
\item [Week 3:] 	Grant, we pray, O Lord, that, schooled throuh Lenten observance and nourished by your word, through holy restraint we may be devoted to you with all our heart and be ever united in prayer. Through our Lord Jesus Christ, your Son, who lives and reigns with you in the unity of the Holy Spirit, one God, for ever and ever.
\item [Week 4:] 	O God, who reward the merits of the just and offer pardon to sinners who do penance, have mercy, we pray, on those who call upon you, that the admission of our guilt may serve to obtain your pardon for our sins. Through our Lord Jesus Christ, your Son, who lives and reigns with you in the unity of the Holy Spirit, one God, for ever and ever.
\item [Week 5:] 	Enlighten, O God of compassion, the hearts of your children, sanctified by penance, and in your kindness grant those you stir to a sense of devotion a gracious hearing when they cry out to you. Through our Lord Jesus Christ, your Son, who lives and reigns with you in the unity of the Holy Spirit, one God, for ever and ever.
\end{description}

\begin{flushleft}\normalsize{\uppercase{SEXT\\}}\end{flushleft}
\noindent\small READING
\begin{description}[labelindent=\parindent, leftmargin=*]
\item [Ash Wednesday \& Weeks 1-4:]     Zech 1:3b-4b \textbf{    \\}
\item [Week 5:]    Rom 15:3   \textbf{} 
\end{description}

\begin{center}\textsc{Response same as Sunday}\end{center}

\begin{flushleft}\normalsize{\uppercase{VESPERS\\}}\end{flushleft}
\small{\uppercase{HYMN} p. \pageref{lent:firstHymn}-\pageref{lent:lastHymn}\\}
\noindent\small READING
\begin{description}[labelindent=\parindent, leftmargin=*]
\item [Ash Wednesday \& Weeks 1-4:]     Phil 2:12b-15a \textbf{\\}
\item [Week 5:]    Eph 4:32-5:2  \textbf{}  
\end{description}

\noindent\small MAGNIFICAT
\begin{description}[labelindent=\parindent, leftmargin=*]
\item [Ash Wednesday:] 	When you give alms, do not let your left hand know what your right hand is doing.
\item [Week 1:] 	As Jonah was three days and three nights in the belly of the whale, so will the Son of Man spend three days and three nights in the heart of the earth.
\item [Week 2:] 	The Son of Man will be handed over to the Gentiles to be mocked, scourged and crucified; and on the third day he will rise again.
\item [Week 3:] 	The one who obeys God's law and teaches others to do so will be great in the kingdom of heaven.
\item [Week 4:] 	By myself, says the Lord, I can do nothing. I judge as I am told to judge, and my sentence is just.
\item [Week 5:] 	Why are you bent on killing me, when I have told you the truth?
\end{description}
