\begin{center}
\normalsize \begin{center}\normalsize ASCENSION THURSDAY\\
\end{center}
\footnotesize SOLEMNITY\\
\end{center}

\hangindent=\parindent \small{INVITATORY}
\begin{center}
\textit{Alleluia, come, let us worship Christ the Lord as he ascends into heaven, alleluia.\\}
\end{center}

\noindent\small{\uppercase{Hymn}}\normalsize\label{ascension:hymn}
\begin{cverse}
Let the earth rejoice and sing, alleluia!\\
At the triumph of our King, alleluia!\\
He ascends from mortal sight, alleluia!\\
Reigns now at our Father's right, alleluia!\\!

He who died upon a tree, alleluia!\\
Now shall reign eternally, alleluia!\\
He who saved our fallen race, alleluia!\\
Takes in heav'n his rightful place, alleluia!\\!

Jesus, Lord, all hail to thee, alleluia!\\
On this day of victory, alleluia!\\
Thou didst shatter Satan's might, alleluia!\\
Rising glorious from the fight, alleluia!\\!

Jesus, Victor, hear our prayer, alleluia!\\
In thy triumph let us share, alleluia!\\
Lift our minds and hearts above, alleluia!\\
Strengthen all men in thy love, alleluia!\\!

While in heaven thou dost gaze, alleluia!\\
On thy Church who sings thy praise, alleluia!\\
Fasten all our hope in thee, alleluia!\\
Till thy face unveiled we see, alleluia! Amen.\\!
\end{cverse}

\begin{flushleft}\normalsize FIRST VESPERS\\\end{flushleft}

\hangindent=\parindent \small{PSALMODY:}\\
\hangindent=\parindent  PS 112 -- PS 116 -- PS 23 ant. O.T. I -- NT 10\vspace{0.5em}

\hangindent=\parindent \small{READING}    Eph 2:4-6 \textbf{   \\}

\hangindent=\parindent \small{MAGNIFICAT 	Father, I have made known your name to the men you have given me; now I am praying for them and not for the world, because I am coming to you, alleluia.\\}

\hangindent=\parindent \small{PRAYER 	}

\begin{flushleft}\normalsize VIGILS\\\end{flushleft}

\hangindent=\parindent \small{PSALMODY:}\\
\hangindent=\parindent  PS 67 -- OT 31 -- OT 42 -- OT 44\vspace{0.5em}

\begin{flushleft}\normalsize LAUDS\\\end{flushleft}

\hangindent=\parindent \small{PSALMODY:}\\
\hangindent=\parindent  PS 8 -- PS 62 ant. O.T. I + alleluia -- PS 96 -- OT 19 ant. Adv. -- PS 107 ant. Lent\vspace{0.5em}

\hangindent=\parindent \small{READING}    Heb 10:12-14 \textbf{   \\}

\hangindent=\parindent \small{BENEDICTUS 	I am ascending to my Father and your Father, to my God and your God, alleluia.\\}

\hangindent=\parindent \small{PRAYER 	}

\begin{flushleft}\normalsize SEXT\\\end{flushleft}

\hangindent=\parindent \small{PSALMODY:}\\
\hangindent=\parindent  PS 118 XI--XII -- PS 10 -- PS 18\vspace{0.5em}

\hangindent=\parindent \small{READING}    Heb 8:1b-3a \textbf{   }

\begin{center}
\textit{The Lord in heaven has prepared a royal throne, alleluia.\\
-Christ has ascended on high, alleluia.}
\end{center}

\begin{flushleft}\normalsize SECOND VESPERS\\\end{flushleft}

HYMN from First Vespers p. \pageref{ascension:hymn}

\hangindent=\parindent \small{PSALMODY:}\\
\hangindent=\parindent  PS 99 -- PS 109 ant. Easter -- PS 46 ant. Lent -- NT 10\vspace{0.5em}

\hangindent=\parindent \small{READING}    1 Pet 3:18, 22 \textbf{   \\}

\hangindent=\parindent \small{MAGNIFICAT 	O Victor King, Lord of power and might, today you have ascended in glory above the heavens. Do not leave us orphans, but send us the Father's promised gift, the Spirit of truth, alleluia.\\}
