\begin{center}\normalsize SUNDAYS OF EASTER\\
\end{center}

\hangindent=\parindent \small{PSALMODY}
\begin{center}
\begin{tabular}{ l l }
1st Sunday &  Week I Easter Sunday - The Resurrection of the Lord\\
2nd Sunday &  Week II Divine Mercy Sunday\\
3rd Sunday &  Week III\\
4th Sunday &  Week IV\\
5th Sunday &  Week I\\
6th Sunday &  Week II\\
7th Sunday &  Week III\\
\end{tabular}
\end{center}		

\begin{flushleft}\normalsize FIRST VESPERS\\\end{flushleft}

\hangindent=\parindent \small{\uppercase{HYMN} p. \pageref{easter:firstHymn}-\pageref{easter:lastHymn}\\}

\hangindent=\parindent \small{\uppercase{READING}}    1 Pet 2:9-10 \textbf{   \\}

\hangindent=\parindent \small MAGNIFICAT
\begin{description}[labelindent=\parindent, leftmargin=*]
\item [Divine Mercy Sunday:] 	After eight days, although the doors were locked, the Lord came among them and said: Peace be with you, alleluia.
\item [3rd Week:] 	Stay with us, Lord, for evening draws near and daylight is fading, alleluia.
\item [4th Week:] 	I am the gate, says the Lord; whoever enters through me shall be saved and find pasture, alleluia.
\item [5th Week:] 	I am the way, the truth and the life; no one comes to the Father except through me, alleluia.
\item [6th Week:] 	I will ask the Father and he will give you another Paraclete to remain with you for ever, alleluia.
\item [7th Week:] 	I will not leave you orphans; I am going now but I will come back to you and your hearts will rejoice, alleluia.
\end{description}

\hangindent=\parindent \small PRAYER
\begin{description}[labelindent=\parindent, leftmargin=*]
\item [Divine Mercy Sunday:] 	
\item [3rd Week:] 	
\item [4th Week:] 	
\item [5th Week:] 	
\item [6th Week:] 	
\item [7th Week:] 
\end{description}

\begin{flushleft}\normalsize LAUDS\\\end{flushleft}

\hangindent=\parindent \small{INVITATORY}
\begin{center}
\end{center}Easter Sunday \& Divine Mercy Sunday:\begin{center}\textit{		The Lord is risen, alleluia.\\}
\end{center}3rd, 4th, 5th, \& 7th Sunday:\begin{center}\textit{	My whole body rejoices, alleluia.	\\}
\textit{- With all my strength I will praise my God, alleluia.\\}
\end{center}6th Sunday:\begin{center}\textit{		My heart and my flesh, alleluia.\\}
\textit{- Rejoice in the living God, alleluia.\\}
\end{center}

\hangindent=\parindent \small{\uppercase{READING}}    Acts 10:40-43 \textbf{   \\}

\hangindent=\parindent \small BENEDICTUS
\begin{description}[labelindent=\parindent, leftmargin=*]
\item [Easter Sunday:] 	Very early on the morning after the Sabbath, when the sun had just risen, they came to the tomb, alleluia.
\item [Divine Mercy Sunday:] 	With your hand, touch the mark of the nails, doubt no longer, but believe, alleluia.
\item [3rd Sunday:] 		It was ordained that Christ should suffer, and on the third day rise from the dead, alleluia.
\item [4th Sunday:] 		I am the shepherd of the sheep; I am the way, the truth and the life: I know my sheep, and my sheep know me, alleluia.
\item [5th Sunday:] 		Whoever lives in me and I in him will yield much fruit, says the Lord, alleluia.
\item [6th Sunday:] 		As the Father has loved me, so I have loved you; live on in my love, alleluia.
\item [7th Sunday:] 		Father, I have glorified you upon the earth, I have accomplished the work you gave me to do, alleluia.
\end{description}

\hangindent=\parindent \small PRAYER
\begin{description}[labelindent=\parindent, leftmargin=*]
\item [Easter Sunday:] 	O God, who on this day, through your Only Begotten Son, have conquered death and unlocked for us the path to eternity, grant, we pray, that we who keep the solemnity of the Lord's Resurrection may, through the renewal brought by your Spirit, rise up in the light of life. Through our Lord Jesus Christ, your Son, who lives and reigns with you in the unity of the Holy Spirit, one God, for ever and ever.
\item [Divine Mercy Sunday:] 	God of everlasting mercy, who in the very recurrence of the paschal feast kindle the faith of the people you have made your own, increase, e pray, the grace you have bestowed, that all may grasp and rightly understand in what font they have been washed, by whose Spirit they have been reborn, by whose Blood they have been redeemed. Through our Lord Jesus Christ, your Son, who lives and reigns with you in the unity of the Holy Spirit, one God, for ever and ever.
\item [3rd Sunday:] 		
\item [4th Sunday:] 		
\item [5th Sunday:] 		
\item [6th Sunday:] 		
\item [7th Sunday:] 	
\end{description}

\begin{flushleft}\normalsize SEXT\\\end{flushleft}

\hangindent=\parindent \small{\uppercase{READING}}    Eph 2:4-6 \textbf{   \\}

\begin{center}
\end{center}Easter Sunday \& Divine Mercy Sunday:\begin{center}\textit{	This is the day the Lord has made, alleluia.\\
- Let us rejoice and be glad, alleluia.}
\end{center}3rd-7th Sundays:\begin{center}\textit{	The disciples rejoiced, alleluia.\\
- When they saw the risen Lord, alleluia.}
\end{center}

\begin{flushleft}\normalsize SECOND VESPERS\\\end{flushleft}

\hangindent=\parindent \small{\uppercase{HYMN} p. \pageref{easter:firstHymn}-\pageref{easter:lastHymn}\\}

\hangindent=\parindent \small{\uppercase{READING}}    Heb 10:12-14 \textbf{   \\}

\hangindent=\parindent \small MAGNIFICAT
\begin{description}[labelindent=\parindent, leftmargin=*]
\item [Easter Sunday:] 	On the evening of the first day of the week, the disciples were gathered together behind locked doors; suddenly, Jesus stood among them and said: Peace be with you, alleluia.
\item [Divine Mercy Sunday:] 	Because you have seen me, Thomas, you have believed; blessed are they who have not seen me and yet believe, alleluia.
\item [3rd Sunday:] 		Jesus said to his disciples: Bring me some of the fish you have just caught. Simon Peter went aboard and hauled ashore the net, full of large fish, alleluia.
\item [4th Sunday:] 		My sheep will hear my voice. I, their Lord, know them.
\item [5th Sunday:] 		I give you a new commandment: love one another as I have loved you, says the Lord, alleluia.
\item [6th Sunday:] 		If anyone loves me he will keep my word, and my Father will love him. We will come to him and make our home with him, alleluia.
\item [7th Sunday:] 		I will send you the Spirit of truth who comes from the Father. When the Paraclete comes he will bear witness to me, alleluia.
\end{description}
