\begin{center}\normalsize MAY 31\\
\footnotesize THE VISITATION OF THE BLESSED VIRGIN MARY\\
\footnotesize Feast\\
\footnotesize From the common of The Blessed Virgin Mary, p.     Except:\\
\end{center}

\hangindent=\parindent \small{PRAYER 
Almighty ever-living God,
who, while the Blessed Virgin Mary was carrying your Son in her womb,
inspired her to visit Elizabeth,
grant us, we pray,
that, faithful to the promptings of the Spirit,
we may magnify your greatness
with the Virgin Mary at all times.
Through our Lord Jesus Christ, your Son,
who lives and reigns with you in the unity of the Holy Spirit,
one God, for ever and ever.\\}
 
\begin{flushleft}\normalsize LAUDS\\\end{flushleft}

\hangindent=\parindent \small{INVITATORY}
\begin{center}
\textit{Let us sing to the Lord\\}
\textit{as we celebrate the Visitation of the Blessed Virgin Mary.\\}
\end{center}

\hangindent=\parindent \small{PSALMODY:}\\
\hangindent=\parindent  OT 3\vspace{0.5em}

\hangindent=\parindent \small{READING} Joel 2:27, 3:1 \textbf{You shall know that I am in the midst of Israel,
and that I, the Lord, am your God and there is none else. And my
people shall never again be put to shame. And it shall come to pass
afterward, that I will pour out my spirit on all flesh; your sons and
your daughters shall prophesy.\\}
 
\hangindent=\parindent \small{BENEDICTUS  When Elizabeth heard Mary’s greeting, she cried out
and said: Who am I that the mother of my Lord should come to me,
alleluia.\\}
 
\hangindent=\parindent \small{PRAYER 
Eternal Father, you inspired the Virgin Mary, mother of your
Son, to visit Elizabeth and assist her in her need. Keep us open to the
working of your Spirit, and with Mary may we praise you for ever.
We ask this…\\}
 
\begin{flushleft}\normalsize SEXT\\\end{flushleft}

\hangindent=\parindent \small{READING} Wis 7:27-28 \textbf{Though wisdom is but one, she can do all
things, and while remaining in herself, she renews all things; in
every generation she passes into holy souls and makes them friends
of God, and prophets; for God loves nothing so much as the man
who lives with wisdom.}
 
\begin{center}
\textit{Blessed is the womb of the Virgin Mary, alleluia.\\
- Who bore the Son of the eternal Father, alleluia.}
\end{center}

\begin{flushleft}\normalsize VESPERS\\\end{flushleft}

\hangindent=\parindent \small{READING} 1 Pet 5:5-7 \textbf{Clothe yourselves, all of you, with humility
toward one another, for “God opposes the proud, but gives grace to
the humble.” Humble yourselves therefore under the mighty hand
of God, that in due time he may exalt you. Cast all your anxieties
on him, for he cares about you.\\}
 
\hangindent=\parindent \small{MAGNIFICAT  All generations will call me blessed; the Lord has looked
with favor on his lowly servant (alleluia).\\}
 

