Psalm 1(1) Beatus vir qui non abiit

1 Happy indeed is the man
who follows not the counsel of the wicked,
nor lingers in the way of sinners
nor sits in the company of scorners,
2 but whose delight is the law of the Lord
and who ponders his law day and night.

3 He is like a tree that is planted
beside the flowing waters,
that yields its fruit in due season
and whose leaves shall never fade;
and all that he does shall prosper.
4 Not so are the wicked, not so!

For they like winnowed chaff
shall be driven away by the wind.
5 When the wicked are judged they shall not stand,
nor find room among those who are just;
6 for the Lord guards the way of the just
but the way of the wicked leads to doom.

Psalm 2(2) Quare fremuerunt gentes

1 Why this tumult among nations,
among peoples this useless murmuring?
2 They arise, the kings of the earth,
princes plot against the Lord and his Anointed.
3 "Come, let us break their fetters,
come, let us cast off their yoke."

4 He who sits in the heavens laughs;
the Lord is laughing them to scorn.
5 Then he will speak in his anger,
his rage will strike them with terror.
6 "It is I who have set up my king on Zion,
my holy mountain."

7 (I will announce the decree of the Lord:)

The Lord said to me: "You are my Son.
It is I who have begotten you this day.
8 Ask and I will shall bequeath you the nations,
put the ends of the earth in your possession.
9 With a rod of iron you will break them,
shatter them like a potter's jar."

10 Now, O kings, understand,
take warning, rulers of the earth;
11 serve the Lord with awe
and trembling, pay him your homage
12 lest he be angry and you perish;
for suddenly his anger will blaze.

Blessed are they who put their trust in God.


Psalm 3(3) Domine, quid multiplicati

.2 How many are my foes, O Lord!
How many are rising up against me!
.3 How many are saying about me:
"There is no help for him in God."

.4 But you, Lord, are a shield about me,
my glory, who lift up my head.
.5 I cry aloud to the Lord.
He answers from his holy mountain.

.6 I lie down to rest, and I sleep.
I wake, for the Lord upholds me.
.7 I will not fear even thousands of people
who are ranged on every side against me.

.8 Arise, Lord; save me, my God,
you who strike my foes on the mouth,
you who break the teeth of the wicked!
.9 O Lord of salvation, bless your people!


Psalm 4(4) Cum invocarem

.2 When I call, answer me, O God of justice;
from anguish you released me, have mercy and hear me!

.3 O men, how long will your hearts be closed,
will you love what is futile and seek what is false?

.4 It is the Lord who grants favors to those whom he loves;
the Lord hears me whenever I call him.

.5 Fear him; do not sin: ponder on your bed and be still
.6 Make justice your sacrifice, and trust in the Lord.

.7 "What can bring us happiness?" many say.
Lift up the light of your face on us, O Lord.

.8 You have put into my heart a greater joy
than they have from abundance of corn and new wine.

.9 I will lie down in peace and sleep comes at once
for you alone, Lord, make me dwell in safety.


Psalm 5(5) Verba mea auribus

.2 To my words give ear, O Lord,
give heed to my groaning.
.3 Attend to the sound of my cries,
my King and my God.

/.4 It is you whom I invoke, O Lord.
In the morning you hear me;
in the morning I offer you my prayer,
watching and waiting.

.5 You are no God who loves evil;
no sinner is your guest.
.6 The boastful shall not stand their ground
before your face.

.7 You hate all who do evil;
you destroy all who lie.
The deceitful and bloodthirsty man
the Lord detests.

.8 But I through the greatness of your love
have access to your house.
I bow down before your holy temple,
filled with awe.

.9 Lead me, Lord, in your justice,
because of those who lie in wait;
make clear your way before me.

.10 No truth can be found in their mouths,
their heart is all mischief,
their throat a wide-open grave,
all honey their speech.

.11 Declare them guilty, O God.
Let them fail in their designs.
Drive them out for their many offenses,
for they have defied you.

.12 All those you protect shall be glad
and ring out their joy.
You shelter them; in you they rejoice,
those who love your name.

.13 It is you who bless the just man
you surround him with favor as with a shield.


Psalm 6(6) Domine, ne in furore

.2 Lord, do not reprove me in your anger;
punish me not in your rage.
.3 Have mercy on me, Lord, I have no strength;
Lord, heal me, my body is racked;
.4 my soul is racked with pain.

But you, O Lord...how long?
.5 Return, Lord, rescue my soul.
Save me in your merciful love;
.6 for in death no one remembers you;
from the grave, who can give you praise?

.7 I am exhausted with my groaning;
every night I drench my pillow with tears;
I bedew my bed with weeping.
.8 My eye wastes away with grief;
I have grown old surrounded by my foes.

.9 Leave me, all you who do evil;
for the Lord has heard my weeping.
.10 The Lord has heard my plea;
The Lord will accept my prayer.
.11 All my foes will retire in confusion,
foiled and suddenly confounded.


Psalm 7(7) Domine, Deus meus

.2 Lord God, I take refuge in you.
From my pursuer save me and rescue me,
.3 lest he tear me to pieces like a lion
and drag me off with no one to rescue me.

.4 Lord God, if my hands have done wrong,
.5 if I have paid back evil for good,
I who saved my unjust oppressor:
.6 then let my foe pursue me and seize me,
let him trample my life to the ground
and lay my soul in the dust.

* * *

.7 Lord, rise up in your anger,
rise against the fury of my foes;
my God, awake! You will give judgment.
.8 Let the company of nations gather round you,
taking your seat above them on high.
.9 (The Lord is judge of the peoples.)

Give judgment for me, Lord; I am just
and innocent of heart.
.10 Put an end to the evil of the wicked!
Make the just stand firm,
you who test mind and heart,
O just God!

.11 God is the shield that protects me,
who saves the upright of heart.
.12 God is a just judge
slow to anger;
but he threatens the wicked every day,
.13 men who will not repent.

* * *

God will sharpen his sword;
he has braced his bow and taken aim.
.14 For them he has prepared deadly weapons;
he barbs his arrows with fire.
.15 Here is one who is pregnant with malice,
who conceives evil and brings forth lies.

.16 He digs a pitfall, digs it deep;
and in the trap he has made he will fall.
.17 His malice will recoil on himself;
on his own head his violence will fall.

* * *

.18 I will thank the Lord for his justice:
I will sing to the Lord, the Most High.


Psalm 8(8) Domine, Dominus noster

.2 How great is your name, O Lord our God,
through all the earth!

Your majesty is praised above the heavens;
.3 on the lips of children and of babes
you have found praise to foil your enemy,
to silence the foe and the rebel.

.4 When I see the heavens, the work of your hands,
the moon and the stars which you arranged,
.5 what is man that you should keep him in mind,
mortal man that you care for him?

.6 Yet you have made him little less than a god;
with glory and honor you crowned him,
.7 gave him power over the works of your hands,
put all things under his feet.

.8 All of them, sheep and cattle,
yes, even the savage beasts,
.9 birds of the air, and fish
that make their way through the waters.

.10 How great is your name, O Lord our God
through all the earth!


Psalm 9(9.1) Confitebor tibi

.2 I will praise you, Lord, with all my heart;
I will recount all your wonders.
.3 I will rejoice in you and be glad,
and sing psalms to your name, O Most High.

.4 See how my enemies turn back,
how they stumble and perish before you.
.5 You upheld the justice of my cause;
you sat enthroned, judging with justice.

.6 You have checked the nations, destroyed the wicked;
you have wiped out their name for ever and ever.
.7 The foe is destroyed, eternally ruined.
You uprooted their cities; their memory has perished.

.8 But the Lord sits enthroned for ever.
He has set up his throne for judgment;
.9 he will judge the world with justice,
he will judge the peoples with his truth.

.10 For the oppressed let the Lord be a stronghold,
a stronghold in times of distress.
.11 Those who know your name will trust you;
you will never forsake those who seek you.

.12 Sing psalms to the Lord who dwells in Zion.
Proclaim his mighty works among the peoples,
.13 for the Avenger of blood has remembered them,
has not forgotten the cry of the poor.

.14 Have pity on me, Lord, see my sufferings,
you who save me from the gates of death;
.15 that I may recount all your praise
at the gates of the city of Zion
and rejoice in your saving help.

.16 The nations have fallen in the pit which they made,
their feet caught in the snare they laid.
.17 The Lord has revealed himself, and given judgment.
The wicked are snared in the work of their own hands.

.18 Let the wicked go down among the dead,
all the nations forgetful of God;
.19 for the needy shall not always be forgotten
nor the hopes of the poor be in vain.

.20 Arise, Lord, let men not prevail!
Let the nations be judged before you.
.21 Lord, strike them with terror,
let the nations know they are but men.


Psalm 10(9.2) Ut quid Domine

1 Lord, why do you stand afar off
and hide yourself in times of distress?
2 The poor man is devoured by the pride of the wicked:
he is caught in the schemes that others have made.

3 For the wicked man boasts of his heart's desires;
the covetous blasphemes and spurns the Lord.
4 In his pride the wicked says: "He will not punish.
There is no God." Such are his thoughts.

5 His path is ever untroubled;
your judgment is far from his mind.
His enemies he regards with contempt.
6 He thinks: "Never shall I falter:
misfortune shall never be my lot."

7 His mouth is full of cursing, guile, oppression;
mischief and deceit are under his tongue.
8 He lies in wait among the reeds;
the innocent he murders in secret.

His eyes are on the watch for the helpless man.
9 He lurks in hiding like a lion in his lair;
he lurks in hiding to seize the poor;
he seizes the poor man and drags him away.

10 He crouches, preparing to spring,
and the helpless fall beneath such strength.
11 He thinks in his heart: "God forgets,
he hides his face, he does not see."

12 Arise then, Lord, lift up your hand!
O God, do not forget the poor!
13 Why should the wicked spurn the Lord
and think in his heart: "God will not punish"?

14 But you have seen the trouble and sorrow,
you note it, you take it in hand.
The helpless trusts himself to you;
for you are the helper of the orphan.

15 Break the power of the wicked and the sinner!
Punish their wickedness till nothing remains!
16 The Lord is king for ever and ever.
The heathen shall perish from the land he rules.

17 Lord, you hear the prayer of the poor;
you strengthen their hearts; you turn your ear
18 to protect the rights of the orphan and oppressed:
so that mortal man may strike terror no more.



Psalm 11(10) In Domine confido

1 In the Lord I have taken my refuge.
How can you say to my soul:
"Fly like a bird to its mountain.

2 See the wicked bracing their bow;
they are fixing their arrows on the string
to shoot upright men in the dark.
3 Foundations once destroyed, what can the just do?"

4 The Lord is in his holy temple,
the Lord, whose throne is in heaven.
His eyes look down on the world;
his gaze tests mortal men.

5 The Lord tests the just and the wicked;
the lover of violence he hates.
6 He sends fire and brimstone on the wicked;
he sends a scorching wind as their lot.

7 The Lord is just and loves justice;
the upright shall see his face.


Psalm 12(11) Salva me fac

.2 Help, O Lord, for good men have vanished;
truth has gone from the sons of men.
.3 Falsehood they speak one to another,
with lying lips, with a false heart.

.4 May the Lord destroy all lying lips,
the tongue that speaks high-sounding words,
.5 those who say: "Our tongue is our strength;
our lips are our own, who is our master?"

.6 "For the poor who are oppressed and the needy who groan
I myself will arise," says the Lord,
"I will grant them the salvation for which they thirst."

.7 The words of the Lord are words without alloy,
silver from the furnace, seven times refined.

.8 It is you, O Lord, who will take us in your care
and protect us for ever from this generation.
.9 See how the wicked prowl on every side,
while the worthless are prized highly by the sons of men.


Psalm 13(12) Usquequo, Domine?

.2 How long, O Lord, will you forget me?
How long will you hide your face?
.3 How long must I bear grief in my soul,
this sorrow in my heart day and night?
How long shall my enemy prevail?

.4 Look at me, answer me, Lord my God!
Give light to my eyes lest I fall asleep in death,
.5 lest my enemy say: "I have overcome him";
lest my foes rejoice to see my fall.

.6 As for me, I trust in your merciful love.
Let my heart rejoice in your saving help:
.7 Let me sing to the Lord for his goodness to me,
singing psalms to the name of the Lord, the Most High.



Psalm 14(13) Dixit insipiens

1 The fool has said in his heart:
"There is no God above."
Their deeds are corrupt, depraved;
not a good man is left.

2 From heaven the Lord looks down
on the sons of men
to see if any are wise,
if any seek God.

3 All have left the right path,
depraved, every one;
there is not a good man left,
no, not even one.

4 Will the evil-doers not understand?
They eat up my people
as though they were eating bread:
they never pray to the Lord.

5 See how they tremble with fear
without cause for fear:
for God is with the just.
6 You may mock the poor man's hope,
but his refuge is the Lord.

7 O that Israel's salvation might come from Zion!
When the Lord delivers his people from bondage,
then Jacob will be glad and Israel rejoice.


Psalm 15(14) Domine, quis habitabit?

1 Lord, who shall be admitted to your tent
and dwell on your holy mountain?

2 He who walks without fault;
he who acts with justice
and speaks the truth from his heart;
3 he who does not slander with his tongue;

He who does no wrong to his brother,
who casts no slur on his neighbor,
4 who holds the godless in disdain,
but honors those who fear the Lord;

he who keeps his pledge, come what may;
5 who takes no interest on a loan
and accepts no bribes against the innocent.
Such a man will stand firm forever.


Psalm 16(15) Conserva me, Domine

1 Preserve me, God, I take refuge in you.
2 I say to the Lord: "You are my God.
My happiness lies in you alone."

3 He has put into my heart a marvelous love
for the faithful ones who dwell in his land.
4 Those who choose other gods increase their sorrows.
Never will I offer their offerings of blood.
Never will I take their name upon my lips.

5 O Lord, it is you who are my portion and cup;
it is you yourself who are my prize.
6 The lot marked out for me is my delight:
welcome indeed the heritage that falls to me!

7 I will bless the Lord who gives me counsel,
who even at night directs my heart.
8 I keep the Lord ever in my sight:
since he is at my right hand, I shall stand firm.

9 And so my heart rejoices, my soul is glad;
even my body shall rest in safety.
10 For you will not leave my soul among the dead,
nor let your beloved know decay.

11 You will show me the path of life,
the fullness of joy in your presence,
at your right hand happiness for ever.


Psalm 17(16) Exaudi Domine

1 Lord, hear a cause that is just,
pay heed to my cry.
Turn your ear to my prayer:
no deceit is on my lips.

2 From you may my judgment come forth.
Your eyes discern the truth.

3 You search my heart, you visit me by night.
You test me and you find in me no wrong.
/4 My words are not sinful as are men's words.

I kept from violence because of your word,
5 I kept my feet firmly in your paths;
there was no faltering in my steps.

6 I am here and I call, you will hear me, O God.
Turn your ear to me; hear my words.
7 Display your great love, you whose right hand saves
your friends from those who rebel against them.

8 Guard me as the apple of your eye.
Hide me in the shadow of your wings
9 from the violent attack of the wicked.

My foes encircle me with deadly intent.
10 Their hearts tight shut, their mouths speak proudly.
11 They advance against me, and now they surround me.

Their eyes are watching to strike me to the ground,
12 as though they were lions ready to claw
or like some young lion crouched in hiding.

13 Lord, arise, confront them, strike them down!
Let your sword rescue my soul from the wicked;
14 let your hand, O Lord, rescue me from men,
from men whose reward is in this present life.

You give them their fill of your treasures;
they rejoice in abundance of offspring
and leave their wealth to their children.

15 As for me, in my justice I shall see your face
and be filled, when I awake, with the sight of your glory.


Psalm 18(17) Diligam te, Domine

.2 I love you, Lord, my strength,
.3 my rock, my fortress, my savior.
My God is the rock where I take refuge;
my shield, my mighty help, my stronghold.
.4 The Lord is worthy of all praise,
when I call I am saved from my foes.

.5 The waves of death rose about me;
the torrents of destruction assailed me;
.6 the snares of the grave entangled me;
the traps of death confronted me.

.7 In my anguish I called to the Lord;
I cried to God for help.
From his temple he heard my voice;
my cry came to his ears.

.8 Then the earth reeled and rocked;
the mountains were shaken to their base:
they reeled at his terrible anger.
.9 Smoke came forth from his nostrils
and scorching fire from his mouth:
coals were set ablaze by its heat.

.10 He lowered the heavens and came down,
a black cloud under his feet.
.11 He came enthroned on the cherubim,
he flew on the wings of the wind.

.12 He made the darkness his covering,
the dark waters of the clouds, his tent.
.13 A brightness shone out before him
with hailstones and flashes of fire.

.14 The Lord thundered in the heavens;
The Most High let his voice be heard.
.15 He shot his arrows, scattered the foe,
flashed his lightnings and put them to flight.

.16 The bed of the ocean was revealed;
the foundations of the world were laid bare
at the thunder of your threat, O Lord,
at the blast of the breath of your anger.

.17 From on high he reached down and seized me;
he drew me forth from the mighty waters.
.18 he snatched me from my powerful foe,
from my enemies whose strength I could not match.

.19 They assailed me in the day of my misfortune,
but the Lord was my support.
.20 He brought me forth into freedom,
he saved me because he loved me.

.21 He rewarded me because I was just,
repaid me, for my hands were clean,
.22 for I have kept the way of the Lord,
and have not fallen away from my God.

.23 For his judgments are all before me:
I have never neglected his commands.
.24 I have always been upright before him;
I have kept myself from guilt.

.25 He repaid me because I was just
and my hands were clean in his eyes.
.26 You are loving with those who love you:
you show yourself perfect with the perfect.

.27 With the sincere you show yourself sincere,
but the cunning you outdo in cunning.
.28 For you save a humble people
but humble the eyes that are proud.

.29 You, O Lord, are my lamp,
my God who lightens my darkness.
.30 With you I can break through any barrier,
with my God I can scale any wall.

.31 As for God, his ways are perfect;
the word of the Lord, purest gold.
He indeed is the shield
of all who make him their refuge.

.32 For who is God but the Lord?
Who is a rock but our God?
.33 the God who girds me with strength
and makes the path safe before me.

.34 My feet you make swift as the deer's;
you have made me stand firm on the heights.
.35 You have trained my hands for battle
and my hands to bend the heavy bow.

.36 You gave me your saving shield;
you upheld me, trained me with care.
.37 You gave me freedom for my steps;
my feet have never slipped.

.38 I pursued and overtook my foes,
never turning back till they were slain.
.39 I smote them so they could not rise;
they fell beneath my feet.

.40 You girded me with strength for battle;
you made my enemies fall beneath me,
.41 you made my foes take flight;
those who hated me I destroyed.

.42 They cried, but there was no one to save them;
they cried to the Lord, but in vain.
.43 I crushed them fine as dust before the wind;
trod them down like dirt in the streets.

.44 You saved me from the feuds of the people
and put me at the head of the nations.
People unknown to me served me:
.45 when they heard of me they obeyed me.

Foreign nations came to me cringing:
.46 foreign nations faded away.
They came trembling out of their strongholds.

.47 Long life to the Lord, my rock!
Praised be the God who saves me,
.48 the God who gives me redress
and subdues people under me.

.49 You saved me from my furious foes.
You set me above my assailants.
You saved me from violent men,
.50 so I will praise you, Lord, among the nations:
I will sing a psalm to your name.

.51 He has given great victories to his king
and shown his love for his anointed,
for David and his sons for ever.


Psalm 19(18) Caeli enarrant

.2 The heavens proclaim the glory of God,
and the firmament shows forth the work of his hands.
.3 Day unto day takes up the story
and night unto night makes known the message.

.4 No speech, no word, no voice is heard
.5 yet their span extends through all the earth,
their words to the utmost bounds of the world.

There he has placed a tent for the sun;
.6 it comes forth like a bridegroom coming from his tent,
rejoices like a champion to run its course.

.7 At the end of the sky is the rising of the sun;
to the furthest end of the sky is its course.
There is nothing concealed from its burning heat.

* * *

.8 The law of the Lord is perfect,
it revives the soul.
The rule of the Lord is to be trusted,
it gives wisdom to the simple.

.9 The precepts of the Lord are right,
they gladden the heart.
The command of the Lord is clear,
it gives light to the eyes.

.10 The fear of the Lord is holy,
abiding for ever.
The decrees of the Lord are truth
and all of them just.

.11 They are more to be desired than gold,
than the purest of gold
and sweeter are they than honey,
than honey from the comb.

.12 So in them your servant finds instruction;
great reward is in their keeping.
.13 But who can detect all his errors?
From hidden faults acquit me.

.14 From presumption restrain your servant
and let it not rule me.
Then shall I be blameless,
clean from grave sin.

.15 May the spoken words of my mouth,
the thoughts of my heart,
win favor in your sight, O Lord,
my rescuer, my rock!



Psalm 20(19) Exaudiat te Dominus

.2 May the Lord answer in time of trial;
may the name of Jacob's God protect you.

.3 May he send you help from his shrine
and give you support from Zion.
.4 May he remember all your offerings
and receive your sacrifice with favor.

.5 May he give you your heart's desire
and fulfill every one of your plans.
.6 May we ring out our joy at your victory
and rejoice in the name of our God.
(May the Lord grant all your prayers.)

.7 I am sure now that the Lord
will give victory to his anointed,
will reply from his holy heaven
with the mighty victory of his hand.

.8 Some trust in chariots or horses,
but we in the name of the Lord.
.9 They will collapse and fall,
but we shall hold and stand firm.

.10 Give victory to the king, O Lord,
give answer on the day we call.


Psalm 21(20) Domine, in virtute tua

.2 O Lord, your strength gives joy to the King;
how your saving help makes him glad!
.3 You have granted him his heart's desire;
you have not refused the prayer of his lips.

.4 You came to meet him with the blessings of success,
you have set on his head a crown of pure gold.
.5 He asked you for life and this you have given,
days that will last from age to age.

.6 Your saving help has given him glory.
You have laid upon him majesty and splendor,
.7 you have granted your blessings to him forever.
You have made him rejoice with the joy of your presence.

.8 The king has put his trust in the Lord:
through the mercy of the Most High he shall stand firm.
.9 His hand will seek and find all his foes,
his right hand find out those that hate him.

.10 You will burn them like a blazing furnace
on the day when you appear.
And the Lord will destroy them in his anger;
fire will swallow them up.

.11 You will wipe out their race from the earth
and their children from the sons of men.
.12 Though they plan evil against you,
though they plot, they shall not prevail.

.13 For you will force them to retreat;
at them you will aim with your bow.
.14 O Lord, arise in your strength;
we shall sing and praise your power.


Psalm 22(21) Deus, Deus meus

.2 My God, my God, why have you forsaken me?
You are far from my plea and the cry of my distress.
.3 O my God, I call by day and you give no reply;
I call by night and I find no peace.

.4 Yet you, O God, are holy,
enthroned on the praises of Israel.
.5 In you our fathers put their trust;
they trusted and you set them free.
.6 When they cried to you, they escaped.
In you they trusted and never in vain.

.7 But I am a worm and no man,
scorned by men, despised by the people.
.8 All who see me deride me.
They curl their lips, they toss their heads.
.9 "He trusted in the Lord, let him save him;
let him release him if this is his friend."

.10 Yes, it was you who took me from the womb,
entrusted me to my mother's breast.
.11 To you I was committed from my birth,
from my mother's womb you have been my God.
.12 Do not leave me alone in my distress;
Come close, there is none else to help.

.13 Many bulls have surrounded me,
fierce bulls of Bashan close me in.
.14 Against me they open wide their jaws,
like lions, rending and roaring.

.15 Like water I am poured out,
disjointed are all my bones.
My heart has become like wax,
it is melted within my breast.

.16 Parched as burnt clay is my throat,
my tongue cleaves to my jaws.

.17 Many dogs have surrounded me,
a band of the wicked beset me.
They tear holes in my hands and my feet
.16c and lay me in the dust of death.

.18 I can count every one of my bones.
These people stare at me and gloat;
.19 they divide my clothing among them.
They cast lots for my robe.

.20 O Lord, do not leave me alone,
my strength, make haste to help me!
.21 Rescue my soul from the sword,
my life from the grip of these dogs.
.22 Save my life from the jaws of these lions,
my poor soul from the horns of these oxen.

.23 I will tell of your name to my brethren
and praise you where they are assembled.
.24 "You who fear the Lord give him praise;
all sons of Jacob, give him glory.
Revere him, Israel's sons.

.25 For he has never despised
nor scorned the poverty of the poor.
From him he has not hidden his face,
but he heard the poor man when he cried."

.26 You are my praise in the great assembly.
My vows I will pay before those who fear him.
.27 The poor shall eat and shall have their fill.
They shall praise the Lord, those who seek him.
May their hearts live for ever and ever!

.28 All the earth shall remember and return to the Lord,
all families of the nations worship before him;
.29 for the kingdom is the Lord's, he is ruler of the nations.
.30 They shall worship him, all the mighty of the earth;
before him shall bow all who go down to the dust.

/.31 And my soul shall live for him, my children serve him.
They shall tell of the Lord to generations yet to come,
.32 declare his faithfulness to peoples yet unborn:
"These things the Lord has done."


Psalm 23(22) Dominus regit me

1 The Lord is my shepherd;
there is nothing I shall want.
2 Fresh and green are the pastures
where he gives me repose.
Near restful waters he leads me,
3 to revive my drooping spirit.

He guides me along the right path;
he is true to his name.
4 If I should walk in the valley of darkness
no evil would I fear.
You are there with your crook and your staff;
with these you give me comfort.

5 You have prepared a banquet for me
in the sight of my foes.
My head you have anointed with oil;
my cup is overflowing.

6 Surely goodness and kindness shall follow me
all the days of my life.
In the Lord's own house shall I dwell
for ever and ever.


Psalm 24(23) Domini est terra

1 The Lord's is the earth and its fullness,
the world and all its peoples.
2 It is he who set it on the seas;
on the waters he made it firm.

3 Who shall climb the mountain of the Lord?
Who shall stand in his holy place?
4 The man with clean hands and pure heart,
who desires not worthless things,
(who have not sworn so as to deceive their neighbor.)

5 He shall receive blessings from the Lord
and reward from the God who saves him .
6 Such are the men who seek him,
seek the face of the God of Jacob.

* * *

7 O gates, lift high your heads;
grow higher, ancient doors.
Let him enter, the king of glory!

8 Who is the king of glory?
The Lord, the mighty, the valiant,
the Lord, the valiant in war.

9 O gates, lift high your heads;
grow higher, ancient doors.
Let him enter, the king of glory!

10 Who is he, the king of glory?
He, the Lord of armies,
he is the king of glory.



Psalm 25(24) Ad te, Domine, levavi

1 To you, O Lord, I lift up my soul.
2 I trust you, let me not be disappointed;
do not let my enemies triumph.
3 Those who hope in you shall not be disappointed,
but only those who wantonly break faith.

4 Lord, make me know your ways.
Lord, teach me your paths.
5 Make me walk in your truth, and teach me:
for you are God my savior.

In you I hope all day long
7c because of your goodness, O Lord.
6 Remember your mercy, Lord,
and the love you have shown from of old.
7 Do not remember the sins of my youth.
In your love remember me.

8 The Lord is good and upright.
He shows the path to those who stray,
9 He guides the humble in the right path,
He teaches his way to the poor.

10 His ways are faithfulness and love
for those who keep his covenant and law.
11 Lord, for the sake of your name
forgive my guilt, for it is great.

12 If anyone fears the Lord
he will show him the path he should choose.
13 His soul shall live in happiness
and his children shall possess the land.
14 The Lord's friendship is for those who revere him;
to them he reveals his covenant.

15 My eyes are always on the Lord;
for he rescues my feet from the snare.
16 Turn to me and have mercy
for I am lonely and poor.

17 Relieve the anguish of my heart
and set me free from my distress.
18 See my affliction and my toil
and take all my sins away.

19 See how many are my foes;
how violent their hatred for me.
20 Preserve my life and rescue me.
Do not disappoint me, you are my refuge.
21 May innocence and uprightness protect me:
for my hope is in you, O Lord.

22 Redeem Israel, O God, from all its distress.


Psalm 26(25) Judica me, Domine

1 Give judgment for me, O Lord:
for I walk the path of perfection.
I trust in the Lord; I have not wavered.

2 Examine me, Lord, and try me;
O test my heart and my mind,
3 for your love is before my eyes
and I walk according to your truth.

4 I never take my place with liars
and with hypocrites I shall not go.
5 I hate the evil-doer's company:
I will not take my place with the wicked.

6 To prove my innocence I wash my hands
and take my place around your altar,
7 singing a song of thanksgiving,
proclaiming all your wonders.

8 O Lord, I love the house where you dwell,
the place where your glory abides.

9 Do not sweep me away with sinners,
nor my life with bloodthirsty men
10 in whose hands are evil plots,
whose right hands are filled with gold.

11 As for me, I walk the path of perfection.
Redeem me and show me your mercy.
12 My foot stands on level ground:
I will bless the Lord in the assembly.


Psalm 27(26) Dominus illuminatio

1 The Lord is my light and my help;
whom shall I fear?
The Lord is the stronghold of my life;
before whom shall I shrink?

2 When evil-doers draw near
to devour my flesh,
it is they, my enemies and foes,
who stumble and fall.

3 Though an army encamp against me
my heart would not fear.
Though war break out against me
even then would I trust.

4 There is one thing I ask of the Lord,
for this I long,
to live in the house of the Lord,
all the days of my life,
to savor the sweetness of the Lord,
to behold his temple.

5 For there he keeps me safe in his tent
in the day of evil.
He hides me in the shelter of his tent,
on a rock he sets me safe.

6 And now my head shall be raised
above my foes who surround me
and I shall offer within his tent
a sacrifice of joy.

I will sing and make music for the Lord.

7 O Lord, hear my voice when I call;
have mercy and answer.
8 Of you my heart has spoken:
"Seek his face."

It is your face, O Lord, that I seek;
9 hide not your face.
Dismiss not your servant in anger;
you have been my help.

Do not abandon or forsake me,
O God my help!
10 Though father and mother forsake me,
the Lord will receive me.

11 Instruct me, Lord, in your way;
on an even path lead me.
/12 When they lie in ambush protect me
from my enemy's greed.
False witnesses rise against me,
breathing out fury.

13 I am sure I shall see the Lord's goodness
in the land of the living.
14 Hope in him, hold firm and take heart.
Hope in the Lord!


Psalm 28(27) Ad te Domine

1 To you, O Lord, I call,
my rock, hear me.
If you do not heed I shall become
like those in the grave.

2 Hear the voice of my pleading
as I call for help,
as I lift up my hands in prayer
to your holy place.

3 Do not drag me away with the wicked,
with the evil-doers,
who speak words of peace to their neighbors
but with evil in their hearts.

4 Repay them as their actions deserve
and the malice of their deeds.
Repay them for the works of their hands;
give them their desserts.
5 For they ignore the deeds of the Lord
and the work of his hands.
(May he ruin them and never rebuild them.)

6 Blessed be Lord for he has heard
my cry, my appeal.
7 The Lord is my strength and my shield;
in him my heart trusts.
I was helped, my heart rejoices
and I praise him with my song.

8 The Lord is the strength of his people,
a fortress where his anointed find salvation.
9 Save your people; bless Israel your heritage.
Be their shepherd and carry them for ever.


Psalm 29(28) Afferte Domino

1 O give the Lord, you sons of God,
give the Lord glory and power;
2 give the Lord the glory of his name.
Adore the Lord in his holy court.

3 The Lord's voice resounding on the waters,
the Lord on the immensity of waters;
4 the voice of the Lord, full of power,
the voice of the Lord, full of splendor.

5 The Lord's voice shattering the cedars,
the Lord shatters the cedars of Lebanon;
6 he makes Lebanon leap like a calf
and Sirion like a young wild ox.

7 (The Lord's voice flashes flames of fire.)

8 The Lord's voice shaking the wilderness,
the Lord shakes the wilderness of Kadesh;
9 the Lord's voice rending the oak tree
and stripping the forest bare.

3b The God of glory thunders.
10 In his temple they all cry: "Glory!"
The Lord sat enthroned over the flood;
the Lord sits as king for ever.

11 The Lord will give strength to his people,
the Lord will bless his people with peace.



Psalm 30(29) Exaltabo te, Domine

.2 I will praise you, Lord, you have rescued me
and have not let my enemies rejoice over me.

* * *

.3 O Lord, I cried to you for help
and you, my God, have healed me.
.4 O Lord, you have raised my soul from the dead,
restored me to life from those who sink into the grave.

.5 Sing psalms to the Lord, you who love him,
give thanks to his holy name.
.6 His anger lasts a moment; his favor all through life.
At night there are tears, but joy comes with dawn.

.7 I said to myself in my good fortune:
"Nothing will ever disturb me."
.8 Your favor had set me on a mountain fastness,
then you hid your face and I was put to confusion.

.9 To you, Lord, I cried,
to my God I made appeal:
.10 "What profit would my death be, my going to the grave?
Can dust give you praise or proclaim your truth?

.11 The Lord listened and had pity.
The Lord came to my help.
.12 For me you have changed my mourning into dancing,
you removed my sackcloth and clothed me with joy.
.13 So my soul sings psalms to you unceasingly.
O Lord my God, I will thank you for ever.


Psalm 31(30) In te, Domine, speravi

.2 In you, O Lord, I take refuge.
Let me never be put to shame.
In your justice, set me free,
.3 hear me and speedily rescue me.

Be a rock of refuge for me,
a mighty stronghold to save me,
.4 for you are my rock, my stronghold.
For your name's sake, lead me and guide me.

.5 Release me from the snares they have hidden
for you are my refuge, Lord.
.6 Into your hands I commend my spirit.
It is you who will redeem me, Lord.

/.7 O God of truth, you detest
those who worship false and empty gods.
.8 As for me, I trust in the Lord:
let me be glad and rejoice in your love.

You who have seen my affliction
and taken heed of my soul's distress,
.9 have not handed me over to the enemy,
but set my feet at large.

* * *

.10 Have mercy on me, O Lord,
for I am in distress.
Tears have wasted my eyes,
my throat and my heart.

.11 For my life is spent with sorrow
and my years with sighs.
Affliction has broken down my strength
and my bones waste away.

.12 In the face of all my foes
I am a reproach,
an object of scorn to my neighbors
and of fear to my friends.

Those who see me in the street
run far away from me.
.13 I am like a dead man, forgotten,
like a thing thrown away.

.14 I have heard the slander of the crowd,
fear is all around me,
as they plot together against me,
as they plan to take my life.

.15 But as for me, I trust in you, Lord;
I say: "You are my God.
.16 My life is in your hands, deliver me
from the hands of those who hate me.

.17 Let your face shine on your servant.
Save me in your love.
.18 Let me not be put to shame for I call you,
let the wicked be shamed!

Let them be silenced in the grave,
.19 let lying lips be dumb,
that speak haughtily against the just
with pride and contempt."

* * *

.20 How great is the goodness, Lord,
that you keep for those who fear you,
that you show to those who trust you
in the sight of men.

.21 You hide them in the shelter of your presence
from the plotting of men;
you keep them safe within your tent
from disputing tongues.

.22 Blessed be the Lord who has shown me
the wonders of his love
in a fortified city.

.23 "I am far removed from your sight"
I said in my alarm.
Yet you heard the voice of my plea
when I cried for help.

.24 Love the Lord, all you saints.
He guards his faithful
but the Lord will repay to the full
those who act with pride.

.25 Be strong, let your heart take courage,
all who hope in the Lord.


Psalm 32(31) Beati quorum

1 Happy the man whose offense is forgiven,
whose sin is remitted.
2 O happy the man to whom the Lord
imputes no guilt,
in whose spirit is no guile.

3 I kept it secret and my frame was wasted.
I groaned all day long,
4 for night and day your hand was heavy upon me.
Indeed my strength was dried up
as by the summer's heat.

5 But now I have acknowledged my sins;
my guilt I did not hide.
I said: "I will confess
my offense to the Lord."
And you, Lord, have forgiven
the guilt of my sin.

6 So let every good man pray to you
in the time of need.
The floods of water may reach high
but him they shall not reach.
7 You are my hiding place, O Lord;
you save me from distress.
(You surround me with cries of deliverance.)

* * *

8 I will instruct you and teach you
the way you should go;
I will give you counsel
with my eye upon you.

9 Be not like horse and mule, unintelligent,
needing bridle and bit
else they will not approach you.
10 Many sorrows has the wicked
but he who trusts in the Lord,
loving mercy surrounds him.

* * *

11 Rejoice, rejoice in the Lord,
exult, you just!
O come, ring out your joy,
all you upright of heart.


Psalm 33(32) Exultate, justi

1 Ring out your joy to the Lord, O you just;
for praise is fitting for loyal hearts.

2 Give thanks to the Lord upon the harp,
with a ten-stringed lute sing him songs.
3 O sing him a song that is new,
play loudly, with all your skill.

4 For the word of the Lord is faithful
and all his works to be trusted.
5 The Lord loves justice and right
and fills the earth with his love.

6 By his word the heavens were made,
by the breath of his mouth all the stars.
7 He collects the waves of the ocean;
he stores up the depths of the sea.

8 Let all the earth fear the Lord
all who live in the world revere him.
9 He spoke; and it came to be.
He commanded; it sprang into being.

10 He frustrates the designs of the nations,
he defeats the plans of the peoples.
11 His own designs shall stand for ever,
the plans of his heart from age to age.

12 They are happy, whose God is the Lord,
the people he has chosen as his own.
13 From the heavens the Lord looks forth,
he sees all the children of men.

14 From the place where he dwells he gazes
on all the dwellers on the earth;
15 he who shapes the hearts of them all;
and considers all their deeds.

16 A king is not saved by his army,
nor a warrior preserved by his strength.
17 A vain hope for safety is the horse;
despite its power it cannot save.

18 The Lord looks on those who revere him,
on those who hope in his love,
19 to rescue their souls from death,
to keep them alive in famine.

20 Our soul is waiting for the Lord.
The Lord is our help and our shield.
21 In him do our hearts find joy.
We trust in his holy name.

22 May your love be upon us, O Lord,
as we place all our hope in you.


Psalm 34(33) Benedicam Dominum

.2 I will bless the Lord at all times,
his praise always on my lips;
.3 in the Lord my soul shall make its boast.
The humble shall hear and be glad.

.4 Glorify the Lord with me.
Together let us praise his name.
.5 I sought the Lord and he answered me;
from all my terrors he set me free.

.6 Look towards him and be radiant;
let your faces not be abashed.
.7 This poor man called, the Lord heard him
and rescued him from all his distress.

.8 The angel of the Lord is encamped
around those who revere him, to rescue them.
.9 Taste and see that the Lord is good.
He is happy who seeks refuge in him.

.10 Revere the Lord, you his saints.
They lack nothing, those who revere him.
.11 Strong lions suffer want and go hungry
but those who seek the Lord lack no blessing.

.12 Come, children, and hear me
that I may teach you the fear of the Lord.
.13 Who is he who longs for life
and many days, to enjoy his prosperity?

.14 Then keep your tongue from evil
and your lips from speaking deceit.
.15 Turn aside from evil and do good;
seek and strive after peace.

.16 The Lord turns his face against the wicked
to destroy their remembrance from the earth.
.17 The Lord turns his eyes to the just
and his ears to their appeal.

.18 They call and the Lord hears
and rescues them in all their distress.
.19 The Lord is close to the broken-hearted;
those whose spirit is crushed he will save.

.20 Many are the trials of the just man
but from them all the Lord will rescue him.
.21 He will keep guard over all his bones,
not one of his bones shall be broken.

.22 Evil brings death to the wicked;
those who hate the good are doomed.
.23 The Lord ransoms the souls of his servants.
Those who hide in him shall not be condemned.


Psalm 35(34) Judica, Domine

1 O Lord, plead my cause against my foes;
fight those who fight me.
2 Take up your buckler and shield;
arise to help me.

3 Take up the javelin and the spear
against those who pursue me.
O Lord, say to my soul:
"I am your salvation."

4 Let those who seek my life
be shamed and disgraced.
Let those who plan evil against me
be routed in confusion.

5 Let them be like chaff before the wind;
let God's angel scatter them.
6 Let their path be slippery and dark;
let God's angel pursue them.

7 They have hidden a net for me wantonly;
they have dug a pit.
8 Let ruin fall upon them
and take them by surprise.
Let them be caught in the net they have hidden;
let them fall into their pit.

9 But my soul shall be joyful in the Lord
and rejoice in his salvation.
10 My whole being will say:
"Lord, who is like you
who rescue the weak from the strong
and the poor from the oppressor?"

11 Lying witnesses arise
and accuse me unjustly.
12 They repay me evil for good;
my soul is forlorn.

13 When they were sick I went into mourning,
afflicted with fasting.
My prayer was ever on my lips,
14 as for a brother, a friend.
I went as though mourning a mother,
bowed down with grief.

15 Now that I am in trouble they gather,
they gather and mock me.
They take me by surprise and strike me
and tear me to pieces.
16 They provoke me with mockery on mockery
and gnash their teeth.

17 O Lord, how long will you look on?
Come to my rescue!
Save my life from these raging beasts,
my soul from these lions.
18 I will thank you in the great assembly,
amid the throng I will praise you.

19 Do not let my lying foes
rejoice over me.
Do not let those who hate me unjustly
wink eyes at each other.

20 They wish no peace to the peaceful
who live in the land.
They make deceitful plots
21 and with mouths wide open
their cry against me is: "Yes!"
We saw you do it!"

22 O Lord, you have seen, do not be silent,
do not stand afar off!
23 Awake, stir to my defense,
to my cause, O God!

24 Vindicate me, Lord, in your justice,
do not let them rejoice.
25 Do not let them think: "Yes, we have won,
we have brought you to an end!"

26 Let them be shamed and brought to disgrace
who rejoice at my misfortune.
Let them be covered with shame and confusion
who raise themselves against me.

27 Let there be joy for those who love my cause.
Let them say without end:
"Great is the Lord who delights
in the peace of his servant."
28 Then my tongue shall speak of your justice,
and all day long of your praise.


Psalm 36(35) Dixit injustus

.2 Sin speaks to the sinner
in the depths of his heart.
There is no fear of God
before his eyes.

.3 He so flatters himself in his mind
that he knows not his guilt.
.4 In his mouth are mischief and deceit.
All wisdom is gone.

.5 He plots the defeat of goodness
as he lies on his bed.
He has set his foot on evil ways,
he clings to what is evil.

* * *

.6 Your love, Lord, reaches to heaven;
your truth to the skies.
.7 Your justice is like God's mountain,
your judgments like the deep.

To both man and beast you give protection.
/.8 O Lord, how precious is your love.
My God, the sons of men
find refuge in the shelter of your wings.

.9 They feast on the riches of your house;
they drink from the stream of your delight.
.10 In you is the source of life
and in your light we see light.

.11 Keep on loving those who know you,
doing justice for upright hearts.
.12 Let the foot of the proud not crush me
nor the hand of the wicked cast me out.

.13 See how the evildoers fall!
Flung down, they shall never arise.


Psalm 37(36) Noli aemulari

1 Do not fret because of the wicked;
do not envy those who do evil,
2 for they wither quickly like grass
and fade like the green of the fields.

3 If you trust in the Lord and do good,
then you will live in the land and be secure.
4 If you find your delight in the Lord,
he will grant your heart's desire.

5 Commit your life to the Lord,
trust in him and he will act,
6 so that your justice breaks forth like the light,
your cause like the noon-day sun.

7 Be still before the Lord and wait in patience;
do not fret at the man who prospers;
a man who makes evil plots
14c to bring down the needy and the poor.

8 Calm your anger and forget your rage;
do not fret, it only leads to evil.
9 For those who do evil shall perish;
the patient shall inherit the land.

10 A little longer--and the wicked shall have gone.
Look at his place, he is not there.
11 But the humble shall own the land
and enjoy the fullness of peace.

12 The wicked man plots against the just
and gnashes his teeth against him;
13 but the Lord laughs at the wicked
for he sees that his day is at hand.

14 The sword of the wicked is drawn,
his bow is bent to slaughter the upright.
15 Their sword shall pierce their own hearts
and their bows shall be broken to pieces.

16 The just man's few possessions
are better than the wicked man's wealth;
17 for the power of the wicked shall be broken
and the Lord will support the just.

18 He protects the lives of the upright,
their heritage will last for ever.
19 They shall not be put to shame in evil days,
in time of famine their food shall not fail.

20 But all the wicked shall perish
and all the enemies of the Lord.
They are like the beauty of the meadows,
they shall vanish, they shall vanish like smoke.

21 The wicked man borrows without repaying,
but the just man is generous and gives.
22 Those blessed by the Lord shall own the land,
but those he has cursed shall be destroyed.

23 The Lord guides the steps of a man
and makes safe the path of one he loves.
24 Though he stumble he shall never fall
for the Lord holds him by the hand.

25 I was young and now I am old,
but I have never seen the just man forsaken
nor his children begging for bread.
26 All the day he is generous and lends
and his children become a blessing.

27 Then turn away from evil and do good
and you shall have a home for ever;
28 for the Lord loves justice
and will never forsake his friends.

The unjust shall be wiped out for ever
and the children of the wicked destroyed.
29 The just shall inherit the land;
there they shall live for ever.

30 The just man's mouth utters wisdom
and his lips speak what is right;
31 the law of his God is in his heart,
his steps shall be saved from stumbling.

32 The wicked man watches for the just
and seeks occasion to kill him.
33 The Lord will not leave him in his power
nor let him be condemned when he is judged.

34 Then wait for the Lord, keep to his way.
It is he who will free you from the wicked,
raise you up to posses the land
and see the wicked destroyed.

35 I have seen the wicked triumphant,
towering like a cedar of Lebanon.
36 I passed by again; he was gone.
I searched; he was nowhere to be found.

37 See the just man, mark the upright,
for the peaceful man a future lies in store,
38 but sinners shall all be destroyed.
No future lies in store for the wicked.

39 The salvation of the just comes from the Lord,
their stronghold in time of distress.
40 The Lord helps them and delivers them
and saves them: for their refuge is in him.


Psalm 38(37) Domine, ne in furore

.2 O Lord, do not rebuke me in your anger;
do not punish me, Lord, in your rage.
.3 Your arrows have sunk deep in me;
your hand has come down upon me.
.4 Through your anger all my body is sick:
through my sin, there is no health in my limbs.

.5 My guilt towers higher than my head;
it is a weight too heavy to bear.
.6 My wounds are foul and festering,
the result of my own folly.
.7 I am bowed and brought to my knees.
I go mourning all the day long.

.8 All my frame burns with fever;
all my body is sick.
.9 Spent and utterly crushed,
I cry aloud in anguish of heart.

.10 O Lord, you know all my longing:
my groans are not hidden from you.
.11 My heart throbs, my strength is spent;
the very light has gone from my eyes.

.12 My friends avoid me like a leper;
those closest to me stand afar off.
.13 Those who plot against my life lay snares;
those who seek my ruin speak of harm,
planning treachery all the day long.

.14 But I am like the deaf who cannot hear,
like the dumb unable to speak.
.15 I am like a man who hears nothing
in whose mouth is no defense.

.16 I count on you, O Lord:
it is you, Lord God, who will answer.
.17 I pray: "Do not let them mock me,
those who triumph if my foot should slip."

.18 For I am on the point of falling
and my pain is always before me.
.19 I confess that I am guilty
and my sin fills me with dismay.

.20 My wanton enemies are numberless
and my lying foes are many.
.21 They repay me evil for good
and attack me for seeking what is right.

.22 O Lord, do not forsake me!
My God, do not stay afar off!
.23 Make haste and come to my help,
O Lord, my God, my savior!


Psalm 39(38) Dixi, custodiam

.2 I said: "I will be watchful of my ways
for fear I should sin with my tongue.
I will put a curb on my lips
when the wicked man stands before me."
.3 I was dumb, silent and still.
His prosperity stirred my grief.

.4 My heart was burning within me.
At the thought of it, the fire blazed up
and my tongue burst into speech:
.5 "O Lord, you have shown me my end,
how short is the length of my days.
Now I know how fleeting is my life.

.6 You have given me a short span of days;
my life is as nothing in your sight.
A mere breath, the man who stood so firm,
.7 a mere shadow, the man passing by;
a mere breath the riches he hoards,
not knowing who will have them."

.8 And now, Lord, what is there to wait for?
In you rests all my hope.
.9 Set me free from all my sins,
do not make me the taunt of the fool.
.10 I was silent, not opening my lips,
because this was all your doing.

.11 Take away your scourge from me.
I am crushed by the blows of your hand.
.12 You punish man's sins and correct him;
like the moth you devour all he treasures.
Mortal man is no more than a breath;
.13 O Lord, hear my prayer.

O Lord, turn your ear to my cry.
Do not be deaf to my tears.
In your house I am a passing guest,
a pilgrim, like all my fathers.
.14 Look away that I may breathe again
before I depart to be no more.


Psalm 40(39) Expectans, expectavi

.2 I waited, I waited for the Lord
and he stooped down to me;
he heard my cry.

.3 He drew me from the deadly pit,
from the miry clay.
He set my feet upon a rock
and made my footsteps firm.

.4 He put a new song into my mouth,
praise of our God.
Many shall see and fear
and shall trust in the Lord.

.5 Happy the man who has placed
his trust in the Lord
and has not gone over to the rebels
who follow false gods.

.6 How many, O Lord my God,
are the wonders and designs
that you have worked for us;
you have no equal.
Should I proclaim and speak of them,
they are more than I can tell!

.7 You do not ask for sacrifice and offerings,
but an open ear.
You do not ask for holocaust and victim.
.8 Instead, here am I.

In the scroll of the book it stands written
.9 that I should do your will.
My God, I delight in your law
in the depth of my heart.

.10 Your justice I have proclaimed
in the great assembly.
My lips I have not sealed;
you know it, O Lord.

.11 I have not hidden your justice in my heart
but declared your faithful help.
I have not hidden your love and your truth
from the great assembly.

.12 O Lord, you will not withhold
your compassion from me.
Your merciful love and your truth
will always guard me.

.13 For I am beset with evils
too many to be counted.
My sins have fallen upon me
and my sight fails me.
They are more than the hairs of my head
and my heart sinks.

.14 O Lord, come to my rescue;
Lord, come to my aid.
.15 O let there be shame and confusion
on those who seek my life.

O let them turn back in confusion,
who delight in my harm.
.16 Let them be appalled, covered with shame,
who jeer at my lot.

.17 O let there be rejoicing and gladness
for all who seek you.
Let them ever say: "The Lord is great",
who love your saving help.

.18 As for me, wretched and poor,
the Lord thinks of me.
You are my rescuer, my help,
O God, do not delay.


Psalm 41(40) Beatus qui intelligit

.2 Happy the man who considers the poor and the weak.
The Lord will save him in the day of evil,
.3 will guard him, give him life, make him happy in the land
and will not give him up to the will of his foes.
.4 The Lord will help him on his bed of pain,
he will bring him back from sickness to health.

.5 As for me, I said: "Lord, have mercy on me,
heal my soul for I have sinned against you."
.6 My foes are speaking evil against me.
"how long before he dies and his name be forgotten?"
.7 They come to visit me and speak empty words,
their hearts full of malice, they spread it abroad.

.8 My enemies whisper together against me.
They all weigh up the evil which is on me.
.9 "Some deadly thing has fastened upon him,
he will not rise again from where he lies."
.10 Thus even my friend, in whom I trusted,
who ate my bread, has turned against me.

.11 But you, O Lord, have mercy on me.
Let me rise once more and I will repay them.
.12 By this I shall know that you are my friend,
if my foes do not shout in triumph over me.
.13 If you uphold me I shall be unharmed
and set in your presence for ever more.


[.14] Blessed be the Lord, the God of Israel
from age to age. Amen. Amen.
