Psalm 1(1) Beatus vir qui non abiit 


1 \mi{Hap}py in\pl{deed} is the \pl{man} 

who follows not the counsel of \pl{the} wicked, 

\mi{nor} lingers in the \pl{way} of sin\pl{ners} 

nor sits in the company \pl{of} scorners, 

2 \mi{but} whose delight is the \pl{law} of the \pl{Lord} 

and who ponders his law \pl{day} and night. 

3 \mi{He} is like a tree \pl{that} is plan\pl{ted} 

beside the flow\pl{ing} waters, 

\mi{that} yields its fruit \pl{in} due sea\pl{son} 

and whose leaves shall \pl{ne}ver fade; 

\mi{and} all that he \pl{does} shall pros\pl{per.} 

4 Not so are the wic\pl{ked,} not so! 

\mi{For} they \pl{like} winnowed \pl{chaff} 

shall be driven away \pl{by} the wind. 

5 \mi{When} the wicked are judged \pl{they} shall not \pl{stand,} 

nor find room among those \pl{who} are just; 

6 \mi{for} the Lord guards the \pl{way} of the \pl{just} 

but the way of the wicked \pl{leads} to doom. 

Psalm 2(2) Quare fremuerunt gentes 


1 Why this tumult a\pl{mong} nations, 

\mi{a}mong peoples this use\pl{less} murmur\pl{ing?} 

2 They arise, the kings \pl{of} the earth, 

\mi{prin}ces plot against the Lord and \pl{his} Anoin\pl{ted.} 

3 "Come, let us break \pl{their} fetters, 

\mi{come,} let us \pl{cast} off their \pl{yoke."} 

4 He who sits in the \pl{hea}vens laughs; 

\mi{the} Lord is laugh\pl{ing} them to \pl{scorn.} 

5 Then he will speak in \pl{his} anger, 

\mi{his} rage will strike \pl{them} with ter\pl{ror.} 

6 "It is I who have set up my king \pl{on} Zion, 

\mi{my} \pl{ho}ly moun\pl{tain."} 

7 (I will announce the decree \pl{of} the Lord:) 

\mi{The} Lord said to me: \pl{"You} are my \pl{Son.} 

It is I who have begotten \pl{you} this day. 

8 \mi{Ask} and I will shall be\pl{queath} you the na\pl{tions,} 

put the ends of the earth in your \pl{pos}session. 

9 \mi{With} a rod of i\pl{ron} you will break \pl{them,} 

shatter them like a \pl{pot}ter's jar." 

10 \mi{Now,} O \pl{kings,} under\pl{stand,} 

take warning, rulers \pl{of} the earth; 

11 \mi{serve} \pl{the} Lord with \pl{awe} 

and trembling, pay him \pl{your} homage 

12 \mi{lest} he be ang\pl{ry} and you pe\pl{rish;} 

for suddenly his an\pl{ger} will blaze. 

\mi{Bles}sed are they who put \pl{their} trust in \pl{God.} 

Psalm 3(3) Domine, quid multiplicati 


.2 \mi{How} many \pl{are} my foes, O \pl{Lord!} 

How many are rising up \pl{a}gainst me! 

.3 \mi{How} many are say\pl{ing} about \pl{me:} 

"There is no help for \pl{him} in God." 

.4 \mi{But} you, Lord, are a \pl{shield} about \pl{me,} 

my glory, who lift \pl{up} my head. 

.5 \mi{I} cry a\pl{loud} to the \pl{Lord.} 

He answers from his ho\pl{ly} mountain. 

.6 \mi{I} lie down to \pl{rest,} and I \pl{sleep.} 

I wake, for the Lord \pl{up}holds me. 

.7 \mi{I} will not fear even thou\pl{sands} of peop\pl{le} 

who are ranged on every side \pl{a}gainst me. 

.8 \mi{A}rise, \pl{Lord;} save me, my \pl{God,} 

you who strike my foes \pl{on} the mouth, 

\mi{you} who break the teeth \pl{of} the wic\pl{ked!} 

.9 O Lord of salvation, bless \pl{your} people! 

Psalm 4(4) Cum invocarem 


.2 When I call, answer me, O God \pl{of} justice; 

\mi{from} anguish you released me, have mer\pl{cy} and hear \pl{me!} 

.3 O men, how long will your hearts \pl{be} closed, 

\mi{will} you love what is futile \pl{and} seek what is \pl{false?} 

.4 It is the Lord who grants favors to those \pl{whom} he loves; 

\mi{the} Lord hears me whe\pl{never} I call \pl{him.} 

.5 Fear him; do not sin: ponder on your bed \pl{and} be still 

.6 \mi{Make} justice your sacrifice, \pl{and} trust in the \pl{Lord.} 

.7 "What can bring us happiness?" \pl{ma}ny say. 

\mi{Lift} up the light of your face \pl{on} us, O \pl{Lord.} 

.8 You have put into my heart a \pl{grea}ter joy 

\mi{than} they have from abundance \pl{of} corn and new \pl{wine.} 

.9 I will lie down in peace and sleep co\pl{mes} at once 

\mi{for} you alone, Lord, make me \pl{dwell} in sa\pl{fety.} 

Psalm 5(5) Verba mea auribus 


.2 \mi{To} my words \pl{give} ear, O \pl{Lord,} 

give heed to \pl{my} groaning. 

.3 \mi{At}tend to the \pl{sound} of my \pl{cries,} 

my King \pl{and} my God. 

\mi{/.4} It is you whom I \pl{in}voke, O \pl{Lord.} 

In the morning \pl{you} hear me; 

\mi{in} the morning I of\pl{fer} you my pra\pl{yer,} 

watching \pl{and} waiting. 

.5 \mi{You} are no God \pl{who} loves e\pl{vil;} 

no sinner \pl{is} your guest. 

.6 \mi{The} boastful \pl{shall} not stand their \pl{ground} 

be\pl{fore} your face. 

.7 \mi{You} hate all \pl{who} do e\pl{vil;} 

you destroy \pl{all} who lie. 

\mi{The} deceitful and \pl{blood}thirsty \pl{man} 

the \pl{Lord} detests. 

.8 \mi{But} I through the great\pl{ness} of your \pl{love} 

have access \pl{to} your house. 

\mi{I} bow down before your \pl{ho}ly tem\pl{ple,} 

fil\pl{led} with awe. 

.9 \mi{Lead} me, Lord, \pl{in} your jus\pl{tice,} 

because of those who \pl{lie} in wait; 

\mi{make} clear your \pl{way} before \pl{me.} 

.10 No truth can be found in \pl{their} mouths, 

\mi{their} heart \pl{is} all mis\pl{chief,} 

their throat a wi\pl{de-o}pen grave, 

\mi{all} \pl{ho}ney their \pl{speech.} 

.11 Declare them guil\pl{ty,} O God. 

\mi{Let} them fail \pl{in} their de\pl{signs.} 

Drive them out for their ma\pl{ny} offenses, 

\mi{for} they \pl{have} defied \pl{you.} 

.12 All those you protect \pl{shall} be glad 

\mi{and} \pl{ring} out their \pl{joy.} 

You shelter them; in you \pl{they} rejoice, 

\mi{those} \pl{who} love your \pl{name.} 

.13 It is you who bless \pl{the} just man 

\mi{you} surround him with fa\pl{vor} as with a \pl{shield.} 

Psalm 6(6) Domine, ne in furore 


.2 \mi{Lord,} do not reprove me \pl{in} your an\pl{ger;} 

punish me not \pl{in} your rage. 

.3 \mi{Have} mercy on me, Lord, \pl{I} have no \pl{strength;} 

Lord, heal me, my body \pl{is} racked; 

.4 \mi{my} soul is \pl{rac}ked with \pl{pain.} 

But you, \pl{O} Lord...how long? 

.5 \mi{Re}turn, Lord, \pl{res}cue my \pl{soul.} 

Save me in your mer\pl{ci}ful love; 

.6 \mi{for} in death no one \pl{re}members \pl{you;} 

from the grave, who can \pl{give} you praise? 

.7 \mi{I} am exhaus\pl{ted} with my groan\pl{ing;} 

every night I drench my pil\pl{low} with tears; 

\mi{I} bedew my \pl{bed} with weep\pl{ing.} 

.8 My eye wastes a\pl{way} with grief; 

\mi{I} have grown old sur\pl{roun}ded by my \pl{foes.} 

.9 Leave me, all you who \pl{do} evil; 

\mi{for} the Lord has \pl{heard} my weep\pl{ing.} 

.10 The Lord has \pl{heard} my plea; 

\mi{The} Lord will ac\pl{cept} my pra\pl{yer.} 

.11 All my foes will retire in \pl{con}fusion, 

\mi{foi}led and sudden\pl{ly} confoun\pl{ded.} 

Psalm 7(7) Domine, Deus meus 


.2 \mi{Lord} God, I take \pl{re}fuge in \pl{you.} 

From my pursuer save me and \pl{res}cue me, 

.3 \mi{lest} he tear me to pie\pl{ces} like a li\pl{on} 

and drag me off with no one to \pl{res}cue me. 

.4 \mi{Lord} God, if my \pl{hands} have done \pl{wrong,} 

.5 if I have paid back e\pl{vil} for good, 

\mi{I} who saved my un\pl{just} oppres\pl{sor:} 

.6 then let my foe pursue me \pl{and} seize me, 

\mi{let} him trample \pl{my} life to the \pl{ground} 

and lay my soul \pl{in} the dust. 

\mi{*} \pl{* * *} * * \pl{*} 

.7 Lord, rise up in \pl{your} anger, 

\mi{rise} against the fu\pl{ry} of my \pl{foes;} 

my God, awake! You will \pl{give} judgment. 

.8 \mi{Let} the company of na\pl{tions} gather round \pl{you,} 

taking your seat above \pl{them} on high. 

.9 \mi{(The} Lord is jud\pl{ge} of the peop\pl{les.)} 

Give judgment for me, Lord; \pl{I} am just 

\mi{and} in\pl{no}cent of \pl{heart.} 

.10 Put an end to the evil of \pl{the} wicked! 

\mi{Make} \pl{the} just stand \pl{firm,} 

you who test \pl{mind} and heart, 

\mi{O} \pl{O just God!} O just \pl{God!} 

.11 God is the shield that \pl{pro}tects me, 

\mi{who} saves the \pl{up}right of \pl{heart.} 

.12 God is a \pl{just} judge 

\mi{slow} \pl{slow} to an\pl{ger;} 

but he threatens the wicked \pl{eve}ry day, 

.13 \mi{men} who \pl{will} not re\pl{pent.} 

\pl{*} * * 

\mi{God} will \pl{shar}pen his \pl{sword;} 

he has braced his bow and \pl{ta}ken aim. 

.14 \mi{For} them he has prepared \pl{dead}ly wea\pl{pons;} 

he barbs his ar\pl{rows} with fire. 

.15 \mi{Here} is one who is preg\pl{nant} with ma\pl{lice,} 

who conceives evil and \pl{brings} forth lies. 

.16 \mi{He} digs a pit\pl{fall,} digs it \pl{deep;} 

and in the trap he has made \pl{he} will fall. 

.17 \mi{His} malice will re\pl{coil} on him\pl{self;} 

on his own head his vio\pl{lence} will fall. 

\mi{*} \pl{* * *} * * \pl{*} 

.18 I will thank the Lord for \pl{his} justice: 

\mi{I} will sing to the \pl{Lord,} the Most \pl{High.} 

Psalm 8(8) Domine, Dominus noster 


.2 \mi{How} great is your name, \pl{O} Lord our \pl{God,} 

through \pl{all} the earth! 

\mi{Your} majesty is praised a\pl{bove} the hea\pl{vens;} 

.3 on the lips of children and \pl{of} babes 

\mi{you} have found praise to \pl{foil} your e\pl{nemy,} 

to silence the foe and \pl{the} rebel. 

.4 \mi{When} I see the heavens, \pl{the} work of your \pl{hands,} 

the moon and the stars which \pl{you} arranged, 

.5 \mi{what} is man that you should \pl{keep} him in \pl{mind,} 

mortal man that you \pl{care} for him? 

.6 \mi{Yet} you have made him lit\pl{tle}less than a \pl{god;} 

with glory and honor \pl{you} crowned him, 

.7 \mi{gave} him power over \pl{the} works of your \pl{hands,} 

put all things un\pl{der} his feet. 

.8 \mi{All} of them, \pl{sheep} and cat\pl{tle,} 

yes, even the \pl{sa}vage beasts, 

.9 \mi{birds} of \pl{the} air, and \pl{fish} 

that make their way through \pl{the} waters. 

.10 \mi{How} great is your name, \pl{O} Lord our \pl{God} 

through \pl{all} the earth! 

Psalm 9(9.1) Confitebor tibi 


.2 I will praise you, Lord, with \pl{all} my heart; 

\mi{I} will re\pl{count} all your won\pl{ders.} 

.3 I will rejoice in you \pl{and} be glad, 

\mi{and} sing psalms to your \pl{name,} O Most \pl{High.} 

.4 See how my e\pl{nemies} turn back, 

\mi{how} they stumble and pe\pl{rish} before \pl{you.} 

.5 You upheld the justice \pl{of} my cause; 

\mi{you} sat enthroned, judg\pl{ing} with jus\pl{tice.} 

.6 You have checked the nations, destroyed \pl{the} wicked; 

\mi{you} have wiped out their name for e\pl{ver} and e\pl{ver.} 

.7 The foe is destroyed, eter\pl{nal}ly ruined. 

\mi{You} uprooted their cities; their memory \pl{has} peris\pl{hed.} 

.8 But the Lord sits enthroned \pl{for} ever. 

\mi{He} has set up his th\pl{rone} for jud\pl{gment;} 

.9 he will judge the world \pl{with} justice, 

\mi{he} will judge the peop\pl{les} with his \pl{truth.} 

.10 For the oppressed let the Lord be \pl{a} stronghold, 

\mi{a} stronghold in ti\pl{mes} of dis\pl{tress.} 

.11 Those who know your name \pl{will} trust you; 

\mi{you} will never for\pl{sake} those who seek \pl{you.} 

.12 Sing psalms to the Lord who dwells \pl{in} Zion. 

\mi{Proc}laim his mighty works a\pl{mong} the peop\pl{les,} 

.13 for the Avenger of blood has remem\pl{be}red them, 

\mi{has} not forgotten \pl{the} cry of the \pl{poor.} 

.14 Have pity on me, Lord, see my \pl{suf}ferings, 

\mi{you} who save me from \pl{the} gates of \pl{death;} 

.15 that I may recount \pl{all} your praise 

\mi{at} the gates of the \pl{city} of Zi\pl{on} 

and rejoice in your \pl{sav}ing help. 

.16 \mi{The} nations have fallen in the \pl{pit} which they \pl{made,} 

their feet caught in the \pl{snare} they laid. 

.17 \mi{The} Lord has revealed himself, and \pl{gi}ven jud\pl{gment.} 

The wicked are snared in the work of \pl{their} own hands. 

.18 \mi{Let} the wicked go down \pl{a}mong the \pl{dead,} 

all the nations forget\pl{ful} of God; 

.19 \mi{for} the needy shall not al\pl{ways} be for\pl{gotten} 

nor the hopes of the poor \pl{be} in vain. 

.20 \mi{A}rise, Lord, let \pl{men} not pre\pl{vail!} 

Let the nations be judged \pl{be}fore you. 

.21 \mi{Lord,} strike \pl{them} with ter\pl{ror,} 

let the nations know they \pl{are} but men. 

Psalm 10(9.2) Ut quid Domine 


1 Lord, why do you stand \pl{a}far off 

\mi{and} hide yourself in ti\pl{mes} of dis\pl{tress?} 

2 The poor man is devoured by the pride of \pl{the} wicked: 

\mi{he} is caught in the schemes that \pl{o}thers have \pl{made.} 

3 For the wicked man boasts of his hear\pl{t's} desires; 

\mi{the} covetous blasphe\pl{mes} and spurns the \pl{Lord.} 

4 In his pride the wicked says: "He will \pl{not} punish. 

\mi{There} is no God." Such \pl{are} his thoug\pl{hts.} 

5 His path is ever \pl{un}troubled; 

\mi{your} judgment \pl{is} far from his \pl{mind.} 

His enemies he regards \pl{with} contempt. 

6 \mi{He} thinks: "Ne\pl{ver} shall I fal\pl{ter:} 

misfortune shall never \pl{be} my lot." 

7 \mi{His} mouth is full of cursing, \pl{guile,} oppres\pl{sion;} 

mischief and deceit are under \pl{his} tongue. 

8 \mi{He} lies in wait \pl{a}mong the \pl{reeds;} 

the innocent he murders \pl{in} secret. 

\mi{His} eyes are on the watch for \pl{the} helpless \pl{man.} 

9 He lurks in hiding like a lion \pl{in} his lair; 

\mi{he} lurks in hid\pl{ing} to seize the \pl{poor;} 

he seizes the poor man and drags \pl{him} away. 

10 \mi{He} crouches, prepar\pl{ing} to spr\pl{ing,} 

and the helpless fall be\pl{neath} such strength. 

11 \mi{He} thinks in his \pl{heart:} "God for\pl{gets,} 

he hides his face, he \pl{does} not see." 

12 \mi{A}rise then, Lord, \pl{lift} up your \pl{hand!} 

O God, do not for\pl{get} the poor! 

13 \mi{Why} should the wic\pl{ked} spurn the \pl{Lord} 

and think in his heart: "God will not \pl{pu}nish"? 

14 \mi{But} you have seen the troub\pl{le} and sor\pl{row,} 

you note it, you take \pl{it} in hand. 

\mi{The} helpless trusts \pl{him}self to \pl{you;} 

for you are the helper of \pl{the} orphan. 

15 \mi{Break} the power of the wic\pl{ked} and the sin\pl{ner!} 

Punish their wickedness till noth\pl{ing} remains! 

16 \mi{The} Lord is king for e\pl{ver} and e\pl{ver.} 

The heathen shall perish from the land \pl{he} rules. 

17 \mi{Lord,} you hear the pra\pl{yer} of the \pl{poor;} 

you strengthen their hearts; you \pl{turn} your ear 

18 \mi{to} protect the rights of the orphan \pl{and} oppres\pl{sed:} 

so that mortal man may strike ter\pl{ror} no more. 

Psalm 11(10) In Domine confido 


1 In the Lord I have taken \pl{my} refuge. 

\mi{How} can you \pl{say} to my \pl{soul:} 

"Fly like a bird to \pl{its} mountain. 

2 \mi{See} the wic\pl{ked} bracing their \pl{bow;} 

they are fixing their arrows \pl{on} the string 

\mi{to} shoot up\pl{right} men in the \pl{dark.} 

3 Foundations once destroyed, what can \pl{the} just do?" 

4 \mi{The} Lord is in his \pl{ho}ly tem\pl{ple,} 

the Lord, whose throne is \pl{in} heaven. 

\mi{His} eyes look down \pl{on} the wor\pl{ld;} 

his gaze tests \pl{mor}tal men. 

5 \mi{The} Lord tests the just \pl{and} the wic\pl{ked;} 

the lover of vio\pl{lence} he hates. 

6 \mi{He} sends fire and brim\pl{stone} on the wic\pl{ked;} 

he sends a scorching wind \pl{as} their lot. 

7 \mi{The} Lord is just \pl{and} loves jus\pl{tice;} 

the upright shall \pl{see} his face. 

Psalm 12(11) Salva me fac 


.2 Help, O Lord, for good men have \pl{va}nished; 

\mi{truth} has gone from \pl{the} sons of \pl{men.} 

.3 Falsehood they speak one to \pl{a}nother, 

\mi{with} lying \pl{lips,} with a false \pl{heart.} 

.4 May the Lord destroy all \pl{ly}ing lips, 

\mi{the} tongue that speaks \pl{hig}h-sounding \pl{words,} 

.5 those who say: "Our tongue \pl{is} our strength; 

\mi{our} lips are our own, who \pl{is} our mas\pl{ter?"} 

.6 "For the poor who are oppressed and the \pl{needy} who groan 

\mi{I} myself will a\pl{rise,"} says the \pl{Lord,} 

"I will grant them the salvation for \pl{which} they thirst." 

.7 \mi{The} words of the Lord are words \pl{wi}thout al\pl{loy,} 

silver from the furnace, seven ti\pl{mes} refined. 

.8 \mi{It} is you, O Lord, who will take \pl{us} in your \pl{care} 

and protect us for ever from this \pl{ge}neration. 

.9 \mi{See} how the wicked prowl \pl{on} every \pl{side,} 

while the worthless are prized highly by the \pl{sons} of men. 

Psalm 13(12) Usquequo, Domine? 


.2 How long, O Lord, will you \pl{for}get me? 

\mi{How} long will \pl{you} hide your \pl{face?} 

.3 How long must I bear grief \pl{in} my soul, 

\mi{this} sorrow in my \pl{heart} day and \pl{night?} 

How long shall my e\pl{nemy} prevail? 

.4 \mi{Look} at me, an\pl{swer} me, Lord my \pl{God!} 

Give light to my eyes lest I fall as\pl{leep} in death, 

.5 \mi{lest} my enemy say: "I have \pl{o}vercome \pl{him";} 

lest my foes rejoice to \pl{see} my fall. 

.6 \mi{As} for me, I trust in your \pl{mer}ciful \pl{love.} 

Let my heart rejoice in your \pl{sav}ing help: 

.7 \mi{Let} me sing to the Lord for his \pl{good}ness to \pl{me,} 

singing psalms to the name of the Lord, \pl{the} Most High. 

Psalm 14(13) Dixit insipiens 


1 The fool has said \pl{in} his heart: 

\mi{"There} is \pl{no} God a\pl{bove."} 

Their deeds are corrupt, \pl{dep}raved; 

\mi{not} a \pl{good} man is \pl{left.} 

2 From heaven the \pl{Lord} looks down 

\mi{on} \pl{the} sons of \pl{men} 

to see if \pl{any} are wise, 

\mi{if} \pl{if} any seek \pl{God.} 

3 All have left \pl{the} right path, 

\mi{dep}ra\pl{ved,} every \pl{one;} 

there is not a \pl{good} man left, 

\mi{no,} \pl{not} even \pl{one.} 

4 Will the evil-doers not \pl{un}derstand? 

\mi{They} eat \pl{up} my peop\pl{le} 

as though they were \pl{eat}ing bread: 

\mi{they} ne\pl{ver} pray to the \pl{Lord.} 

5 See how they trem\pl{ble} with fear 

\mi{wi}\pl{thout} cause for \pl{fear:} 

for God is \pl{with} the just. 

6 \mi{You} may mock \pl{the} poor man's \pl{hope,} 

but his refuge \pl{is} the Lord. 

7 \mi{O} that Israel's salvation might \pl{come} from Zi\pl{on!} 

When the Lord delivers his people \pl{from} bondage, 

\mi{then} Jacob will be glad and Is\pl{ra}el re\pl{joice.} 

Psalm 15(14) Domine, quis habitabit? 


1 \mi{Lord,} who shall be ad\pl{mitted} to your \pl{tent} 

and dwell on your ho\pl{ly} mountain? 

2 \mi{He} who \pl{walks} without \pl{fault;} 

he who acts \pl{with} justice 

\mi{and} speaks the \pl{truth} from his \pl{heart;} 

3 he who does not slander with \pl{his} tongue; 

\mi{He} who does no wrong \pl{to} his bro\pl{ther,} 

who casts no slur on \pl{his} neighbor, 

4 \mi{who} holds the god\pl{less} in dis\pl{dain,} 

but honors those who \pl{fear} the Lord; 

\mi{he} who keeps his pled\pl{ge,} come what \pl{may;} 

5 who takes no interest \pl{on} a loan 

\mi{and} accepts no bribes against \pl{the} inno\pl{cent.} 

Such a man will stand \pl{firm} forever. 

Psalm 16(15) Conserva me, Domine 


1 Preserve me, God, I take re\pl{fuge} in you. 

2 \mi{I} say to the Lord: \pl{"You} are my \pl{God.} 

My happiness lies in \pl{you} alone." 

3 \mi{He} has put into my heart \pl{a} marvelous \pl{love} 

for the faithful ones who dwell \pl{in} his land. 

4 \mi{Those} who choose other gods in\pl{crease} their sor\pl{rows.} 

Never will I offer their offe\pl{rings} of blood. 

\mi{Ne}ver will I take their name \pl{u}pon my \pl{lips.} 

5 O Lord, it is you who are my por\pl{tion} and cup; 

\mi{it} is you your\pl{self} who are my \pl{prize.} 

6 The lot marked out for me is \pl{my} delight: 

\mi{wel}come indeed the he\pl{ritage} that falls to \pl{me!} 

7 I will bless the Lord who gives \pl{me} counsel, 

\mi{who} even at night \pl{di}rects my \pl{heart.} 

8 I keep the Lord ever \pl{in} my sight: 

\mi{since} he is at my right hand, \pl{I} shall stand \pl{firm.} 

9 And so my heart rejoices, my \pl{soul} is glad; 

\mi{e}ven my body shall \pl{rest} in sa\pl{fety.} 

10 For you will not leave my soul a\pl{mong} the dead, 

\mi{nor} let your be\pl{loved} know de\pl{cay.} 

11 You will show me the \pl{path} of life, 

\mi{the} fullness of joy \pl{in} your pre\pl{sence,} 

at your right hand happiness \pl{for} ever. 

Psalm 17(16) Exaudi Domine 


1 Lord, hear a cause \pl{that} is just, 

\mi{pay} \pl{heed} to my \pl{cry.} 

Turn your ear to \pl{my} prayer: 

\mi{no} de\pl{ceit} is on my \pl{lips.} 

2 From you may my jud\pl{gment} come forth. 

\mi{Your} e\pl{yes} discern the \pl{truth.} 

3 You search my heart, you visit \pl{me} by night. 

\mi{You} test me and you find \pl{in} me no \pl{wrong.} 

/4 My words are not sinful as \pl{are} men's words. 

\mi{I} kept from violence be\pl{cause} of your \pl{word,} 

5 I kept my feet firmly in \pl{your} paths; 

\mi{there} was no fal\pl{ter}ing in my \pl{steps.} 

6 I am here and I call, you will hear \pl{me,} O God. 

\mi{Turn} your ear to \pl{me;} hear my \pl{words.} 

7 Display your great love, you whose \pl{right} hand saves 

\mi{your} friends from those who re\pl{bel} against \pl{them.} 

8 Guard me as the apple \pl{of} your eye. 

\mi{Hide} me in the sha\pl{dow} of your \pl{wings} 

9 from the violent attack of \pl{the} wicked. 

\mi{My} foes encircle me with \pl{dead}ly in\pl{tent.} 

10 Their hearts tight shut, their mouths \pl{speak} proudly. 

11 \mi{They} advance against me, and now \pl{they} surround \pl{me.} 

Their eyes are watching to strike me \pl{to} the ground, 

12 \mi{as} though they were li\pl{ons} ready to \pl{claw} 

or like some young lion crouched \pl{in} hiding. 

13 \mi{Lord,} arise, con\pl{front} them, strike them \pl{down!} 

Let your sword rescue my soul from \pl{the} wicked; 

14 \mi{let} your hand, O Lord, res\pl{cue} me from \pl{men,} 

from men whose reward is in this \pl{pre}sent life. 

\mi{You} give them their fill \pl{of} your trea\pl{sures;} 

they rejoice in abundance \pl{of} offspring 

\mi{and} leave their wealth \pl{to} their chil\pl{dren.} 

15 As for me, in my justice I shall \pl{see} your face 

\mi{and} be filled, when I awake, with the sight \pl{of} your glo\pl{ry.} 

Psalm 18(17) Diligam te, Domine 


.2 \mi{I} love \pl{you,} Lord, my \pl{strength,} 

.3 my rock, my fortress, my \pl{sa}vior. 

\mi{My} God is the rock where \pl{I} take re\pl{fuge;} 

my shield, my mighty help, \pl{my} stronghold. 

.4 \mi{The} Lord is wor\pl{thy} of all \pl{praise,} 

when I call I am saved \pl{from} my foes. 

.5 \mi{The} waves of death \pl{rose} about \pl{me;} 

the torrents of destruction as\pl{sai}led me; 

.6 \mi{the} snares of the grave \pl{en}tangled \pl{me;} 

the traps of death con\pl{fron}ted me. 

.7 \mi{In} my anguish I cal\pl{led} to the \pl{Lord;} 

I cried to \pl{God} for help. 

\mi{From} his tem\pl{ple} he heard my \pl{voice;} 

my cry came \pl{to} his ears. 

.8 \mi{Then} the earth ree\pl{led} and roc\pl{ked;} 

the mountains were shaken \pl{to} their base: 

\mi{they} reeled at his \pl{ter}rible an\pl{ger.} 

.9 Smoke came forth from \pl{his} nostrils 

\mi{and} scorch\pl{ing} fire from his \pl{mouth:} 

coals were set ablaze \pl{by} its heat. 

.10 \mi{He} lowered the hea\pl{vens} and came \pl{down,} 

a black cloud un\pl{der} his feet. 

.11 \mi{He} came en\pl{throned} on the che\pl{rubim,} 

he flew on the wings \pl{of} the wind. 

.12 \mi{He} made the darkness \pl{his} cover\pl{ing,} 

the dark waters of the \pl{clouds,} his tent. 

.13 \mi{A} brightness shone \pl{out} before \pl{him} 

with hailstones and flas\pl{hes} of fire. 

.14 \mi{The} Lord thunde\pl{red} in the hea\pl{vens;} 

The Most High let his \pl{voice} be heard. 

.15 \mi{He} shot his arrows, scat\pl{te}red the \pl{foe,} 

flashed his lightnings and put \pl{them} to flight. 

.16 \mi{The} bed of the o\pl{cean} was re\pl{vealed;} 

the foundations of the world \pl{were} laid bare 

\mi{at} the thunder of your \pl{th}reat, O \pl{Lord,} 

at the blast of the breath of \pl{your} anger. 

.17 \mi{From} on high he reached down \pl{and} seized \pl{me;} 

he drew me forth from the mig\pl{hty} waters. 

.18 \mi{he} snatched me from my \pl{po}werful \pl{foe,} 

from my enemies whose strength I could \pl{not} match. 

.19 \mi{They} assailed me in the day \pl{of} my mis\pl{fortune,} 

but the Lord was \pl{my} support. 

.20 \mi{He} brought me forth \pl{in}to free\pl{dom,} 

he saved me because he \pl{lo}ved me. 

.21 \mi{He} rewarded me be\pl{cause} I was \pl{just,} 

repaid me, for my \pl{hands} were clean, 

.22 \mi{for} I have kept the \pl{way} of the \pl{Lord,} 

and have not fallen away \pl{from} my God. 

.23 \mi{For} his judgments are \pl{all} before \pl{me:} 

I have never neglected \pl{his} commands. 

.24 \mi{I} have always been up\pl{right} before \pl{him;} 

I have kept my\pl{self} from guilt. 

.25 \mi{He} repaid me be\pl{cause} I was \pl{just} 

and my hands were clean in \pl{his} eyes. 

.26 \mi{You} are loving \pl{with} those who love \pl{you:} 

you show yourself perfect with \pl{the} perfect. 

.27 \mi{With} the sincere you show \pl{your}self sin\pl{cere,} 

but the cunning you outdo \pl{in} cunning. 

.28 \mi{For} you save a \pl{hum}ble peop\pl{le} 

but humble the eyes \pl{that} are proud. 

.29 \mi{You,} O \pl{Lord,} are my \pl{lamp,} 

my God who lightens \pl{my} darkness. 

.30 \mi{With} you I can break th\pl{rough} any bar\pl{rier,} 

with my God I can \pl{scale} any wall. 

.31 \mi{As} for God, his \pl{ways} are per\pl{fect;} 

the word of the Lord, \pl{pu}rest gold. 

\mi{He} in\pl{deed} is the \pl{shield} 

of all who make him \pl{their} refuge. 

.32 \mi{For} who is \pl{God} but the \pl{Lord?} 

Who is a rock \pl{but} our God? 

.33 \mi{the} God who \pl{girds} me with \pl{strength} 

and makes the path safe \pl{be}fore me. 

.34 \mi{My} feet you make \pl{swift} as the \pl{deer's;} 

you have made me stand firm on \pl{the} heights. 

.35 \mi{You} have trained my \pl{hands} for bat\pl{tle} 

and my hands to bend the \pl{hea}vy bow. 

.36 \mi{You} gave me \pl{your} saving \pl{shield;} 

you upheld me, trained \pl{me} with care. 

.37 \mi{You} gave me free\pl{dom} for my \pl{steps;} 

my feet have \pl{ne}ver slipped. 

.38 \mi{I} pursued and o\pl{ver}took my \pl{foes,} 

never turning back till \pl{they} were slain. 

.39 \mi{I} smote them so \pl{they} could not \pl{rise;} 

they fell be\pl{neath} my feet. 

.40 \mi{You} girded me with \pl{strength} for bat\pl{tle;} 

you made my enemies fall \pl{be}neath me, 

.41 \mi{you} made \pl{my} foes take \pl{flight;} 

those who hated me I \pl{des}troyed. 

.42 \mi{They} cried, but there was no \pl{one} to save \pl{them;} 

they cried to the Lord, \pl{but} in vain. 

.43 \mi{I} crushed them fine as dust \pl{be}fore the \pl{wind;} 

trod them down like dirt \pl{in} the streets. 

.44 \mi{You} saved me from the feuds \pl{of} the peop\pl{le} 

and put me at the head of \pl{the} nations. 

\mi{Peop}le unknown to \pl{me} served \pl{me:} 

.45 when they heard of me they \pl{o}beyed me. 

\mi{Fo}reign nations came \pl{to} me cring\pl{ing:} 

.46 foreign nations fa\pl{ded} away. 

\mi{They} came trembling out \pl{of} their strong\pl{holds.} 

.47 Long life to the \pl{Lord,} my rock! 

\mi{Prai}sed be the \pl{God} who saves \pl{me,} 

.48 the God who gives \pl{me} redress 

\mi{and} subdues peop\pl{le} under \pl{me.} 

.49 You saved me from my \pl{fu}rious foes. 

\mi{You} set me above \pl{my} assai\pl{lants.} 

You saved me from \pl{vio}lent men, 

.50 \mi{so} I will praise you, Lord, a\pl{mong} the na\pl{tions:} 

I will sing a psalm \pl{to} your name. 

.51 \mi{He} has given great vic\pl{to}ries to his \pl{king} 

and shown his love for his \pl{a}nointed, 

\mi{for} David and his \pl{sons} for e\pl{ver.} 

Psalm 19(18) Caeli enarrant 


.2 \mi{The} heavens proclaim the \pl{glo}ry of \pl{God,} 

and the firmament shows forth the work \pl{of} his hands. 

.3 \mi{Day} unto day ta\pl{kes} up the sto\pl{ry} 

and night unto night makes known \pl{the} message. 

.4 \mi{No} speech, no word, \pl{no} voice is \pl{heard} 

.5 yet their span extends through \pl{all} the earth, 

\mi{their} words to the utmost bounds \pl{of} the wor\pl{ld.} 

There he has placed a tent \pl{for} the sun; 

.6 \mi{it} comes forth like a bridegroom com\pl{ing} from his \pl{tent,} 

rejoices like a champion to \pl{run} its course. 

.7 \mi{At} the end of the sky is the ris\pl{ing} of the \pl{sun;} 

to the furthest end of the sky \pl{is} its course. 

\mi{There} is nothing concealed from \pl{its} burning \pl{heat.} 

\pl{*} * * 

.8 \mi{The} law of the \pl{Lord} is per\pl{fect,} 

it re\pl{vives} the soul. 

\mi{The} rule of the Lord is \pl{to} be trus\pl{ted,} 

it gives wisdom to \pl{the} simple. 

.9 \mi{The} precepts \pl{of} the Lord are \pl{right,} 

they glad\pl{den} the heart. 

\mi{The} command \pl{of} the Lord is \pl{clear,} 

it gives light to \pl{the} eyes. 

.10 \mi{The} fear of the \pl{Lord} is ho\pl{ly,} 

abiding \pl{for} ever. 

\mi{The} decrees \pl{of} the Lord are \pl{truth} 

and all \pl{of} them just. 

.11 \mi{They} are more to be \pl{de}sired than \pl{gold,} 

than the pu\pl{rest} of gold 

\mi{and} sweeter are \pl{they} than ho\pl{ney,} 

than honey \pl{from} the comb. 

.12 \mi{So} in them your ser\pl{vant} finds inst\pl{ruction;} 

great reward is in \pl{their} keeping. 

.13 \mi{But} who can de\pl{tect} all his er\pl{rors?} 

From hidden faults \pl{ac}quit me. 

.14 \mi{From} presumption res\pl{train} your ser\pl{vant} 

and let it \pl{not} rule me. 

\mi{Then} shall \pl{I} be blame\pl{less,} 

clean \pl{from} grave sin. 

.15 \mi{May} the spo\pl{ken} words of my \pl{mouth,} 

the thoughts \pl{of} my heart, 

\mi{win} favor \pl{in} your sight, O \pl{Lord,} 

my res\pl{cuer,} my rock! 

Psalm 20(19) Exaudiat te Dominus 


.2 May the Lord answer in \pl{time} of trial; 

\mi{may} the name of Ja\pl{cob's} God protect \pl{you.} 

.3 May he send you help from \pl{his} shrine 

\mi{and} give you sup\pl{port} from Zi\pl{on.} 

.4 May he remember all your \pl{of}ferings 

\mi{and} receive your sacri\pl{fice} with fa\pl{vor.} 

.5 May he give you your hear\pl{t's} desire 

\mi{and} fulfill eve\pl{ry} one of your \pl{plans.} 

.6 May we ring out our joy at your \pl{vic}tory 

\mi{and} rejoice in the \pl{name} of our \pl{God.} 

(May the Lord grant all \pl{your} prayers.) 

.7 \mi{I} am sure \pl{now} that the \pl{Lord} 

will give victory to his \pl{a}nointed, 

\mi{will} reply from his \pl{ho}ly hea\pl{ven} 

with the mighty victory \pl{of} his hand. 

.8 \mi{Some} trust in chari\pl{ots} or hor\pl{ses,} 

but we in the name \pl{of} the Lord. 

.9 \mi{They} will \pl{col}lapse and \pl{fall,} 

but we shall hold \pl{and} stand firm. 

.10 \mi{Give} victory \pl{to} the king, O \pl{Lord,} 

give answer on the \pl{day} we call. 

Psalm 21(20) Domine, in virtute tua 


.2 O Lord, your strength gives joy to \pl{the} King; 

\mi{how} your saving help \pl{ma}kes him \pl{glad!} 

.3 You have granted him his hear\pl{t's} desire; 

\mi{you} have not refused the pra\pl{yer} of his \pl{lips.} 

.4 You came to meet him with the blessings \pl{of} success, 

\mi{you} have set on his head a \pl{crown} of pure \pl{gold.} 

.5 He asked you for life and this you \pl{have} given, 

\mi{days} that will last \pl{from} age to \pl{age.} 

.6 Your saving help has given \pl{him} glory. 

\mi{You} have laid upon him majes\pl{ty} and sp\pl{lendor,} 

.7 you have granted your blessings to \pl{him} forever. 

\mi{You} have made him rejoice with the joy \pl{of} your pre\pl{sence.} 

.8 The king has put his trust \pl{in} the Lord: 

\mi{th}rough the mercy of the Most High \pl{he} shall stand \pl{firm.} 

.9 His hand will seek and find \pl{all} his foes, 

\mi{his} right hand find out \pl{those} that hate \pl{him.} 

.10 You will burn them like a blaz\pl{ing} furnace 

\mi{on} the day \pl{when} you ap\pl{pear.} 

And the Lord will destroy them in \pl{his} anger; 

\mi{fire} will \pl{swal}low them \pl{up.} 

.11 You will wipe out their race \pl{from} the earth 

\mi{and} their children \pl{from} the sons of \pl{men.} 

.12 Though they plan evil \pl{a}gainst you, 

\mi{though} they plot, they \pl{shall} not pre\pl{vail.} 

.13 For you will force them \pl{to} retreat; 

\mi{at} them you will \pl{aim} with your \pl{bow.} 

.14 O Lord, arise \pl{in} your strength; 

\mi{we} shall sing and \pl{praise} your po\pl{wer.} 

Psalm 22(21) Deus, Deus meus 


.2 \mi{My} God, my God, why have you \pl{for}saken \pl{me?} 

You are far from my plea and the cry of \pl{my} distress. 

.3 \mi{O} my God, I call by day and you \pl{give} no rep\pl{ly;} 

I call by night and I \pl{find} no peace. 

.4 \mi{Yet} you, O \pl{God,} are ho\pl{ly,} 

enthroned on the praises of \pl{Is}rael. 

.5 \mi{In} you our fa\pl{thers} put their \pl{trust;} 

they trusted and you \pl{set} them free. 

.6 \mi{When} they cried to \pl{you,} they es\pl{caped.} 

In you they trusted and ne\pl{ver} in vain. 

.7 \mi{But} I am a \pl{worm} and no \pl{man,} 

scorned by men, despised by \pl{the} people. 

.8 \mi{All} who see \pl{me} deride \pl{me.} 

They curl their lips, they \pl{toss} their heads. 

.9 \mi{"He} trusted in the Lord, \pl{let} him save \pl{him;} 

let him release him if this \pl{is} his friend." 

.10 \mi{Yes,} it was you who took \pl{me} from the \pl{womb,} 

entrusted me to my \pl{mo}ther's breast. 

.11 \mi{To} you I was com\pl{mitted} from my \pl{birth,} 

from my mother's womb you have \pl{been} my God. 

.12 \mi{Do} not leave me a\pl{lone} in my dis\pl{tress;} 

Come close, there is none \pl{else} to help. 

.13 \mi{Many} bulls have \pl{sur}rounded \pl{me,} 

fierce bulls of Bashan \pl{close} me in. 

.14 \mi{A}gainst me they o\pl{pen} wide their \pl{jaws,} 

like lions, rending \pl{and} roaring. 

.15 \mi{Like} water I \pl{am} poured \pl{out,} 

disjointed are all \pl{my} bones. 

\mi{My} heart has \pl{be}come like \pl{wax,} 

it is melted wi\pl{thin} my breast. 

.16 \mi{Par}ched as burnt clay \pl{is} my th\pl{roat,} 

my tongue cleaves \pl{to} my jaws. 

.17 \mi{Many} dogs have \pl{sur}rounded \pl{me,} 

a band of the wicked \pl{be}set me. 

\mi{They} tear holes in my \pl{hands} and my \pl{feet} 

.16c and lay me in the \pl{dust} of death. 

.18 \mi{I} can count every one \pl{of} my bo\pl{nes.} 

These people stare at \pl{me} and gloat; 

.19 \mi{they} divide my cloth\pl{ing} among \pl{them.} 

They cast lots \pl{for} my robe. 

.20 \mi{O} Lord, do not \pl{leave} me a\pl{lone,} 

my strength, make haste \pl{to} help me! 

.21 \mi{Res}cue \pl{my} soul from the \pl{sword,} 

my life from the grip \pl{of} these dogs. 

.22 \mi{Save} my life from the jaws \pl{of} these li\pl{ons,} 

my poor soul from the horns of \pl{these} oxen. 

.23 \mi{I} will tell of your name \pl{to} my bre\pl{thren} 

and praise you where they are \pl{as}sembled. 

.24 \mi{"You} who fear the \pl{Lord} give him \pl{praise;} 

all sons of Jacob, give \pl{him} glory. 

\mi{Re}vere him, \pl{Is}rael's \pl{sons.} 

.25 For he has never \pl{des}pised 

\mi{nor} scorned the po\pl{ver}ty of the \pl{poor.} 

From him he has not hid\pl{den} his face, 

\mi{but} he heard the poor \pl{man} when he \pl{cried."} 

.26 You are my praise in the great \pl{as}sembly. 

\mi{My} vows I will pay be\pl{fore} those who fear \pl{him.} 

.27 The poor shall eat and shall \pl{have} their fill. 

\mi{They} shall praise the Lord, \pl{those} who seek \pl{him.} 

May their hearts live for ever \pl{and} ever! 

.28 \mi{All} the earth shall remember and re\pl{turn} to the \pl{Lord,} 

all families of the nations worship \pl{be}fore him; 

.29 \mi{for} the kingdom is the Lord's, he is ru\pl{ler} of the na\pl{tions.} 

.30 They shall worship him, all the mighty \pl{of} the earth; 

\mi{be}fore him shall bow all who go \pl{down} to the \pl{dust.} 

/.31 And my soul shall live for him, my chil\pl{dren} serve him. 

\mi{They} shall tell of the Lord to ge\pl{nera}tions yet to \pl{come,} 

.32 declare his faithfulness to peoples \pl{yet} unborn: 

\mi{"These} things \pl{the} Lord has \pl{done."} 

Psalm 23(22) Dominus regit me 


1 \mi{The} Lord \pl{is} my shep\pl{herd;} 

there is nothing \pl{I} shall want. 

2 \mi{Fresh} and green are \pl{the} pastu\pl{res} 

where he gives \pl{me} repose. 

\mi{Near} restful wa\pl{ters} he leads \pl{me,} 

3 to revive my droop\pl{ing} spirit. 

\mi{He} guides me a\pl{long} the right \pl{path;} 

he is true \pl{to} his name. 

4 \mi{If} I should walk in the val\pl{ley} of dark\pl{ness} 

no evil \pl{would} I fear. 

\mi{You} are there with your \pl{crook} and your \pl{staff;} 

with these you give \pl{me} comfort. 

5 \mi{You} have prepared a \pl{ban}quet for \pl{me} 

in the sight \pl{of} my foes. 

\mi{My} head you have a\pl{noin}ted with \pl{oil;} 

my cup is o\pl{ver}flowing. 

6 \mi{Sure}ly goodness and kind\pl{ness} shall follow \pl{me} 

all the days \pl{of} my life. 

\mi{In} the Lord's \pl{own} house shall I \pl{dwell} 

for ever \pl{and} ever. 

Psalm 24(23) Domini est terra 


1 The Lord's is the earth and \pl{its} fullness, 

\mi{the} world and \pl{all} its peop\pl{les.} 

2 It is he who set it \pl{on} the seas; 

\mi{on} the wa\pl{ters} he made it \pl{firm.} 

3 Who shall climb the mountain \pl{of} the Lord? 

\mi{Who} shall stand in \pl{his} holy \pl{place?} 

4 The man with clean hands \pl{and} pure heart, 

\mi{who} de\pl{sires} not worthless \pl{things,} 

(who have not sworn so as to deceive \pl{their} neighbor.) 

5 \mi{He} shall receive bles\pl{sings} from the \pl{Lord} 

and reward from the God who \pl{saves} him . 

6 \mi{Such} are the \pl{men} who seek \pl{him,} 

seek the face of the God \pl{of} Jacob. 

\mi{*} \pl{* * *} * * \pl{*} 

7 O gates, lift \pl{high} your heads; 

\mi{grow} hig\pl{her,} ancient \pl{doors.} 

Let him enter, the king \pl{of} glory! 

8 \mi{Who} is the \pl{king} of glo\pl{ry?} 

The Lord, the mighty, \pl{the} valiant, 

\mi{the} Lord, the \pl{va}liant in \pl{war.} 

9 O gates, lift \pl{high} your heads; 

\mi{grow} hig\pl{her,} ancient \pl{doors.} 

Let him enter, the king \pl{of} glory! 

10 \mi{Who} is he, the \pl{king} of glo\pl{ry?} 

He, the Lord \pl{of} armies, 

\mi{he} is the \pl{king} of glo\pl{ry.} 

Psalm 25(24) Ad te, Domine, levavi 


1 \mi{To} you, O Lord, I \pl{lift} up my \pl{soul.} 

2 I trust you, let me not be di\pl{sap}pointed; 

\mi{do} not let my \pl{e}nemies tri\pl{umph.} 

3 Those who hope in you shall not be di\pl{sap}pointed, 

\mi{but} only those who wan\pl{ton}ly break \pl{faith.} 

4 Lord, make me \pl{know} your ways. 

\mi{Lord,} teach \pl{me} your pa\pl{ths.} 

5 Make me walk in your truth, \pl{and} teach me: 

\mi{for} you are God \pl{my} savi\pl{or.} 

In you I hope \pl{all} day long 

\mi{7c} because of your \pl{good}ness, O \pl{Lord.} 

6 Remember your \pl{mer}cy, Lord, 

\mi{and} the love you have \pl{shown} from of \pl{old.} 

7 Do not remember the sins \pl{of} my youth. 

\mi{In} your love \pl{re}member \pl{me.} 

8 The Lord is good \pl{and} upright. 

\mi{He} shows the path \pl{to} those who \pl{stray,} 

9 He guides the humble in \pl{the} right path, 

\mi{He} teaches \pl{his} way to the \pl{poor.} 

10 His ways are faithful\pl{ness} and love 

\mi{for} those who keep his \pl{co}venant and \pl{law.} 

11 Lord, for the sake \pl{of} your name 

\mi{for}give my guilt, \pl{for} it is \pl{great.} 

12 If anyone \pl{fears} the Lord 

\mi{he} will show him the \pl{path} he should \pl{choose.} 

13 His soul shall live in \pl{hap}piness 

\mi{and} his children shall \pl{pos}sess the \pl{land.} 

14 The Lord's friendship is for those who \pl{re}vere him; 

\mi{to} them he re\pl{veals} his co\pl{venant.} 

15 My eyes are always \pl{on} the Lord; 

\mi{for} he rescues \pl{my} feet from the \pl{snare.} 

16 Turn to me and \pl{have} mercy 

\mi{for} I am \pl{lone}ly and \pl{poor.} 

17 Relieve the anguish \pl{of} my heart 

\mi{and} set me free \pl{from} my dis\pl{tress.} 

18 See my affliction \pl{and} my toil 

\mi{and} take all \pl{my} sins a\pl{way.} 

19 See how many \pl{are} my foes; 

\mi{how} violent their \pl{hat}red for \pl{me.} 

20 Preserve my life and \pl{res}cue me. 

\mi{Do} not disappoint me, you \pl{are} my re\pl{fuge.} 

21 May innocence and uprightness \pl{pro}tect me: 

\mi{for} my hope is \pl{in} you, O \pl{Lord.} 

22 Redeem Israel, O God, from all \pl{its} distress. 

Psalm 26(25) Judica me, Domine 


1 Give judgment for \pl{me,} O Lord: 

\mi{for} I walk the \pl{path} of per\pl{fection.} 

I trust in the Lord; I have \pl{not} wavered. 

2 \mi{E}xamine \pl{me,} Lord, and try \pl{me;} 

O test my heart \pl{and} my mind, 

3 \mi{for} your love is be\pl{fore} my e\pl{yes} 

and I walk according \pl{to} your truth. 

4 \mi{I} never \pl{take} my place with \pl{liars} 

and with hypocrites I \pl{shall} not go. 

5 \mi{I} hate the evil\pl{-doer's} compa\pl{ny:} 

I will not take my place with \pl{the} wicked. 

6 \mi{To} prove my inno\pl{cence} I wash my \pl{hands} 

and take my place around \pl{your} altar, 

7 \mi{sing}ing a song \pl{of} thanksgiv\pl{ing,} 

proclaiming all \pl{your} wonders. 

8 \mi{O} Lord, I love the \pl{house} where you \pl{dwell,} 

the place where your glo\pl{ry} abides. 

9 \mi{Do} not sweep me a\pl{way} with sin\pl{ners,} 

nor my life with blood\pl{thir}sty men 

10 \mi{in} whose hands \pl{are} evil \pl{plots,} 

whose right hands are fil\pl{led} with gold. 

11 \mi{As} for me, I walk the \pl{path} of per\pl{fection.} 

Redeem me and show me \pl{your} mercy. 

12 \mi{My} foot stands \pl{on} level \pl{ground:} 

I will bless the Lord in the \pl{as}sembly. 

Psalm 27(26) Dominus illuminatio 


1 The Lord is my light \pl{and} my help; 

\mi{whom} \pl{whom} shall I \pl{fear?} 

The Lord is the stronghold \pl{of} my life; 

\mi{be}fore whom \pl{shall} I sh\pl{rink?} 

2 When evil\pl{-doers} draw near 

\mi{to} \pl{de}vour my \pl{flesh,} 

it is they, my e\pl{nemies} and foes, 

\mi{who} \pl{stum}ble and \pl{fall.} 

3 Though an army encamp \pl{a}gainst me 

\mi{my} \pl{heart} would not \pl{fear.} 

Though war break out \pl{a}gainst me 

\mi{e}\pl{ven} then would I \pl{trust.} 

4 There is one thing I ask \pl{of} the Lord, 

\mi{for} \pl{for} this I \pl{long,} 

to live in the house \pl{of} the Lord, 

\mi{all} the \pl{days} of my \pl{life,} 

to savor the sweetness \pl{of} the Lord, 

\mi{to} be\pl{hold} his tem\pl{ple.} 

5 For there he keeps me safe \pl{in} his tent 

\mi{in} the \pl{day} of e\pl{vil.} 

He hides me in the shelter \pl{of} his tent, 

\mi{on} a rock \pl{he} sets me \pl{safe.} 

6 And now my head shall \pl{be} raised 

\mi{a}bove my foes \pl{who} surround \pl{me} 

and I shall offer wi\pl{thin} his tent 

\mi{a} sac\pl{ri}fice of \pl{joy.} 

I will sing and make music \pl{for} the Lord. 

7 \mi{O} Lord, hear my \pl{voice} when I \pl{call;} 

have mercy \pl{and} answer. 

8 \mi{Of} you my \pl{heart} has spo\pl{ken:} 

\pl{"Seek} his face." 

\mi{It} is your face, O \pl{Lord,} that I \pl{seek;} 

9 hide \pl{not} your face. 

\mi{Dis}miss not your ser\pl{vant} in an\pl{ger;} 

you have \pl{been} my help. 

\mi{Do} not aban\pl{don} or forsake \pl{me,} 

O \pl{God} my help! 

10 \mi{Though} father and mo\pl{ther} forsake \pl{me,} 

the Lord will \pl{re}ceive me. 

11 \mi{In}struct \pl{me,} Lord, in your \pl{way;} 

on an even \pl{path} lead me. 

\mi{/12} When they lie in am\pl{bush} protect \pl{me} 

from my e\pl{nem}y's greed. 

\mi{False} wit\pl{nesses} rise against \pl{me,} 

breathing \pl{out} fury. 

13 \mi{I} am sure I shall see the \pl{Lor}d's good\pl{ness} 

in the land of \pl{the} living. 

14 \mi{Hope} in him, hold \pl{firm} and take \pl{heart.} 

Hope \pl{in} the Lord! 

Psalm 28(27) Ad te Domine 


1 To you, O \pl{Lord,} I call, 

\mi{my} \pl{my} rock, hear \pl{me.} 

If you do not heed I \pl{shall} become 

\mi{like} \pl{those} in the \pl{grave.} 

2 Hear the voice of \pl{my} pleading 

\mi{as} \pl{I} call for \pl{help,} 

as I lift up my hands \pl{in} prayer 

\mi{to} \pl{your} holy \pl{place.} 

3 Do not drag me away with \pl{the} wicked, 

\mi{with} \pl{the} evil\pl{-doers,} 

who speak words of peace to \pl{their} neighbors 

\mi{but} with e\pl{vil} in their \pl{hearts.} 

4 Repay them as their ac\pl{tions} deserve 

\mi{and} the ma\pl{lice} of their \pl{deeds.} 

Repay them for the works \pl{of} their hands; 

\mi{give} \pl{them} their des\pl{serts.} 

5 For they ignore the deeds \pl{of} the Lord 

\mi{and} the \pl{work} of his \pl{hands.} 

(May he ruin them and never \pl{re}build them.) 

6 \mi{Bles}sed be Lord \pl{for} he has \pl{heard} 

my cry, \pl{my} appeal. 

7 \mi{The} Lord is my \pl{strength} and my \pl{shield;} 

in him \pl{my} heart trusts. 

\mi{I} was helped, \pl{my} heart re\pl{joices} 

and I praise him \pl{with} my song. 

8 \mi{The} Lord is the strength \pl{of} his peop\pl{le,} 

a fortress where his anointed find \pl{sal}vation. 

9 \mi{Save} your people; bless Isra\pl{el} your he\pl{ritage.} 

Be their shepherd and carry them \pl{for} ever. 

Psalm 29(28) Afferte Domino 


1 O give the Lord, you \pl{sons} of God, 

\mi{give} the Lord glo\pl{ry} and po\pl{wer;} 

2 give the Lord the glory \pl{of} his name. 

\mi{A}dore the Lord in \pl{his} holy \pl{court.} 

3 The Lord's voice resounding on \pl{the} waters, 

\mi{the} Lord on the im\pl{mensity} of wa\pl{ters;} 

4 the voice of the Lord, full \pl{of} power, 

\mi{the} voice of the Lord, \pl{full} of sp\pl{lendor.} 

5 The Lord's voice shattering \pl{the} cedars, 

\mi{the} Lord shatters the ce\pl{dars} of Le\pl{banon;} 

6 he makes Lebanon leap \pl{like} a calf 

\mi{and} Sirion \pl{like} a young wild \pl{ox.} 

7 (The Lord's voice flashes fla\pl{mes} of fire.) 

8 \mi{The} Lord's voice shaking \pl{the} wilder\pl{ness,} 

the Lord shakes the wilderness \pl{of} Kadesh; 

9 \mi{the} Lord's voice rend\pl{ing} the oak \pl{tree} 

and stripping the \pl{fo}rest bare. 

\mi{3b} The God of \pl{glo}ry thun\pl{ders.} 

10 In his temple they all cry: \pl{"G}lory!" 

\mi{The} Lord sat en\pl{throned} over the \pl{flood;} 

the Lord sits as king \pl{for} ever. 

11 \mi{The} Lord will give strength \pl{to} his peop\pl{le,} 

the Lord will bless his peop\pl{le} with peace. 

Psalm 30(29) Exaltabo te, Domine 


.2 I will praise you, Lord, you have \pl{res}cued me 

\mi{and} have not let my enemies re\pl{joice} over \pl{me.} 

\pl{*} * * 

.3 \mi{O} Lord, I cried \pl{to} you for \pl{help} 

and you, my God, have \pl{hea}led me. 

.4 \mi{O} Lord, you have raised \pl{my} soul from the \pl{dead,} 

restored me to life from those who sink in\pl{to} the grave. 

.5 \mi{S}ing psalms to the Lord, \pl{you} who love \pl{him,} 

give thanks to his \pl{ho}ly name. 

.6 \mi{His} anger lasts a moment; his fa\pl{vor} all through \pl{life.} 

At night there are tears, but joy co\pl{mes} with dawn. 

.7 \mi{I} said to myself in \pl{my} good for\pl{tune:} 

"Nothing will ever \pl{dis}turb me." 

.8 \mi{Your} favor had set me on a \pl{moun}tain fast\pl{ness,} 

then you hid your face and I was put to \pl{con}fusion. 

.9 \mi{To} \pl{you,} Lord, I \pl{cried,} 

to my God I \pl{made} appeal: 

.10 \mi{"W}hat profit would my death be, my go\pl{ing} to the \pl{grave?} 

Can dust give you praise or proc\pl{laim} your truth? 

.11 \mi{The} Lord lis\pl{tened} and had \pl{pity.} 

The Lord came \pl{to} my help. 

.12 \mi{For} me you have changed my mourning \pl{in}to danc\pl{ing,} 

you removed my sackcloth and clothed \pl{me} with joy. 

.13 \mi{So} my soul sings psalms to you \pl{un}ceasing\pl{ly.} 

O Lord my God, I will thank you \pl{for} ever. 

Psalm 31(30) In te, Domine, speravi 


.2 In you, O Lord, I \pl{take} refuge. 

\mi{Let} me ne\pl{ver} be put to \pl{shame.} 

In your justice, \pl{set} me free, 

.3 \mi{hear} me and speedi\pl{ly} rescue \pl{me.} 

Be a rock of re\pl{fuge} for me, 

\mi{a} mighty strong\pl{hold} to save \pl{me,} 

.4 for you are my rock, \pl{my} stronghold. 

\mi{For} your name's sake, lead \pl{me} and guide \pl{me.} 

.5 Release me from the snares they \pl{have} hidden 

\mi{for} you are \pl{my} refuge, \pl{Lord.} 

.6 Into your hands I commend \pl{my} spirit. 

\mi{It} is you who will \pl{re}deem me, \pl{Lord.} 

/.7 O God of truth, \pl{you} detest 

\mi{those} who worship false \pl{and} empty \pl{gods.} 

.8 As for me, I trust \pl{in} the Lord: 

\mi{let} me be glad and re\pl{joice} in your \pl{love.} 

You who have seen my \pl{af}fliction 

\mi{and} taken heed of \pl{my} soul's dis\pl{tress,} 

.9 have not handed me over to \pl{the} enemy, 

\mi{but} set my \pl{feet} at lar\pl{ge.} 

\pl{*} * * 

.10 \mi{Have} mer\pl{cy} on me, O \pl{Lord,} 

for I am \pl{in} distress. 

\mi{Tears} have was\pl{ted} my e\pl{yes,} 

my throat \pl{and} my heart. 

.11 \mi{For} my life is \pl{spent} with sor\pl{row} 

and my \pl{years} with sighs. 

\mi{Af}fliction has bro\pl{ken} down my \pl{strength} 

and my bones was\pl{te} away. 

.12 \mi{In} the face \pl{of} all my \pl{foes} 

I am \pl{a} reproach, 

\mi{an} object of scorn \pl{to} my neig\pl{hbors} 

and of fear \pl{to} my friends. 

\mi{Those} who see \pl{me} in the \pl{street} 

run far a\pl{way} from me. 

.13 \mi{I} am like a \pl{dead} man, for\pl{gotten,} 

like a thing th\pl{rown} away. 

.14 \mi{I} have heard the slan\pl{der} of the \pl{crowd,} 

fear is all \pl{a}round me, 

\mi{as} they plot toge\pl{ther} against \pl{me,} 

as they plan to \pl{take} my life. 

.15 \mi{But} as for me, I \pl{trust} in you, \pl{Lord;} 

I say: "You \pl{are} my God. 

.16 \mi{My} life is in your \pl{hands,} deliver \pl{me} 

from the hands of those \pl{who} hate me. 

.17 \mi{Let} your face shine \pl{on} your ser\pl{vant.} 

Save me \pl{in} your love. 

.18 \mi{Let} me not be put to shame \pl{for} I call \pl{you,} 

let the wic\pl{ked} be shamed! 

\mi{Let} them be si\pl{len}ced in the \pl{grave,} 

.19 let lying \pl{lips} be dumb, 

\mi{that} speak haughti\pl{ly} against the \pl{just} 

with pride \pl{and} contempt." 

\mi{*} \pl{* * *} * * \pl{*} 

.20 How great is the \pl{good}ness, Lord, 

\mi{that} you keep for \pl{those} who fear \pl{you,} 

that you show to those \pl{who} trust you 

\mi{in} \pl{the} sight of \pl{men.} 

.21 You hide them in the shelter of \pl{your} presence 

\mi{from} the \pl{plott}ing of \pl{men;} 

you keep them safe wi\pl{thin} your tent 

\mi{from} dis\pl{put}ing ton\pl{gues.} 

.22 Blessed be the Lord who \pl{has} shown me 

\mi{the} won\pl{ders} of his \pl{love} 

in a for\pl{ti}fied city. 

.23 \mi{"I} am far re\pl{moved} from your \pl{sight"} 

I said in \pl{my} alarm. 

\mi{Yet} you heard the \pl{voice} of my \pl{plea} 

when I \pl{cried} for help. 

.24 \mi{Love} the \pl{Lord,} all you \pl{saints.} 

He guards \pl{his} faithful 

\mi{but} the Lord will re\pl{pay} to the \pl{full} 

those who \pl{act} with pride. 

.25 \mi{Be} strong, let your \pl{heart} take cou\pl{rage,} 

all who hope \pl{in} the Lord. 

Psalm 32(31) Beati quorum 


1 Happy the man whose offense is \pl{for}given, 

\mi{whose} sin \pl{is} remit\pl{ted.} 

2 O happy the man to \pl{whom} the Lord 

\mi{im} \pl{im}putes no \pl{guilt,} 

in whose spirit \pl{is} no guile. 

3 \mi{I} kept it secret and my \pl{frame} was was\pl{ted.} 

I groaned \pl{all} day long, 

4 \mi{for} night and day your hand was hea\pl{vy} upon \pl{me.} 

Indeed my strength \pl{was} dried up 

\mi{as} by \pl{the} summer's \pl{heat.} 

5 But now I have acknow\pl{ledged} my sins; 

\mi{my} guilt \pl{I} did not \pl{hide.} 

I said: "I \pl{will} confess 

\mi{my} of\pl{fense} to the \pl{Lord."} 

And you, Lord, have \pl{for}given 

\mi{the} \pl{guilt} of my \pl{sin.} 

6 So let every good man \pl{pray} to you 

\mi{in} \pl{the} time of \pl{need.} 

The floods of water \pl{may} reach high 

\mi{but} him \pl{they} shall not \pl{reach.} 

7 You are my hiding \pl{place,} O Lord; 

\mi{you} save \pl{me} from dis\pl{tress.} 

(You surround me with cries of \pl{de}liverance.) 

\mi{*} \pl{* * *} * * \pl{*} 

8 I will instruct you \pl{and} teach you 

\mi{the} \pl{way} you should \pl{go;} 

I will give \pl{you} counsel 

\mi{with} my \pl{eye} upon \pl{you.} 

9 Be not like horse and mule, un\pl{in}telligent, 

\mi{need}\pl{ing} bridle and \pl{bit} 

else they will not \pl{ap}proach you. 

10 \mi{Many} sor\pl{rows} has the wic\pl{ked} 

but he who trusts \pl{in} the Lord, 

\mi{lov}ing mer\pl{cy} surrounds \pl{him.} 

\pl{*} * * 

11 \mi{Re}joice, re\pl{joice} in the \pl{Lord,} 

e\pl{xult,} you just! 

\mi{O} come, \pl{ring} out your \pl{joy,} 

all you up\pl{right} of heart. 

Psalm 33(32) Exultate, justi 


1 Ring out your joy to the Lord, \pl{O} you just; 

\mi{for} praise is fitt\pl{ing} for loyal \pl{hearts.} 

2 Give thanks to the Lord u\pl{pon} the harp, 

\mi{with} a ten\pl{-stringed} lute sing him \pl{songs.} 

3 O sing him a song \pl{that} is new, 

\mi{play} loud\pl{ly,} with all your \pl{skill.} 

4 For the word of the Lord \pl{is} faithful 

\mi{and} all his works \pl{to} be trus\pl{ted.} 

5 The Lord loves jus\pl{tice} and right 

\mi{and} fills the \pl{earth} with his \pl{love.} 

6 By his word the hea\pl{vens} were made, 

\mi{by} the breath of his \pl{mouth} all the \pl{stars.} 

7 He collects the waves of \pl{the} ocean; 

\mi{he} stores up the dep\pl{ths} of the \pl{sea.} 

8 Let all the earth \pl{fear} the Lord 

\mi{all} who live in the wor\pl{ld} revere \pl{him.} 

9 He spoke; and it \pl{came} to be. 

\mi{He} commanded; it sprang \pl{in}to be\pl{ing.} 

10 He frustrates the designs of \pl{the} nations, 

\mi{he} defeats the plans \pl{of} the peop\pl{les.} 

11 His own designs shall stand \pl{for} ever, 

\mi{the} plans of his heart \pl{from} age to \pl{age.} 

12 They are happy, whose God \pl{is} the Lord, 

\mi{the} people he has cho\pl{sen} as his \pl{own.} 

13 From the heavens the \pl{Lord} looks forth, 

\mi{he} sees all the \pl{chil}dren of \pl{men.} 

14 From the place where he dwells \pl{he} gazes 

\mi{on} all the dw\pl{el}lers on the \pl{earth;} 

15 he who shapes the hearts \pl{of} them all; 

\mi{and} con\pl{si}ders all their \pl{deeds.} 

16 A king is not saved by \pl{his} army, 

\mi{nor} a warrior pre\pl{ser}ved by his \pl{strength.} 

17 A vain hope for safety \pl{is} the horse; 

\mi{des}pite its po\pl{wer} it cannot \pl{save.} 

18 The Lord looks on those who \pl{re}vere him, 

\mi{on} those who \pl{hope} in his \pl{love,} 

19 to rescue their \pl{souls} from death, 

\mi{to} keep them a\pl{live} in fa\pl{mine.} 

20 Our soul is waiting \pl{for} the Lord. 

\mi{The} Lord is our \pl{help} and our \pl{shield.} 

21 In him do our \pl{hearts} find joy. 

\mi{We} trust in \pl{his} holy \pl{name.} 

22 May your love be upon \pl{us,} O Lord, 

\mi{as} we place all \pl{our} hope in \pl{you.} 

Psalm 34(33) Benedicam Dominum 


.2 \mi{I} will bless the Lord \pl{at} all ti\pl{mes,} 

his praise always \pl{on} my lips; 

.3 \mi{in} the Lord my soul \pl{shall} make its \pl{boast.} 

The humble shall hear \pl{and} be glad. 

.4 \mi{Glo}\pl{rify} the Lord with \pl{me.} 

Together let us \pl{praise} his name. 

.5 \mi{I} sought the Lord and he \pl{an}swered \pl{me;} 

from all my terrors he \pl{set} me free. 

.6 \mi{Look} towards him \pl{and} be ra\pl{diant;} 

let your faces not be \pl{a}bashed. 

.7 \mi{This} poor man cal\pl{led,} the Lord heard \pl{him} 

and rescued him from all \pl{his} distress. 

.8 \mi{The} angel of the \pl{Lord} is en\pl{camped} 

around those who revere him, to \pl{res}cue them. 

.9 \mi{Tas}te and see that \pl{the} Lord is \pl{good.} 

He is happy who seeks re\pl{fuge} in him. 

.10 \mi{Re}vere \pl{the} Lord, you his \pl{saints.} 

They lack nothing, those who \pl{re}vere him. 

.11 \mi{St}rong lions suffer want \pl{and} go hung\pl{ry} 

but those who seek the Lord lack no \pl{b}lessing. 

.12 \mi{Come,} chil\pl{dren,} and hear \pl{me} 

that I may teach you the fear \pl{of} the Lord. 

.13 \mi{Who} is he \pl{who} longs for \pl{life} 

and many days, to enjoy his \pl{pros}perity? 

.14 \mi{Then} keep your ton\pl{gue} from e\pl{vil} 

and your lips from speak\pl{ing} deceit. 

.15 \mi{Turn} aside from e\pl{vil} and do \pl{good;} 

seek and strive \pl{af}ter peace. 

.16 \mi{The} Lord turns his face a\pl{gainst} the wic\pl{ked} 

to destroy their remembrance \pl{from} the earth. 

.17 \mi{The} Lord turns his e\pl{yes} to the \pl{just} 

and his ears to \pl{their} appeal. 

.18 \mi{They} call \pl{and} the Lord \pl{hears} 

and rescues them in all \pl{their} distress. 

.19 \mi{The} Lord is close to the \pl{bro}ken-hear\pl{ted;} 

those whose spirit is crushed \pl{he} will save. 

.20 \mi{Many} are the trials \pl{of} the just \pl{man} 

but from them all the Lord will \pl{res}cue him. 

.21 \mi{He} will keep guard o\pl{ver} all his bo\pl{nes,} 

not one of his bones shall \pl{be} broken. 

.22 \mi{E}vil brings death \pl{to} the wic\pl{ked;} 

those who hate the \pl{good} are doomed. 

.23 \mi{The} Lord ransoms the souls \pl{of} his ser\pl{vants.} 

Those who hide in him shall not \pl{be} condemned. 

Psalm 35(34) Judica, Domine 


1 O Lord, plead my cause a\pl{gainst} my foes; 

\mi{fight} \pl{those} who fight \pl{me.} 

2 Take up your buc\pl{kler} and shield; 

\mi{a}\pl{rise} to help \pl{me.} 

3 Take up the javelin \pl{and} the spear 

\mi{a}gainst those \pl{who} pursue \pl{me.} 

O Lord, say \pl{to} my soul: 

\mi{"I} am \pl{your} salva\pl{tion."} 

4 Let those who \pl{seek} my life 

\mi{be} shamed \pl{and} disgra\pl{ced.} 

Let those who plan evil \pl{a}gainst me 

\mi{be} routed \pl{in} confu\pl{sion.} 

5 Let them be like chaff be\pl{fore} the wind; 

\mi{let} God's an\pl{gel} scatter \pl{them.} 

6 Let their path be slippe\pl{ry} and dark; 

\mi{let} God's an\pl{gel} pursue \pl{them.} 

7 They have hidden a net for me \pl{wan}tonly; 

\mi{they} \pl{have} dug a \pl{pit.} 

8 Let ruin fall \pl{u}pon them 

\mi{and} take \pl{them} by sur\pl{prise.} 

Let them be caught in the net they \pl{have} hidden; 

\mi{let} them fall \pl{in}to their \pl{pit.} 

9 But my soul shall be joyful \pl{in} the Lord 

\mi{and} rejoice in \pl{his} salva\pl{tion.} 

10 My whole be\pl{ing} will say: 

\mi{"Lord,} \pl{who} is like \pl{you} 

who rescue the weak \pl{from} the strong 

\mi{and} the poor from \pl{the} oppres\pl{sor?"} 

11 Lying wit\pl{nesses} arise 

\mi{and} accuse \pl{me} unjust\pl{ly.} 

12 They repay me e\pl{vil} for good; 

\mi{my} \pl{soul} is for\pl{lorn.} 

13 When they were sick I went in\pl{to} mourning, 

\mi{af}flic\pl{ted} with fast\pl{ing.} 

My prayer was ever \pl{on} my lips, 

14 \mi{as} for a \pl{bro}ther, a \pl{friend.} 

I went as though mourning \pl{a} mother, 

\mi{bowed} \pl{bowed} down with \pl{grief.} 

15 Now that I am in trouble \pl{they} gather, 

\mi{they} ga\pl{ther} and mock \pl{me.} 

They take me by surprise \pl{and} strike me 

\mi{and} tear \pl{me} to pie\pl{ces.} 

16 They provoke me with mockery on \pl{moc}kery 

\mi{and} \pl{and} gnash their \pl{teeth.} 

17 O Lord, how long will \pl{you} look on? 

\mi{Come} \pl{to} my res\pl{cue!} 

Save my life from these \pl{rag}ing beasts, 

\mi{my} soul \pl{from} these li\pl{ons.} 

18 I will thank you in the great \pl{as}sembly, 

\mi{a}mid the th\pl{rong} I will praise \pl{you.} 

19 Do not let my \pl{ly}ing foes 

\mi{re}\pl{joice} over \pl{me.} 

Do not let those who hate me \pl{un}justly 

\mi{wink} e\pl{yes} at each o\pl{ther.} 

20 They wish no peace to \pl{the} peaceful 

\mi{who} \pl{live} in the \pl{land.} 

They make de\pl{ceit}ful plots 

21 \mi{and} with mou\pl{ths} wide o\pl{pen} 

their cry against \pl{me} is: "Yes!" 

\mi{We} \pl{saw} you do \pl{it!"} 

22 O Lord, you have seen, do not \pl{be} silent, 

\mi{do} not \pl{stand} afar \pl{off!} 

23 Awake, stir to \pl{my} defense, 

\mi{to} \pl{my} cause, O \pl{God!} 

24 Vindicate me, Lord, in \pl{your} justice, 

\mi{do} not \pl{let} them re\pl{joice.} 

25 Do not let them think: "Yes, \pl{we} have won, 

\mi{we} have brought \pl{you} to an \pl{end!"} 

26 Let them be shamed and brought \pl{to} disgrace 

\mi{who} re\pl{joice} at my mis\pl{fortune.} 

Let them be covered with shame and \pl{con}fusion 

\mi{who} raise them\pl{selves} against \pl{me.} 

27 Let there be joy for those who \pl{love} my cause. 

\mi{Let} them \pl{say} without \pl{end:} 

"Great is the Lord who \pl{de}lights 

\mi{in} the peace \pl{of} his ser\pl{vant."} 

28 Then my tongue shall speak of \pl{your} justice, 

\mi{and} all day \pl{long} of your \pl{praise.} 

Psalm 36(35) Dixit injustus 


.2 \mi{Sin} speaks \pl{to} the sin\pl{ner} 

in the depths \pl{of} his heart. 

\mi{There} is \pl{no} fear of \pl{God} 

before \pl{his} eyes. 

.3 \mi{He} so flatters him\pl{self} in his \pl{mind} 

that he knows \pl{not} his guilt. 

.4 \mi{In} his mouth are mis\pl{chief} and de\pl{ceit.} 

All wis\pl{dom} is gone. 

.5 \mi{He} plots the de\pl{feat} of good\pl{ness} 

as he lies \pl{on} his bed. 

\mi{He} has set his foot \pl{on} evil \pl{ways,} 

he clings to what \pl{is} evil. 

\mi{*} \pl{* * *} * * \pl{*} 

.6 Your love, Lord, reaches \pl{to} heaven; 

\mi{your} \pl{truth} to the \pl{skies.} 

.7 Your justice is like \pl{God's} mountain, 

\mi{your} jud\pl{gments} like the \pl{deep.} 

To both man and beast you give \pl{pro}tection. 

\mi{/.8} O Lord, how pre\pl{cious} is your \pl{love.} 

My God, the \pl{sons} of men 

\mi{find} refuge in the sh\pl{el}ter of your \pl{wings.} 

.9 They feast on the riches \pl{of} your house; 

\mi{they} drink from the stream \pl{of} your de\pl{light.} 

.10 In you is the \pl{source} of life 

\mi{and} in your \pl{light} we see \pl{light.} 

.11 Keep on loving those \pl{who} know you, 

\mi{do}ing jus\pl{tice} for upright \pl{hearts.} 

.12 Let the foot of the proud \pl{not} crush me 

\mi{nor} the hand of the wic\pl{ked} cast me \pl{out.} 

.13 See how the e\pl{vil}doers fall! 

\mi{Flung} down, they shall \pl{ne}ver a\pl{rise.} 

Psalm 37(36) Noli aemulari 


1 \mi{Do} not fret be\pl{cause} of the wic\pl{ked;} 

do not envy those who \pl{do} evil, 

2 \mi{for} they wi\pl{ther} quickly like \pl{grass} 

and fade like the green \pl{of} the fields. 

3 \mi{If} you trust in the \pl{Lord} and do \pl{good,} 

then you will live in the land and \pl{be} secure. 

4 \mi{If} you find your de\pl{light} in the \pl{Lord,} 

he will grant your hear\pl{t's} desire. 

5 \mi{Com}mit \pl{your} life to the \pl{Lord,} 

trust in him and \pl{he} will act, 

6 \mi{so} that your justice \pl{breaks} forth like the \pl{light,} 

your cause like the \pl{noon}-day sun. 

7 \mi{Be} still before the Lord and \pl{wait} in pa\pl{tience;} 

do not fret at the man \pl{who} prospers; 

\mi{a} man who ma\pl{kes} evil \pl{plots} 

14c to bring down the needy \pl{and} the poor. 

8 \mi{Calm} your anger and \pl{for}get your \pl{rage;} 

do not fret, it only leads \pl{to} evil. 

9 \mi{For} those who do e\pl{vil} shall pe\pl{rish;} 

the patient shall inhe\pl{rit} the land. 

10 \mi{A} little longer--and the wic\pl{ked} shall have \pl{gone.} 

Look at his place, he \pl{is} not there. 

11 \mi{But} the hum\pl{ble} shall own the \pl{land} 

and enjoy the full\pl{ness} of peace. 

12 \mi{The} wicked man plots \pl{a}gainst the \pl{just} 

and gnashes his teeth \pl{a}gainst him; 

13 \mi{but} the Lord laughs \pl{at} the wic\pl{ked} 

for he sees that his day \pl{is} at hand. 

14 \mi{The} sword of the \pl{wic}ked is \pl{drawn,} 

his bow is bent to slaughter \pl{the} upright. 

15 \mi{Their} sword shall \pl{pierce} their own \pl{hearts} 

and their bows shall be broken \pl{to} pieces. 

16 \mi{The} just \pl{man's} few pos\pl{sessions} 

are better than the wic\pl{ked} man's wealth; 

17 \mi{for} the power of the wic\pl{ked} shall be bro\pl{ken} 

and the Lord will sup\pl{port} the just. 

18 \mi{He} protects the lives \pl{of} the up\pl{right,} 

their heritage will last \pl{for} ever. 

19 \mi{They} shall not be put to shame \pl{in} evil \pl{days,} 

in time of famine their food \pl{shall} not fail. 

20 \mi{But} all the wic\pl{ked} shall pe\pl{rish} 

and all the enemies \pl{of} the Lord. 

\mi{They} are like the beauty \pl{of} the mea\pl{dows,} 

they shall vanish, they shall va\pl{nish} like smoke. 

21 \mi{The} wicked man borrows wi\pl{thout} repay\pl{ing,} 

but the just man is ge\pl{nerous} and gives. 

22 \mi{Those} blessed by the Lord \pl{shall} own the \pl{land,} 

but those he has cursed shall be \pl{des}troyed. 

23 \mi{The} Lord guides \pl{the} steps of a \pl{man} 

and makes safe the path of \pl{one} he loves. 

24 \mi{Though} he stumble he \pl{shall} never \pl{fall} 

for the Lord holds him \pl{by} the hand. 

25 \mi{I} was young and \pl{now} I am \pl{old,} 

but I have never seen the just man \pl{for}saken 

\mi{nor} his chil\pl{dren} begging for \pl{bread.} 

26 All the day he is ge\pl{nerous} and lends 

\mi{and} his children become \pl{a} bless\pl{ing.} 

27 Then turn away from evil \pl{and} do good 

\mi{and} you shall have a \pl{home} for e\pl{ver;} 

28 for the Lord \pl{loves} justice 

\mi{and} will ne\pl{ver} forsake his \pl{friends.} 

The unjust shall be wiped out \pl{for} ever 

\mi{and} the children of the wic\pl{ked} destro\pl{yed.} 

29 The just shall inhe\pl{rit} the land; 

\mi{there} they shall \pl{live} for e\pl{ver.} 

30 The just man's mouth ut\pl{ters} wisdom 

\mi{and} his lips \pl{speak} what is \pl{right;} 

31 the law of his God is \pl{in} his heart, 

\mi{his} steps shall be saved \pl{from} stumbl\pl{ing.} 

32 The wicked man watches \pl{for} the just 

\mi{and} seeks oc\pl{ca}sion to kill \pl{him.} 

33 The Lord will not leave him in \pl{his} power 

\mi{nor} let him be con\pl{demned} when he is \pl{judged.} 

34 Then wait for the Lord, keep \pl{to} his way. 

\mi{It} is he who will free you \pl{from} the wic\pl{ked,} 

raise you up to pos\pl{ses} the land 

\mi{and} see the wic\pl{ked} destro\pl{yed.} 

35 I have seen the wicked \pl{tri}umphant, 

\mi{to}wering like a ce\pl{dar} of Le\pl{banon.} 

36 I passed by again; \pl{he} was gone. 

\mi{I} searched; he was now\pl{here} to be \pl{found.} 

37 See the just man, mark \pl{the} upright, 

\mi{for} the peaceful man a fu\pl{ture} lies in \pl{store,} 

38 but sinners shall all be \pl{des}troyed. 

\mi{No} future lies in store \pl{for} the wic\pl{ked.} 

39 The salvation of the just comes \pl{from} the Lord, 

\mi{their} stronghold in \pl{time} of dis\pl{tress.} 

40 The Lord helps them and \pl{de}livers them 

\mi{and} saves them: for their re\pl{fuge} is in \pl{him.} 

Psalm 38(37) Domine, ne in furore 


.2 \mi{O} Lord, do not rebuke me \pl{in} your an\pl{ger;} 

do not punish me, Lord, \pl{in} your rage. 

.3 \mi{Your} arrows \pl{have} sunk deep in \pl{me;} 

your hand has come down \pl{u}pon me. 

.4 \mi{Th}rough your anger \pl{all} my body is \pl{sick:} 

through my sin, there is no health \pl{in} my limbs. 

.5 \mi{My} guilt towers hig\pl{her} than my \pl{head;} 

it is a weight too hea\pl{vy} to bear. 

.6 \mi{My} wounds are foul \pl{and} fester\pl{ing,} 

the result of my \pl{own} folly. 

.7 \mi{I} am bowed and \pl{brought} to my \pl{knees.} 

I go mourning all \pl{the} day long. 

.8 \mi{All} my frame \pl{burns} with fe\pl{ver;} 

all my \pl{body} is sick. 

.9 \mi{Spent} and ut\pl{ter}ly crus\pl{hed,} 

I cry aloud in an\pl{guish} of heart. 

.10 \mi{O} Lord, you know \pl{all} my long\pl{ing:} 

my groans are not hid\pl{den} from you. 

.11 \mi{My} heart th\pl{robs,} my strength is \pl{spent;} 

the very light has gone from \pl{my} eyes. 

.12 \mi{My} friends avoid me \pl{like} a le\pl{per;} 

those closest to me stand \pl{a}far off. 

.13 \mi{Those} who plot against my \pl{life} lay sna\pl{res;} 

those who seek my ruin \pl{speak} of harm, 

\mi{plann}ing treache\pl{ry} all the day \pl{long.} 

.14 But I am like the deaf who \pl{can}not hear, 

\mi{like} the dumb un\pl{ab}le to \pl{speak.} 

.15 I am like a man who \pl{hears} nothing 

\mi{in} whose mouth \pl{is} no de\pl{fense.} 

.16 I count on \pl{you,} O Lord: 

\mi{it} is you, Lord God, \pl{who} will an\pl{swer.} 

.17 I pray: "Do not let \pl{them} mock me, 

\mi{those} who triumph \pl{if} my foot should \pl{slip."} 

.18 For I am on the point \pl{of} falling 

\mi{and} my pain is al\pl{ways} before \pl{me.} 

.19 I confess that I \pl{am} guilty 

\mi{and} my sin fills \pl{me} with dis\pl{may.} 

.20 My wanton enemies are \pl{num}berless 

\mi{and} my ly\pl{ing} foes are ma\pl{ny.} 

.21 They repay me e\pl{vil} for good 

\mi{and} attack me for seek\pl{ing} what is \pl{right.} 

.22 O Lord, do not \pl{for}sake me! 

\mi{My} God, do not \pl{stay} afar \pl{off!} 

.23 Make haste and come \pl{to} my help, 

\mi{O} Lord, my God, \pl{my} savi\pl{or!} 

Psalm 39(38) Dixi, custodiam 


.2 \mi{I} said: "I will be wat\pl{ch}ful of my \pl{ways} 

for fear I should sin with \pl{my} tongue. 

\mi{I} will put a \pl{curb} on my \pl{lips} 

when the wicked man stands \pl{be}fore me." 

.3 \mi{I} was dumb, \pl{si}lent and \pl{still.} 

His prosperity stir\pl{red} my grief. 

.4 \mi{My} heart was burn\pl{ing} within \pl{me.} 

At the thought of it, the fire \pl{bla}zed up 

\mi{and} my ton\pl{gue} burst into \pl{speech:} 

.5 "O Lord, you have shown \pl{me} my end, 

\mi{how} short is the len\pl{gth} of my \pl{days.} 

Now I know how fleeting \pl{is} my life. 

.6 \mi{You} have given me a \pl{short} span of \pl{days;} 

my life is as nothing \pl{in} your sight. 

\mi{A} mere breath, the man \pl{who} stood so \pl{firm,} 

.7 a mere shadow, the man \pl{pass}ing by; 

\mi{a} mere breath the \pl{ric}hes he \pl{hoards,} 

not knowing who \pl{will} have them." 

.8 \mi{And} now, Lord, what is \pl{there} to wait \pl{for?} 

In you rests \pl{all} my hope. 

.9 \mi{Set} me free \pl{from} all my \pl{sins,} 

do not make me the taunt \pl{of} the fool. 

.10 \mi{I} was silent, not o\pl{pen}ing my \pl{lips,} 

because this was all \pl{your} doing. 

.11 \mi{Take} away your \pl{scour}ge from \pl{me.} 

I am crushed by the blows \pl{of} your hand. 

.12 \mi{You} punish man's sins \pl{and} correct \pl{him;} 

like the moth you devour all \pl{he} treasures. 

\mi{Mor}tal man is no \pl{more} than a \pl{breath;} 

.13 O Lord, hear \pl{my} prayer. 

\mi{O} Lord, turn your \pl{ear} to my \pl{cry.} 

Do not be deaf \pl{to} my tears. 

\mi{In} your house I am \pl{a} passing \pl{guest,} 

a pilgrim, like all \pl{my} fathers. 

.14 \mi{Look} away that I may \pl{brea}the a\pl{gain} 

before I depart to \pl{be} no more. 

Psalm 40(39) Expectans, expectavi 


.2 I waited, I waited \pl{for} the Lord 

\mi{and} he \pl{stooped} down to \pl{me;} 

he \pl{heard} my cry. 

.3 \mi{He} drew me from \pl{the} deadly \pl{pit,} 

from the \pl{mi}ry clay. 

\mi{He} set my feet \pl{u}pon a \pl{rock} 

and made my \pl{foot}steps firm. 

.4 \mi{He} put a new song \pl{in}to my \pl{mouth,} 

praise \pl{of} our God. 

\mi{Many} \pl{shall} see and \pl{fear} 

and shall trust \pl{in} the Lord. 

.5 \mi{Hap}py the man \pl{who} has pla\pl{ced} 

his trust \pl{in} the Lord 

\mi{and} has not gone o\pl{ver} to the re\pl{bels} 

who fol\pl{low} false gods. 

.6 \mi{How} ma\pl{ny,} O Lord my \pl{God,} 

are the wonders \pl{and} designs 

\mi{that} you have \pl{wor}ked for \pl{us;} 

you have \pl{no} equal. 

\mi{Should} I proc\pl{laim} and speak of \pl{them,} 

they are more than \pl{I} can tell! 

.7 \mi{You} do not ask for sacrifice \pl{and} offe\pl{rings,} 

but an \pl{o}pen ear. 

\mi{You} do not ask for ho\pl{locaust} and vic\pl{tim.} 

.8 Instead, \pl{here} am I. 

\mi{In} the scroll of the book \pl{it} stands writ\pl{ten} 

.9 that I should \pl{do} your will. 

\mi{My} God, I de\pl{light} in your \pl{law} 

in the depth \pl{of} my heart. 

.10 \mi{Your} jus\pl{tice} I have proc\pl{laimed} 

in the great \pl{as}sembly. 

\mi{My} lips I \pl{have} not sea\pl{led;} 

you know \pl{it,} O Lord. 

.11 \mi{I} have not hidden your jus\pl{tice} in my \pl{heart} 

but declared your \pl{faith}ful help. 

\mi{I} have not hidden \pl{your} love and your \pl{truth} 

from the great \pl{as}sembly. 

.12 \mi{O} Lord, you \pl{will} not wi\pl{thhold} 

your compas\pl{sion} from me. 

\mi{Your} merci\pl{ful} love and your \pl{truth} 

will al\pl{ways} guard me. 

.13 \mi{For} I am be\pl{set} with e\pl{vils} 

too many to \pl{be} counted. 

\mi{My} sins have fal\pl{len} upon \pl{me} 

and my \pl{sight} fails me. 

\mi{They} are more than the \pl{hairs} of my \pl{head} 

and \pl{my} heart sinks. 

.14 \mi{O} Lord, come \pl{to} my res\pl{cue;} 

Lord, come \pl{to} my aid. 

.15 \mi{O} let there be shame \pl{and} confu\pl{sion} 

on those who \pl{seek} my life. 

\mi{O} let them turn back \pl{in} confu\pl{sion,} 

who delight \pl{in} my harm. 

.16 \mi{Let} them be ap\pl{palled,} covered with \pl{shame,} 

who jeer \pl{at} my lot. 

.17 \mi{O} let there be rejoic\pl{ing} and glad\pl{ness} 

for all \pl{who} seek you. 

\mi{Let} them ever \pl{say:} "The Lord is \pl{great",} 

who love your \pl{sav}ing help. 

.18 \mi{As} for me, \pl{wret}ched and \pl{poor,} 

the Lord \pl{thinks} of me. 

\mi{You} are my \pl{res}cuer, my \pl{help,} 

O God, do \pl{not} delay. 

Psalm 41(40) Beatus qui intelligit 


.2 Happy the man who considers the poor \pl{and} the weak. 

\mi{The} Lord will save him in the \pl{day} of e\pl{vil,} 

.3 will guard him, give him life, make him happy \pl{in} the land 

\mi{and} will not give him up to the \pl{will} of his \pl{foes.} 

.4 The Lord will help him on his \pl{bed} of pain, 

\mi{he} will bring him back from \pl{sick}ness to \pl{health.} 

.5 As for me, I said: "Lord, have mer\pl{cy} on me, 

\mi{heal} my soul for I have \pl{sinned} against \pl{you."} 

.6 My foes are speaking evil \pl{a}gainst me. 

\mi{"how} long before he dies and his \pl{name} be for\pl{gotten?"} 

.7 They come to visit me and speak \pl{em}pty words, 

\mi{their} hearts full of malice, they sp\pl{read} it ab\pl{road.} 

.8 My enemies whisper together \pl{a}gainst me. 

\mi{They} all weigh up the e\pl{vil} which is on \pl{me.} 

.9 "Some deadly thing has fastened \pl{u}pon him, 

\mi{he} will not rise a\pl{gain} from where he \pl{lies."} 

.10 Thus even my friend, in whom \pl{I} trusted, 

\mi{who} ate my bread, has \pl{turned} against \pl{me.} 

.11 But you, O Lord, have mer\pl{cy} on me. 

\mi{Let} me rise once more and I \pl{will} repay \pl{them.} 

.12 By this I shall know that you \pl{are} my friend, 

\mi{if} my foes do not shout in tri\pl{umph} over \pl{me.} 

.13 If you uphold me I shall \pl{be} unharmed 

\mi{and} set in your pre\pl{sence} for ever \pl{more.} 

[.14] Blessed be the Lord, the God of \pl{Is}rael 

\mi{from} age to age. \pl{A}men. A\pl{men.} 

