\begin{center}\normalsize JANUARY 25\\
\footnotesize CONVERSION OF ST. PAUL\\
\footnotesize Apostle\\
\footnotesize Feast\\
\footnotesize Common of the Apostles p.   except:\\
\end{center}

\hangindent=\parindent \small{PRAYER 
O God, who taught the whole world
through the preaching of the blessed Apostle Paul,
draw us, we pray, nearer to you
through the example of him whose conversion we celebrate today,
and so make us witnesses to your truth in the world.
Through our Lord Jesus Christ, your Son,
who lives and reigns with you in the unity of the Holy Spirit,
one God, for ever and ever.\\}
 
\begin{flushleft}\normalsize LAUDS\\\end{flushleft}

\hangindent=\parindent \small{INVITATORY}
\begin{center}
\textit{Come, let us worship God, on the feast of the conversion of Saint Paul.\\}
\end{center}

\hangindent=\parindent \small{READING} Acts 26:16-18 \textbf{I have appeared to you for this purpose, to
appoint you to serve and bear witness to the things in which you
have seen me and to those in which I will appear to you, delivering
you from the people and from the Gentiles to whom I send you
to open their eyes, that they may turn from darkness to light and
from the power of Satan to God, that they may receive forgiveness
of sins and a place among those who are sanctified by faith in me.\\}
 
\hangindent=\parindent \small{BENEDICTUS  Let us celebrate the conversion of Saint Paul the apostle.
He was transformed from being a persecutor of Christ into a vessel
of his grace.\\}
 
\begin{flushleft}\normalsize SEXT\\\end{flushleft}

\hangindent=\parindent \small{PSALMODY:}\\
\hangindent=\parindent  of the weekday\vspace{0.5em}

\hangindent=\parindent \small{READING} 1 Tim 1:16 \textbf{I received mercy for this reason, that in me, as
the foremost, Jesus Christ might display his perfect patience for an
example to those who were to believe in him for eternal life.
I will glorify your name forever, Lord.
- So great has been your compassion toward me.}
 
\begin{flushleft}\normalsize VESPERS\\\end{flushleft}

\hangindent=\parindent \small{READING} 1 Cor 15:9-10 \textbf{I am the least of the apostles, unfit to be called
an apostle, because I persecuted the church of God. But by the
grace of God I am what I am, and his grace toward me was not in
vain. On the contrary, I worked harder than any of them, though it
was not I, but the grace of God which is with me.\\}
 
\hangindent=\parindent \small{MAGNIFICAT  Holy apostle Paul, preacher of truth and teacher of the
Gentiles, intercede for us with God, who chose you.\\}
 
 

