\begin{center}\normalsize AUGUST 29\\
\footnotesize THE PASSION OF ST. JOHN THE BAPTIST\\
\footnotesize Martyr \\
\footnotesize Memorial\\
\footnotesize From the common of one Martyr p.   except:\\
\end{center}

\hangindent=\parindent \small{PRAYER 
O God, who willed that Saint John the Baptist
should go ahead of your Son
both in his birth and in his death,
grant that, as he died a Martyr for truth and justice,
we, too, may fight hard
for the confession of what you teach.
Through our Lord Jesus Christ, your Son,
who lives and reigns with you in the unity of the Holy Spirit,
one God, for ever and ever.\\}
 
\begin{flushleft}\normalsize LAUDS\\\end{flushleft}

\hangindent=\parindent \small{PSALMODY:}\\
\hangindent=\parindent  OT 24\vspace{0.5em}

\hangindent=\parindent \small{READING} Is 49:1-2 \textbf{Listen to me, O coastlands, and hearken, you
peoples from afar. The Lord called me from the womb, from the
body of my mother he named my name. He made my mouth like
a sharp sword, in the shadow of his hand he hid me; he made me a
polished arrow, in his quiver he hid me away.\\}
 
\hangindent=\parindent \small{BENEDICTUS  The friend of the bridegroom, who waits and listens
for his return, rejoices when he hears his voice; so now my joy is
complete.\\}
 
\begin{flushleft}\normalsize VESPERS\\\end{flushleft}

\hangindent=\parindent \small{READING} Acts 13:23-25 \textbf{Of David’s posterity God has brought to Israel a
Savior, Jesus, as he promised. Before his coming John had preached
a baptism of repentance to all the people of Israel. And as John was
finishing his course, he said, ‘What do you suppose that I am? I am
not he. No, but after me one is coming, the sandals of whose feet I
am not worthy to untie.’\\}
 
\hangindent=\parindent \small{MAGNIFICAT  I am not the Christ: I have been sent before him to prepare
his way. He must increase, and I must decrease.\\}
 
