\begin{center}\noindent\textsc{\small{Christmas Season\\}}\end{center}
\end{center}

Hymn I
\begin{cverse}
Christe, redemptor omnium,\\
Ex Patre, Patris Unice,\\
Solus ante principium\\
Natus ineffabiliter.\\!

Tu lumen, tu splendor Patris,\\
Tu spes perennis omnium,\\
Intende quas fundunt preces\\
Tui per orbem servuli.\\!

Salutis auctor, recole\\
Quod nostri quondam corporis,\\
Ex illibata Virgine\\
Nascendo, formam sumpseris.\\!

Hic praesens testatur dies,\\
Currens per anni circulum,\\
Quod solus a sede Patris\\
Mundi salus adveneris;\\!

Hunc caelum, terra, hunc mare,\\
Hunc omne quod in eis est,\\
Auctorem adventus tui\\
Ludat exsultans cantico.\\!

Nos quoque, qui sancto tuo\\
Redempti sumus sanguine,\\
Ob diem natalis tui\\
Hymnum novum concinimus\\!

Jesus, tibi sit gloria,\\
Qui natus es de Virgine,\\
Cum Patre et almo Spiritu,\\
In sempiterna saecula. Amen.\\!
\end{cverse}

Hymn II
\begin{cverse}
Come with rejoicing,\\
Come with gladness,\\
Come, all people of the erath,\\
See what God does for us.\\!

Our God comes and takes on flesh from the Virgin,\\
The Seraphim and Cherubim sing of the Virgin and Son;\\
All creation glorifies the Mother of God,\\
From East to West.\\!

He is God, truly  God, He is God, Word of the Father,\\
He is God, Son of the Virgin;\\
Jesus Christ, whose name is our salvation,\\
Jesus who assumed flesh in the Virgin.\\!

For all people and for every faithful nation,\\
The sole source of salvation springs forth in Mary;\\
Rejoice, O veritable Spouse\\
Who give birth to Him in whom we are made one.\\!

Let us give glory to God the Father,\\
Glory to His Son Jesus Christ the Lord,\\
And glory to the Spirit Counselor\\
Forever and ever. Amen.\\!
\end{cverse}

Hymn III
\begin{cverse}
Splendor that flowed from the bosom of the Father,\\
Light born of Light,\\
Before the world was born,\\
You shown in the darkness.\\!

We worship you, Beloved Son,\\
Who was show every favor,\\
Upon you rests the grace\\
Of the Father who sent you.\\!

You come into the depths of our night\\
For all peple in this world,\\
You are the source of life\\
And the true light.\\!

Glory to you, O Father Most Holy,\\
Glory to you, O Only Son,\\
With the Spirit, the Comforter,\\
Both now and forever. Amen.\\!
\end{cverse}

Hymn IV
\begin{cverse}
Unto us a Child is given,\\
Christ our Savior bring release;\\
Counselor, Eternal Father,\\
God made man, and Prince of Peace.\\!

Born of Mary, gentle virgin,\\
By the Spirit of the Lord;\\
From eternal ages spoken:\\
This the mighty Father's Word.\\!

Love and truth in him shall flower,\\
From his strength their vigor take.\\
Branches that are bare shall blossom;\\
Joy that slept begins to wake.\\!

Praise the everlasting Father,\\
And the Word, his only Son;\\
Praise them with the Holy Spirit,\\
Perfect Trinity in One. Amen.\\!
\end{cverse}
-----
DECEMBER 25
CHRISTMAS
SOLEMNITY

\begin{flushleft}\normalsize FIRST VESPERS\\\end{flushleft}
\hangindent=\parindent \small{\uppercase{HYMN} p.  ?\\}

\hangindent=\parindent \small{PSALMODY}
\begin{center}
\begin{tabular}{ l l }
Ps 112 &  - Ps 147 - Ps 8 - NT 5\\
\hangindent=\parindent \small{READING}    Gal &  4:4-5 \textbf{   But when the fullness of time had come, God sent his Son, born of a woman, born under the law, to ransom those under the law, so that we might receive adoption.\\\\}
\end{tabular}
\end{center}		

\hangindent=\parindent \small{MAGNIFICAT 	When the sun rises in the morning sky, you will see the King of kings coming forth from the Father like a radiant bridegroom from the bridal chamber.\\}

\hangindent=\parindent \small{PRAYER 	O God, who gladden us year by year as we wait in hope for our redemption, grant that, just as we joyfully welcome your Only Begotten Son as our Redeemer, we may also merit to face him confidently when he comes again as our Judge. Who lives and reigns with you in the unity of the Holy Spirit, one God, for ever and ever.}

\begin{flushleft}\normalsize VIGILS\\\end{flushleft}
\hangindent=\parindent \small{PSALMODY}
\begin{center}
\begin{tabular}{ l l }
Ps 2 &  - Ps 18 - Ps 44 - OT 20 - OT 24 - OT 32\\
\end{tabular}
\end{center}		

\hangindent=\parindent \small{PRAYER 	O God, who wonderfully created the dignity of human nature and still more wonderfully restored it, grant, we pray, that we may share in the divinity of Christ, who humbled himself to share in our humanity. Who lives and reigns with you in the unity of the Holy Spirit, one God, for ever and ever.}

\begin{flushleft}\normalsize LAUDS\\\end{flushleft}
\hangindent=\parindent \small{INVITATORY}
\begin{center}
\textit{Christ is born for us; come, let us adore him.\\}
\end{center}

\hangindent=\parindent \small{PSALMODY}
\begin{center}
\begin{tabular}{ l l }
Ps 62 &  - OT 41 - Ps 148 - Ps 149 - Ps 150 (Per.)\\
\end{tabular}
\end{center}		

\hangindent=\parindent \small{READING}    Heb 1:1-2 \textbf{   In times past, God spoke in partial and various ways to our ancestors through the prophets; in these last days, he spoke to us through a son, whom he made heir of all things and through whom he created the unicverse.\\}

\hangindent=\parindent \small{BENEDICTUS 	Glory to God in the highest, and peace to his people on earth, alleluia.\\}

\hangindent=\parindent \small{PRAYER 	Grant, we pray, almighty God, that, as we are bathed in the new radiance of your incarnate Word, the light of faith, which illumines our minds, may also shine through in our deeds. Through our Lord Jesus Christ, your Son, who lives and reigns with you in the unity of the Holy Spirit, one God, for ever and ever.}

\begin{flushleft}\normalsize SEXT\\\end{flushleft}
\hangindent=\parindent \small{PSALMODY}
\begin{center}
\begin{tabular}{ l l }
Ps 86 &  - Ps 95\\
\end{tabular}
\end{center}		

\hangindent=\parindent \small{READING}    1 Jn 4:9 \textbf{    In this way the love of God was revealed to us: God sent his only Son into the world so that we might have life through him.}
All the ends of the earth, alleluia.
-Have seen the saving power of God, alleluia.

(use prayer of Second Vespers)

\begin{flushleft}\normalsize SECOND VESPERS\\\end{flushleft}
\hangindent=\parindent \small{\uppercase{HYMN} p.  ?\\}
Psalmody
Ps 109 - Ps 129 - Ps 84 - NT 6

\hangindent=\parindent \small{READING}    1 Jn 1:1-3 \textbf{   What was from the beginning, what we have heard, what we have seen with our eyes, what we looked upon and touched with our hands concerns the Word of life for the life was made visible; we have seen it and testify to it and proclaim to you the eternal life that was with the Father and was made visible to us what we have seen and heard we proclaim now to you, so that you too may have fellowship with us; for our fellowship is with the Father and with his Son, Jesus Christ.\\}

\hangindent=\parindent \small{MAGNIFICAT 	Christ the Lord is born today; today, the Savior has appeared. Earth echoes songs of angel choirs, archangels' joyful praise. Today on earth his friends exult: Glory to God in the highest, alleluia.\\}

\hangindent=\parindent \small{PRAYER 	O God, who wonderfully created the dignity of human nature and still more wonderfully restored it, grant, we pray, that we may share in the divinity of Christ, who humbled himself to share in our humanity. Who lives and reigns with you in the unity of the Holy Spirit, one God, for ever and ever.}
-----
HOLY FAMILY
Sunday in the Octave of Christmas*
FEAST

\begin{flushleft}\normalsize FIRST VESPERS\\\end{flushleft}
\hangindent=\parindent \small{\uppercase{HYMN} p.  ?\\}
\hangindent=\parindent \small{PSALMODY}
\begin{center}
\begin{tabular}{ l l }
Ps 112 &  - Ps 147 - Ps 8 - NT 4\\
\end{tabular}
\end{center}		

\hangindent=\parindent \small{READING}    2 Cor 8:9 \textbf{   For you know the gracious act of our Lord Jesus Christ, that for your sake he became poor although he was rich, so that by his poverty you might become rich. \\}

\hangindent=\parindent \small{MAGNIFICAT 	The child Jesus remained in Jerusalem, and his parents did not know it. They thought he was in the group of travelers and looked for him among their relatives and friends.\\}

\hangindent=\parindent \small{PRAYER 	O God, who were please to give us the shining example of the Holy Family, graciously grant that we may imitate them in practicing the virtues of family life and in the bonds of charity, and so, in the joy of your house, delight one day in eternal rewards. Through our Lord Jesus Christ, your Son, who lives and reigns with you in the unity of the Holy Spirit, one God, for ever and ever.}

\begin{flushleft}\normalsize VIGILS\\\end{flushleft}
\hangindent=\parindent \small{PSALMODY}
\begin{center}
\begin{tabular}{ l l }
Ps 45 &  - Ps 86 - Ps 84 - OT 18 - OT 20 - OT 32\\
\end{tabular}
\end{center}		

\begin{flushleft}\normalsize LAUDS\\\end{flushleft}
\hangindent=\parindent \small{INVITATORY}
\begin{center}
\textit{Come, let us worship Christ, the Son of God,\\}
\textit{-Who was obedient to Mary and Joseph.\\}
\end{center}

\hangindent=\parindent \small{PSALMODY}
\begin{center}
\begin{tabular}{ l l }
Ps 62 &  - Ps 23 - OT 41 - Ps 149 - Ps 150 (mode 7)\\
\end{tabular}
\end{center}		

\hangindent=\parindent \small{READING}    Dt 5:16 \textbf{   Honor your father and your mother, as the LORD, your God, has commanded you, that you may have a long life and that you may prosper in the land the LORD your God is giving you. \\}

\hangindent=\parindent \small{BENEDICTUS 	Lord, give us light through the example of your family and guide our feet into the way of peace.\\}

\begin{flushleft}\normalsize SEXT\\\end{flushleft}
\hangindent=\parindent \small{PSALMODY}
\begin{center}
\begin{tabular}{ l l }
Ps 117 &  - Ps 118 XIII-XIV\\
\end{tabular}
\end{center}		

\hangindent=\parindent \small{READING}    Col 3:14-15 \textbf{   And over all these put on love, that is, the bond of perfection. And let the peace of Christ control your hearts, the peace into which you were also called in one body. And be thankful.}
I am a poor man. I have worked since my youth.
-I was raised up only to be brought low and left bewildered.

\begin{flushleft}\normalsize SECOND VESPERS\\\end{flushleft}
\hangindent=\parindent \small{\uppercase{HYMN} p.  ?\\}
\hangindent=\parindent \small{PSALMODY}
\begin{center}
\begin{tabular}{ l l }
Ps 126 &  - Ps 127 - Ps 44 - NT 4\\
\end{tabular}
\end{center}		

\hangindent=\parindent \small{READING}    Phil 2:6-7 \textbf{   Who, though he was in the form of God, did not regard equality with God something to be grasped. Rather, he emptied himself, taking the form of a slave, coming in human likeness; and found human in appearance.\\}

\hangindent=\parindent \small{MAGNIFICAT 	Son, why have you done this to us? Think what anguish your father and I have endured looking for you. But why did you look for me? Did you know know that I had to be in my Father's house?\\}

For the Benedictus between the 26th and 29th, see The Proper of Saints
-----
DECEMBER 26
Office of Saint Stephen p. ? except vespers
First Vespers of Saint John p. ?

\hangindent=\parindent \small{MAGNIFICAT 	When all things are made new, and the Son of Man is enthroned in majesty, you will sit in judgment over the twelve tribes of Israel.\\}

DECEMBER 27
Office of Saint John p. ?

\hangindent=\parindent \small{MAGNIFICAT 	Virgin Mary, all that the prophets foretold of Christ has been fulfilled through you: as a virgin, you conceived, and after you gave birth, a virgin you remained.\\}

DECEMBER 28
Office of the Holy Innocents p. ?
\begin{flushleft}\normalsize (VESPERS\\\end{flushleft} taken from Second Vespers of the Nativity)

\hangindent=\parindent \small{READING}    Eph 2:3b-5 \textbf{   We were by nature children of wrath, like the rest. But God, who is rich in mercy, because of the great love he had for us, even when we were dead in our transgressions, brought us to life with Christ (by grace you have been saved).\\}

\hangindent=\parindent \small{MAGNIFICAT 	The holy Virgin gave birth to God who became for us the frail, tender baby she nursed at her breast. Let us worship the Lord who comes to save us.\\}
-----
FROM DECEMBER 29 TO 31
-For Sext and Vigils, take the psalmody proper to the week (IV or I).
-For Lauds and Vesers, everything is taken from Christmas day except the READING and the PRAYER.

DECEMBER 29
5th day in the Octave of Christmas

\hangindent=\parindent \small{INVITATORY	}
\begin{center}
\textit{Christ is born for us; come, let us adore him.\\}
\end{center}

\begin{flushleft}\normalsize LAUDS\\\end{flushleft}
\hangindent=\parindent \small{READING}    Heb 1:1-2 \textbf{   In times past, God spoke in partial and various ways to our ancestors through the prophets; in these last days, he spoke to us through a son, whom he made heir of all things and through whom he created the unicverse.\\}

\hangindent=\parindent \small{BENEDICTUS 	The shepherds said to one another: Let us make our way to Bethlehem and see for ourselves this thing which the Lord has revealed to us.\\}

\hangindent=\parindent \small{PRAYER 	Almighty and invisible God, who dispersed the darkness of this world by the coming of your light, look, we pray, with serene countenance upon us, that we may acclaim with fitting praise the greatness of the Nativity of your Only Begotten Son. Who lives and reigns with you in the unity of the Holy Spirit, one God, for ever and ever.}

\begin{flushleft}\normalsize SEXT\\\end{flushleft}
\hangindent=\parindent \small{READING}    1 Jn 4:9 \textbf{    In this way the love of God was revealed to us: God sent his only Son into the world so that we might have life through him.}
All the ends of the earth, alleluia.
-Have seen the saving power of God, alleluia.

\begin{flushleft}\normalsize VESPERS\\\end{flushleft}
\hangindent=\parindent \small{\uppercase{HYMN} p.  ?\\}
\hangindent=\parindent \small{READING}    1 Jn 1:1-3 \textbf{   What was from the beginning, what we have heard, what we have seen with our eyes, what we looked upon and touched with our hands concerns the Word of life—for the life was made visible; we have seen it and testify to it and proclaim to you the eternal life that was with the Father and was made visible to us—what we have seen and heard we proclaim now to you, so that you too may have fellowship with us; for our fellowship is with the Father and with his Son, Jesus Christ.\\}

\hangindent=\parindent \small{MAGNIFICAT 	The King of heaven humbled himself to be born of a virgin, that he might restore man to the kingdom he had lost.\\}

DECEMBER 30
6th day in the Octave of Christmas

\hangindent=\parindent \small{INVITATORY	}
\begin{center}
\textit{Christ is born for us; come, let us adore him.\\}
\end{center}

\begin{flushleft}\normalsize LAUDS\\\end{flushleft}
\hangindent=\parindent \small{READING}    Is 9:6 \textbf{   His dominion is vast and forever peaceful, upon David’s throne, and over his kingdom, which he confirms and sustains by judgment and justice, both now and forever. The zeal of the LORD of hosts will do this!\\}

\hangindent=\parindent \small{BENEDICTUS  (before Epiphany)\\}
At the Lord's birth the choirs of angels sang: Blessed be our God enthroned as King and blessed be the Lamb.
(Monday after Epiphany)
The wie men came from the East to adore the Lord in Bethlehem. Opening their treasures, they offered him three precious gifts: gold for the great King, frankincense for the true God, and myrrh for his burial, alleluia.

\hangindent=\parindent \small{PRAYER 	Grant, we pray, almighty God, that the newness of the Nativity in the flesh of your Only Begotten Son may set us free, for ancient servitude holds us bound beneath the yoke of sin. Through our Lord Jesus Christ, your Son, who lives and reigns with you in the unity of the Holy Spirit, one God, for ever and ever.}

\begin{flushleft}\normalsize SEXT\\\end{flushleft}
\hangindent=\parindent \small{READING}    Is 12:5-6 \textbf{   Sing praise to the LORD for he has done glorious things; let this be known throughout all the earth. Shout with exultation, City of Zion, for great in your midst is the Holy One of Israel!}
All the ends of the earth, alleluia.
-Have seen the saving power of God, alleluia.

\begin{flushleft}\normalsize VESPERS\\\end{flushleft}
\hangindent=\parindent \small{\uppercase{HYMN} p.  ?\\}
\hangindent=\parindent \small{READING}    2 Pet 1:3-4 \textbf{   His divine power has bestowed on us everything that makes for life and devotion, through the knowledge of him who called us by his own glory and power. Through these, he has bestowed on us the precious and very great promises, so that through them you may come to share in the divine nature, after escaping from the corruption that is in the world because of evil desire.\\}

\hangindent=\parindent \small{MAGNIFICAT  (before the Epiphany)\\}
We sing your praises, holy Mother of God: you gave birth to our Savior, Jesus Christ; watch over all who honor you.
(Monday after the Epiphany)
When they saw the star the Magi were filled with great joy; entering the house, they offered their gifts to the Lord: gold, frankincense and myrrh.

DECEMBER 31
7th day in the octave of Christmas

\begin{flushleft}\normalsize LAUDS\\\end{flushleft}
\hangindent=\parindent \small{READING}    Is 4:2-3 \textbf{   On that day, the branch of the LORD will be beauty and glory, and the fruit of the land will be honor and splendor for the survivors of Israel. Everyone who remains in Zion, everyone left in Jerusalem will be called holy: everyone inscribed for life in Jerusalem.\\}

\hangindent=\parindent \small{BENEDICTUS 	Suddenly there was with the angel a great company of the heavenly host, praising God and singing: Glory to God in the highest and peace to his people on earth, alleluia.\\}
(Tuesday after the Epiphany)
The wise men offered gifts of gold, frankincense and myrrh to the Lord, the Son of God and King most high, alleluia.

\hangindent=\parindent \small{PRAYER 	Almighty ever-living God, who in the Nativity of your Son established the beginning and fulfillment of all religion, grant, we pray, that we may be numbered among those who belong to him, in whom is the fullness of human salvation. Who lives and reigns with you in the unity of the Holy Spirit, one God, for ever and ever.}

\begin{flushleft}\normalsize SEXT\\\end{flushleft}
\hangindent=\parindent \small{READING}    Is 48:20 \textbf{   Go forth from Babylon, flee from Chaldea! With shouts of joy declare this, announce it; make it known to the ends of the earth, say: “The LORD has redeemed his servant Jacob.}
All the ends of the earth, alleluia.
-Have seen the saving power of God, alleluia.
-----
JANUARY 1
MARY, MOTHER OF GOD
SOLEMNITY

\begin{flushleft}\normalsize FIRST VESPERS\\\end{flushleft}

Hymn
\begin{cverse}
Rejoice, O holy Mother,\\
You who gave birth to the King of kings,\\
Who throughout the ages holds in His hands\\
The heavens, the earth, and the entire unicverse.\\!

The divine king to whom the boundless empire\\
Belongs for the duration of time\\
Gave to your blessed womb\\
The joys of a Mother and the honor of a Virgin.\\!

No woman is your equal,\\
Either in ages past or in future years,\\
You who alone are full of grace\\
Who found favor with Christ our Savior.\\!

O Virgin, you were deemed worthy\\
To give birth to the God who triumphs over evil,\\
The enemy trembles for he has seen mercy,\\
The wolf flees for the Lamb is victorious.\\!

Let us give glory to the Everlasting Father,\\
To his Son who was birn of a Virgin,\\
To the Spirit who overshadowed her,\\
Forever and ever. Amen.\\!
\end{cverse}

\hangindent=\parindent \small{PSALMODY}
\begin{center}
\begin{tabular}{ l l }
From the &  common of the Blessed Virgin Mary p. ?\\
\hangindent=\parindent \small{READING}    Gal &  4:4-5 \textbf{   But when the fullness of time had come, God sent his Son, born of a woman, born under the law, to ransom those under the law, so that we might receive adoption.\\\\}
\end{tabular}
\end{center}		

\hangindent=\parindent \small{MAGNIFICAT 	In his great love for us, God sent his Son in the likeness of our sinful nature, born of a woman and subject to the law, alleluia.\\}
(Tuesday after the Epiphany)
Christ, you are Light from Light; when you appeared on the earth, the wise men offered their gifts to you, alleluia.

\hangindent=\parindent \small{PRAYER 	O God, who through the fruitful virginity of Blessed Mary bestowed on the human race the grace of eternal salvation, rant, we pray, that we may experience the intercession of her, through whom we were found worthy to receive the author of life, our Lord JEsus Christ, your Son. Who lives an reigns with you in the unity of the Holy Spirit, one God, for ever and ever.}

\begin{flushleft}\normalsize VIGILS\\\end{flushleft}
\hangindent=\parindent \small{PSALMODY}
\begin{center}
\begin{tabular}{ l l }
Ps 23 & \\
\end{tabular}
\end{center}		

need revised antiphons (sheet music)

\begin{flushleft}\normalsize LAUDS\\\end{flushleft}
\hangindent=\parindent \small{INVITATORY}
\begin{center}
\textit{Let us celebrate the motherhood of the Virgin Mary;\\}
\textit{let us worhship her Son, Christ the Lord.\\}
\end{center}

\hangindent=\parindent \small{PSALMODY}
\begin{center}
\begin{tabular}{ l l }
Ps 18 &  - Ps 47 - OT 18 - Ps 149 - Ps 150 (mode 7)\\
\end{tabular}
\end{center}		

\hangindent=\parindent \small{READING}    Mic 5:2, 3, 4a \textbf{   \\}

\hangindent=\parindent \small{BENEDICTUS 	Marvelous is the mystery proclaimed today: man's nature is made new as God becomes man; he remains what he was and becomes what he was not. Yet each nature stays distinct and for ever undivided.\\}

\begin{flushleft}\normalsize SEXT\\\end{flushleft}
PSALMODY of Sunday Week II
If a weekday: Ps 123 - Ps 124

\hangindent=\parindent \small{READING}    Zep 9:9 \textbf{   For then I will make pure the speech of the peoples, that they all may call upon the name of the LORD, to serve him with one accord.}
All the ends of the earth, alleluia.
-Have seen the saving power of God, alleluia.

\begin{flushleft}\normalsize SECOND VESPERS\\\end{flushleft}
HYMN from First Vespers

\hangindent=\parindent \small{PSALMODY}
\begin{center}
\begin{tabular}{ l l }
Ps 121- &  Ps 126 - Ps 131 - NT 4\\
\end{tabular}
\end{center}		

need revised antiphons (sheet music)

\hangindent=\parindent \small{READING}    Gal 4:4-5 \textbf{   But when the fullness of time had come, God sent his Son, born of a woman, born under the law, to ransom those under the law, so that we might receive adoption.\\}

\hangindent=\parindent \small{MAGNIFICAT 	Blessed is the womb that bore you, O Christ, and the breast that nursed you, Lord and Savior of the world, alleluia.\\}
-----
SECOND SUNDAY AFTER CHRISTMAS

PSALMODY of Sunday II
All HYMNS and READING from the Nativity p. ?

\begin{flushleft}\normalsize FIRST VESPERS\\\end{flushleft}

\hangindent=\parindent \small{READING}    1 Jn 5:20 \textbf{    We also know that the Son of God has come and has given us discernment to know the one who is true. And we are in the one who is true, in his Son Jesus Christ. He is the true God and eternal life.\\}

\hangindent=\parindent \small{MAGNIFICAT 	By the power of the Holy Spirit the Virgin Mary has conceived a child; she carries in her womb this mystery which she cannot comprehend.\\}

\hangindent=\parindent \small{INVITATORY}
\begin{center}
\textit{Christ has been born for us; come, let us adore him.\\}
\textit{*If the Epiphany is celebrated on January 6th\\}
\end{center}

\hangindent=\parindent \small{BENEDICTUS 	The Virgin believed in the Lord's promise: as a virgin she gave birth to the Word made man, and yet she remained a virgin. Let us praise her and say: Blessed are you among women.\\}

\hangindent=\parindent \small{PRAYER 	Almighty ever-living God, splendor of faithful souls, graciously be pleased to fill the world with you glory, and show yourself to all people by the radiance of your light. Through our Lord Jesus Christ, your Son, who lives and reigns with you in the unity of the Holy Spirit, one God, for ever and ever.}

\begin{flushleft}\normalsize SECOND VESPERS\\\end{flushleft}
\hangindent=\parindent \small{\uppercase{HYMN} p.  ?\\}

\hangindent=\parindent \small{MAGNIFICAT 	Blessed is the womb that bore the Son of the Eternal Father, and blessed are the breasts that nursed Christ the Lord.\\}
-----
FROM JANUARY 2 TO THE EPIPHANY
PSALMODY of WEEK II

\begin{center}
\normalsize MONDAY
\end{center}

\begin{flushleft}\normalsize LAUDS\\\end{flushleft}
\hangindent=\parindent \small{INVITATORY}
\begin{center}
\textit{Sing to the Lord and bless his name.\\}
\textit{-Proclaim his saving love day after day.\\}
\end{center}

\hangindent=\parindent \small{READING}    Is 49:8-9 \textbf{   Thus says the LORD: in a time of favor I answer you, on the day of salvation I help you; I form you and set you as a covenant for the people, to restore the land and allot the devastated heritages, to say to the prisoners: Come out! To those in darkness: Show yourselves! Along the roadways they shall find pasture, on every barren height shall their pastures be.\\}

\hangindent=\parindent \small{BENEDICTUS 	Helpless, he lay in a manger; glorious, he shone in the heavens. Humbled, he lived among men; eternal, he dwelt with the Father.\\}
(Wednesday after the Epiphany)
We have seen his star in the East and have come with gifts to worship the Lord.

\hangindent=\parindent \small{PRAYER 	Grant your people, O Lord, we pray, unshakable strength of faith, so that all who profess that your Only Begotten Son is with you for ever in your glory and was born of the Virgin Mary in a body truly like our own may be freed from present trials and given a place in abiding gladness. Through our Lord Jesus Christ, your Son, who lives and reigns with you in the unity of the Holy Spirit, one God, for ever and ever.}

\begin{flushleft}\normalsize SEXT\\\end{flushleft}
\hangindent=\parindent \small{READING}    Rev 21:23-24 \textbf{   The city had no need of sun or moon to shine on it, for the glory of God gave it light, and its lamp was the Lamb. The nations will walk by its light, and to it the kings of the earth will bring their treasure.}
All the ends of the earth, alleluia.
-Have seen the saving power of God, alleluia.

\begin{flushleft}\normalsize VESPERS\\\end{flushleft}
\hangindent=\parindent \small{\uppercase{HYMN} p.  ?\\}
\hangindent=\parindent \small{READING}    Col 1:13-15 \textbf{   He delivered us from the power of darkness and transferred us to the kingdom of his beloved Son, in whom we have redemption, the forgiveness of sins.\\}

\hangindent=\parindent \small{MAGNIFICAT 	O radiant child! You brought healing to human life as you came forth from the womb of Mary, your mother, like the bridegroom from his marriage chamber.\\}
(Wednesday after the Epiphany)
Herod questioned the Magi: What is this sign of which you speak, this sign of a newborn king? We saw a brilliant star in the heavens; its splendor filled the world.

\begin{center}
\normalsize TUESDAY
\end{center}

\begin{flushleft}\normalsize LAUDS\\\end{flushleft}
\hangindent=\parindent \small{READING}    Is 62:11-12 \textbf{   The LORD has proclaimed to the ends of the earth: Say to daughter Zion, “See, your savior comes! See, his reward is with him, his recompense before him.” They shall be called “The Holy People,” “The Redeemed of the LORD.” And you shall be called “Cared For,” “A City Not Forsaken.”\\}

\hangindent=\parindent \small{BENEDICTUS 	The Word was made man; full of grace and truth, he lived among us. From his fullness we all have received gift upon gift of his love, alleluia.\\}
(Thursday after the Epiphany)
All people, bearing gifts, will come from afar, alleluia.

\hangindent=\parindent \small{PRAYER 	O God, who in the blessed childbearing of the holy Virgin Mary kept the flesh of your Son free from the sentence incurred by the human race, grant, we pray, that we, who have been taken up into this new creation, may be freed from the ancient taint of sin. Through our Lord Jesus Christ, your Son, who lives and reigns with you in the unity of the Holy Spirit, one God, for ever and ever.}

\begin{flushleft}\normalsize SEXT\\\end{flushleft}
\hangindent=\parindent \small{READING}    Is 9:1 \textbf{   The people who walked in darkness have seen a great light; upon those who lived in a land of gloom a light has shone.}
All the ends of the earth, alleluia.
-Have seen the saving power of God, alleluia.

\begin{flushleft}\normalsize VESPERS\\\end{flushleft}
\hangindent=\parindent \small{\uppercase{HYMN} p.  ?\\}
\hangindent=\parindent \small{READING}    1 Jn 1:5b, 7 \textbf{   God is light, and in him there is no darkness at all. But if we walk in the light as he is in the light, then we have fellowship with one another, and the blood of his Son Jesus cleanses us from all sin.\\}

\hangindent=\parindent \small{MAGNIFICAT 	Let us dance with delight in the Lord and let our hearts be filled with rejoicing, for eternal salvation has appeared on the earth, alleluia.\\}
(Thursday after the Epiphany)
The people of Saba shall come bringing gold, frankincense and myrrh, alleluia.

\begin{center}
\normalsize WEDNESDAY
\end{center}

\begin{flushleft}\normalsize LAUDS\\\end{flushleft}
\hangindent=\parindent \small{INVITATORY}
\begin{center}
\textit{In Christ was life.\\}
\textit{-And that life was the light of manking.\\}
\end{center}

\hangindent=\parindent \small{READING}    Is 45:22-23 \textbf{   Turn to me and be safe, all you ends of the earth, for I am God; there is no other! By myself I swear, uttering my just decree, a word that will not return: to me every knee shall bend; by me every tongue shall swear, saying, “Only in the LORD are just deeds and power. Before him in shame shall come all who vent their anger against him.\\}

\hangindent=\parindent \small{BENEDICTUS 	Christ our God, in whom the fullness of the Godhead dwells, took upon himself our wounded nature and became the first new man, alleluia.\\}
(Friday after the Epiphany)
All who once reviled you will come and bow down in worship before your very footprints.

\hangindent=\parindent \small{PRAYER 	Grant us, almighty God, that the bringer of your salvation, who for the world's redemption came forth with newness of heavenly light, may dawn afresh in our hearts and bring us constant renewal. Who lives and reigns with you in the unity of the Holy Spirit, one God, for ever and ever.}

\begin{flushleft}\normalsize SEXT\\\end{flushleft}
\hangindent=\parindent \small{READING}    Jer 31:11-12 \textbf{   The LORD shall ransom Jacob, he shall redeem him from a hand too strong for him. Shouting, they shall mount the heights of Zion, they shall come streaming to the LORD’s blessings: the grain, the wine, and the oil, flocks of sheep and cattle; they themselves shall be like watered gardens, never again neglected.}
All the ends of the earth, alleluia.
-Have seen the saving power of God, alleluia.

\begin{flushleft}\normalsize VESPERS\\\end{flushleft}
\hangindent=\parindent \small{\uppercase{HYMN} p.  ?\\}
\hangindent=\parindent \small{READING}    Rom 8:3-4 \textbf{   For what the law, weakened by the flesh, was powerless to do, this God has done: by sending his own Son in the likeness of sinful flesh and for the sake of sin, he condemned sin in the flesh, so that the righteous decree of the law might be fulfilled in us, who live not according to the flesh but according to the spirit.\\}

\hangindent=\parindent \small{MAGNIFICAT 	I have come forth from God into the world; I have not come of myself, but the Father sent me.\\}
(Friday after the Epiphany)
An angel warned the wise men in a dream to return to their own country by a different route.

\begin{center}
\normalsize THURSDAY
\end{center}

\begin{flushleft}\normalsize LAUDS\\\end{flushleft}
\hangindent=\parindent \small{INVITATORY}
\begin{center}
\textit{Christ is the true light.\\}
\textit{-He gives light to all people.\\}
\end{center}

\hangindent=\parindent \small{READING}    Wis 7:26-27 \textbf{   For she is the reflection of eternal light, the spotless mirror of the power of God, the image of his goodness. Although she is one, she can do all things, and she renews everything while herself perduring; passing into holy souls from age to age, she produces friends of God and prophet.\\}

\hangindent=\parindent \small{BENEDICTUS 	The Lord God has come to his people and set them free.\\}

\hangindent=\parindent \small{PRAYER 	}

\begin{flushleft}\normalsize SEXT\\\end{flushleft}
\hangindent=\parindent \small{READING}    Ez 34:11-12 \textbf{   For thus says the Lord GOD: Look! I myself will search for my sheep and examine them. As a shepherd examines his flock while he himself is among his scattered sheep, so will I examine my sheep. I will deliver them from every place where they were scattered on the day of dark clouds.}
All the ends of the earth, alleluia.
-Have seen the saving power of God, alleluia.

\begin{flushleft}\normalsize VESPERS\\\end{flushleft}
\hangindent=\parindent \small{\uppercase{HYMN} p.  ?\\}
\hangindent=\parindent \small{READING}    1 Jn 5:20 \textbf{   We also know that the Son of God has come and has given us discernment to know the one who is true. And we are in the one who is true, in his Son Jesus Christ. He is the true God and eternal life.\\}

\hangindent=\parindent \small{MAGNIFICAT 	We have found Jesus of Nazareth, the son of Joseph. He is the one of whom Moses and the prophets wrote.\\}

\begin{center}
\normalsize FRIDAY
\end{center}

Invitatory from Monday
\begin{flushleft}\normalsize LAUDS\\\end{flushleft}
\hangindent=\parindent \small{READING}    Is 61:1-2a \textbf{   The spirit of the Lord GOD is upon me, because the LORD has anointed me; He has sent me to bring good news to the afflicted, to bind up the brokenhearted, to proclaim liberty to the captives, release to the prisoners, to announce a year of favor from the LORD and a day of vindication by our God.\\}

\hangindent=\parindent \small{BENEDICTUS 	He came through blood and water, Jesus Christ our Lord.\\}

\hangindent=\parindent \small{PRAYER 	}

\begin{flushleft}\normalsize SEXT\\\end{flushleft}
\hangindent=\parindent \small{READING}    Is 42:1 \textbf{   Here is my servant whom I uphold, my chosen one with whom I am pleased. Upon him I have put my spirit; he shall bring forth justice to the nations.}
All the ends of the earth, alleluia.
-Have seen the saving power of God, alleluia.

\begin{flushleft}\normalsize VESPERS\\\end{flushleft}
\hangindent=\parindent \small{\uppercase{HYMN} p.  ?\\}
\hangindent=\parindent \small{READING}    Acts 10:37-38 \textbf{   What has happened all over Judea, beginning in Galilee after the baptism that John preached, how God anointed Jesus of Nazareth with the holy Spirit and power. He went about doing good and healing all those oppressed by the devil, for God was with him.\\}

\hangindent=\parindent \small{MAGNIFICAT 	From heaven the Father's voice proclaimed: You are my Son, my beloved, in whom I take delight.\\}

\begin{center}
\normalsize SATURDAY
\end{center}
\begin{flushleft}\normalsize LAUDS\\\end{flushleft}
\hangindent=\parindent \small{INVITATORY}
\begin{center}
\textit{In these last days God has spoken to us through his Son.\\}
\textit{-The Word through whom he made all things.\\}
\end{center}

\hangindent=\parindent \small{READING}    Is 9:5 \textbf{   For a child is born to us, a son is given to us; upon his shoulder dominion rests. They name him Wonder-Counselor, God-Hero, Father-Forever, Prince of Peace.\\}

\hangindent=\parindent \small{BENEDICTUS 	He is the one of whom it has been written: Christ is born in Israel; his kingdom will last for ever.\\}

\hangindent=\parindent \small{PRAYER 	}

\begin{flushleft}\normalsize SEXT\\\end{flushleft}
\hangindent=\parindent \small{READING}    Is 12:5-6 \textbf{   Sing praise to the LORD for he has done glorious things; let this be known throughout all the earth. Shout with exultation, City of Zion, for great in your midst is the Holy One of Israel!}
All the ends of the earth, alleluia.
-Have seen the saving power of God, alleluia.
-----
THE EPIPHANY OF THE LORD
JANUARY 6 OR THE SUNDAY BETWEEN JANUARY 2 AND JANUARY 8
SOLEMNITY

\begin{flushleft}\normalsize FIRST VESPERS\\\end{flushleft}

Hymn
\begin{cverse}
All you who seek the Christ,\\
Lift your eyes on high and look,\\
For a heavenly sign has been raised for you,\\
And you will see His eternal glory.\\!

A star more radiant than the sun,\\
A light that surpasses all brilliance,\\
A message of great joy,\\
God descends in mortal flesh.\\!

The divine star shines for ever.\\
Light which will never grow dim;\\
It has pierced the darkness,\\
And the darkness cannot overcome it.\\!

The Wise Men have seen the rising star,\\
Eyes fixed toward heaven, they follow its path;\\
They come to the child of threefold destiny,\\
They offer gold, incense and myrrh.\\!

Gold heralds the King, incense proclaims the God,\\
And myrrh foretells the tomb,\\
Where God, letting His body be laid,\\
Will arise, smashing the gates of death.\\!

Glory to You, Holy Trinity,\\
Father, Son and Holy Spirit\\
Light made manifest to man,\\
Which shines for all ages. Amen.\\!
\end{cverse}
-Prudence, 5th century ?

\hangindent=\parindent \small{PSALMODY}
\begin{center}
\begin{tabular}{ l l }
Ps 134 &  - Ps 97 - Ps 71 - NT 7\\
\end{tabular}
\end{center}		

\hangindent=\parindent \small{READING}    2 Tim 1:9-10 \textbf{   He saved us and called us to a holy life, not according to our works but according to his own design and the grace bestowed on us in Christ Jesus before time began, but now made manifest through the appearance of our savior Christ Jesus, who destroyed death and brought life and immortality to light through the gospel.\\}

\hangindent=\parindent \small{MAGNIFICAT 	Seeing the star, the wise men said: This must signify the birth of some great king. Let us search for him and lay our treasures at his feet: gold, frankincense and myrrh.\\}

\hangindent=\parindent \small{PRAYER 	May the splendor of your majesty, O Lord, we pray, shed its light upon our hearts, that we may pass through the shadows of this world and reach the brightness of our eternal home. Through our Lord Jesus Christ, your Son, who lives and reigns with you in the unity of the Holy  Spirit, one God, for ever and ever.}

\begin{flushleft}\normalsize VIGILS\\\end{flushleft}
\hangindent=\parindent \small{PSALMODY}
\begin{center}
\begin{tabular}{ l l }
Ps 66 &  - Ps 95 - Ps 96 - OT 18 - OT 4 - OT 20\\
\end{tabular}
\end{center}		

\begin{flushleft}\normalsize LAUDS\\\end{flushleft}
\hangindent=\parindent \small{INVITATORY}
\begin{center}
\textit{Christ has appeared to us; come, let us adore him.\\}
\textit{PSALMODY\\}
\textit{Ps 23 - Ps 99 - OT 6 - Ps 148 - Ps 150\\}
\end{center}

\hangindent=\parindent \small{READING}    Is 52:7-10 \textbf{    How beautiful upon the mountains are the feet of the one bringing good news, announcing peace, bearing good news, announcing salvation, saying to Zion, “Your God is King!” Listen! Your sentinels raise a cry, together they shout for joy, for they see directly, before their eyes, the LORD’s return to Zion. Break out together in song, O ruins of Jerusalem! For the LORD has comforted his people, has redeemed Jerusalem. The LORD has bared his holy arm in the sight of all the nations; all the ends of the earth can see the salvation of our God.\\}

\hangindent=\parindent \small{BENEDICTUS 	Today the Bridegroom claims his bride, the Church, since Christ has washed her sins away in Jordan's waters; the Magi hasten with their gifts to the royal wedding; and the wedding guests rejoice, for Christ has changed water into wine, alleluia.\\}

\begin{flushleft}\normalsize SEXT\\\end{flushleft}
\hangindent=\parindent \small{PSALMODY}
\begin{center}
\begin{tabular}{ l l }
Ps 46 &  - Ps 85\\
\end{tabular}
\end{center}		

\hangindent=\parindent \small{READING}    Is 49:6 \textbf{    It is too little, he says, for you to be my servant, to raise up the tribes of Jacob, and restore the survivors of Israel; I will make you a light to the nations, that my salvation may reach to the ends of the earth.}
All nations will see the glory of your holy One.
-All the kings of the earth will acknowledge your majesty.

\begin{flushleft}\normalsize SECOND VESPERS\\\end{flushleft}

HYMN of First Vespers p. ?
\hangindent=\parindent \small{PSALMODY}
\begin{center}
\begin{tabular}{ l l }
Ps 109 &  - Ps 137 - Ps 44 - NT 11\\
\end{tabular}
\end{center}		

\hangindent=\parindent \small{READING}    Tit 3:4-5 \textbf{    But when the kindness and generous love of God our savior appeared, not because of any righteous deeds we had done but because of his mercy, he saved us through the bath of rebirth and renewal by the holy Spirit.\\}

\hangindent=\parindent \small{MAGNIFICAT 	Three mysteries mark this holy day: today the star leads the Magi to the infant Christ; today water is changed into wine for the wedding feast; today Christ will to be baptized by John in the river Jordan to bring us salvation.\\}
-----
WEEK AFTER THE EPIPHANY TO THE BAPTISM OF THE LORD
- PSALMODY Week II
\begin{flushleft}\normalsize - HYMNS for VESPERS\\\end{flushleft} taken from the Epiphany or from the Christmas Season pg's: ?

\begin{center}
\normalsize MONDAY
\end{center}

\begin{flushleft}\normalsize LAUDS\\\end{flushleft}
\hangindent=\parindent \small{INVITATORY}
\begin{center}
\textit{The heavens proclaim the justice of God.\\}
\textit{-All nations shall see his glory.\\}
\end{center}

\hangindent=\parindent \small{READING}    Is 9:5 \textbf{    For a child is born to us, a son is given to us; upon his shoulder dominion rests. They name him Wonder-Counselor, God-Hero, Father-Forever, Prince of Peace.\\}

\hangindent=\parindent \small{BENEDICTUS 	The wise men came from the East to adore the Lord in Bethlehem. Opening their treasures, they offered him three precious gifts: gold for the great King, frankincense for the true God, and myrrh for his burial, alleluia.\\}

\hangindent=\parindent \small{PRAYER 	O God, whose eternal Word adorns the face of the heavens yet accepted from the Virgin Mary the frailty of our flesh, grant, we pray, that he who appeared among us as the splendor of truth may go forth in the fullness of power for the redemption of the world. Who lives and reigns with you in the unity of the Holy Spirit, one God, for ever and ever.}

\begin{flushleft}\normalsize SEXT\\\end{flushleft}
\hangindent=\parindent \small{READING}    Is 12:5-6 \textbf{   Sing praise to the LORD for he has done glorious things; let this be known throughout all the earth. Shout with exultation, City of Zion, for great in your midst is the Holy One of Israel!}
All nations will see the glory of your holy One.
-All the kings of the earth will acknowledge your majesty.

\begin{flushleft}\normalsize VESPERS\\\end{flushleft}
\hangindent=\parindent \small{READING}   2 Pet 1:3-4 \textbf{  His divine power has bestowed on us everything that makes for life and devotion, through the knowledge of him who called us by his own glory and power. Through these, he has bestowed on us the precious and very great promises, so that through them you may come to share in the divine nature, after escaping from the corruption that is in the world because of evil desire.\\}

\hangindent=\parindent \small{MAGNIFICAT 	When they saw the star the Magi were filled with great joy; entering the house, they offered their gifts to the Lord: gold, frankincense and myrrh.\\}

\begin{center}
\normalsize TUESDAY
\end{center}

\begin{flushleft}\normalsize LAUDS\\\end{flushleft}
\hangindent=\parindent \small{INVITATORY:}
\begin{center}
\textit{Praise the Lord, Jerusalem.\\}
\textit{-He sends forth his word to give life to the earth.\\}
\end{center}

\hangindent=\parindent \small{READING}   Is 4:2-3 \textbf{  On that day, the branch of the LORD will be beauty and glory, and the fruit of the land will be honor and splendor for the survivors of Israel. Everyone who remains in Zion, everyone left in Jerusalem will be called holy: everyone inscribed for life in Jerusalem.\\}

\hangindent=\parindent \small{BENEDICTUS 	The wise men offered gifts of gold, frankincense, and myrrh to the Lord, the Son of God and King most high, alleluia.\\}

\hangindent=\parindent \small{PRAYER 	O God, whose Only Begotten Son has appeared in our very flesh, grant, we pray, that we, who have been taken up into this new creation, may be freed from the ancient taint of sin. Through our Lord Jesus Christ, your Son, who lives and reigns with you in the unity of the Holy Spirit, one God, for ever and ever.}

\begin{flushleft}\normalsize SEXT\\\end{flushleft}
\hangindent=\parindent \small{READING}   Is 48:20 \textbf{  Go forth from Babylon, flee from Chaldea! With shouts of joy declare this, announce it; make it known to the ends of the earth, say: “The LORD has redeemed his servant Jacob.}
All nations will see the glory of your holy One.
-All the kings of the earth will acknowledge your majesty.

\begin{flushleft}\normalsize VESPERS\\\end{flushleft}
\hangindent=\parindent \small{READING}   Eph 2:3b-5 \textbf{  We were by nature children of wrath, like the rest. But God, who is rich in mercy, because of the great love he had for us, even when we were dead in our transgressions, brought us to life with Christ (by grace you have been saved).\\}

\hangindent=\parindent \small{MAGNIFICAT 	Christ, you are Light from Light; when you appeared on the earth, the wise men offered their gifts to you, alleluia.\\}

\begin{center}
\normalsize WEDNESDAY
\end{center}

\begin{flushleft}\normalsize LAUDS\\\end{flushleft}
\hangindent=\parindent \small{INVITATORY}
\begin{center}
\textit{The Lord will teach us his way.\\}
\textit{-And we will follow in his footsteps.\\}
\end{center}

\hangindent=\parindent \small{READING}   Is 49:8-9 \textbf{  Thus says the LORD: in a time of favor I answer you, on the day of salvation I help you; I form you and set you as a covenant for the people, to restore the land and allot the devastated heritages, to say to the prisoners: Come out! To those in darkness: Show yourselves! Along the roadways they shall find pasture, on every barren height shall their pastures be.\\}

\hangindent=\parindent \small{BENEDICTUS 	We have seen his star in the East and have come with gifts to worship the Lord.\\}

\hangindent=\parindent \small{PRAYER 	O God, who bestow light on all the nations, grant your peoples the gladness of lasting peace and pour into our hearts that brilliant light by which you purified the minds of our fathers in faith. Through our Lord Jesus Christ, your Son, who lives and reigns with you in the unity of the Holy Spirit, one God, for ever and ever.}

\begin{flushleft}\normalsize SEXT\\\end{flushleft}
\hangindent=\parindent \small{READING}   Rev 21:23-24 \textbf{  The city had no need of sun or moon to shine on it, for the glory of God gave it light, and its lamp was the Lamb. The nations will walk by its light, and to it the kings of the earth will bring their treasure.}
All nations will see the glory of your holy One.
-All the kings of the earth will acknowledge your majesty.

\begin{flushleft}\normalsize VESPERS\\\end{flushleft}
\hangindent=\parindent \small{READING}   Col 1:13-15 \textbf{  He delivered us from the power of darkness and transferred us to the kingdom of his beloved Son, in whom we have redemption, the forgiveness of sins. He is the image of the invisible God, the firstborn of all creation.\\}

\hangindent=\parindent \small{MAGNIFICAT 	Herod questioned the Magi: What is this sign of which you speak, this sign of a newborn king? We saw a brilliant star in the heavens; its splendor filled the world.\\}

\begin{center}
\normalsize THURSDAY
\end{center}

\begin{flushleft}\normalsize LAUDS\\\end{flushleft}
\hangindent=\parindent \small{INVITATORY}
\begin{center}
\textit{The Son of God has come o give us understanding.\\}
\textit{-That we might know the true God.\\}
\end{center}

\hangindent=\parindent \small{READING}    Is 62:11-12 \textbf{   The LORD has proclaimed to the ends of the earth: say to daughter Zion, “See, your savior comes! See, his reward is with him, his recompense before him.” They shall be called “The Holy People,” “The Redeemed of the LORD.” And you shall be called “Cared For,” “A City Not Forsaken.”\\}

\hangindent=\parindent \small{BENEDICTUS 	All peoples, bearing gifts, will come from afar, alleluia.\\}

\hangindent=\parindent \small{PRAYER 	O God, who through your Son raised up your eternal light for all nations, grant that your people may come to acknowledge the full splendor of their Redeemer, that, bathed ever more in his radiance, they may reach everlasting glory. Through our Lord Jesus Christ, your Son, who lives and reigns with you in the unity of the Holy Spirit, one God, for ever and ever.}

\begin{flushleft}\normalsize SEXT\\\end{flushleft}
\hangindent=\parindent \small{READING}   Is 9:1 \textbf{  The people who walked in darkness have seen a great light; upon those who lived in a land of gloom a light has shone.}
All nations will see the glory of your holy One.
-All the kings of the earth will acknowledge your majesty.

\begin{flushleft}\normalsize VESPERS\\\end{flushleft}
\hangindent=\parindent \small{READING}   1 Jn 1:5b, 7 \textbf{   God is light, and in him there is no darkness at all. But if we walk in the light as he is in the light, then we have fellowship with one another, and the blood of his Son Jesus cleanses us from all sin\\}

\hangindent=\parindent \small{MAGNIFICAT 	The people of Saba shall come bringing gold, frankincense and myrrh, alleluia.\\}

\begin{center}
\normalsize FRIDAY
\end{center}

\begin{flushleft}\normalsize LAUDS\\\end{flushleft}
\hangindent=\parindent \small{INVITATORY:}
\begin{center}
\textit{In Christ was life.\\}
\textit{-And that life was the light of mankind.\\}
\end{center}

\hangindent=\parindent \small{READING}   Is 45:22-23 \textbf{  Turn to me and be safe, all you ends of the earth, for I am God; there is no other! By myself I swear, uttering my just decree, a word that will not return: to me every knee shall bend; by me every tongue shall swear.\\}

\hangindent=\parindent \small{BENEDICTUS 	All who once reviled you will come and bow down in worship before your very footprints.\\}

\hangindent=\parindent \small{PRAYER 	Grant, we ask, almighty God, that the Nativity of the Savior of the world, made known by the guidance of a star, may be revealed ever more fully to our minds. Through our Lord Jesus Christ, your Son, who lives and reigns with you in the unity of the Holy Spirit, one God, for ever and ever.}

\begin{flushleft}\normalsize SEXT\\\end{flushleft}
\hangindent=\parindent \small{READING}   Jer 31:11-12 \textbf{  The LORD shall ransom Jacob, he shall redeem him from a hand too strong for him. Shouting, they shall mount the heights of Zion, they shall come streaming to the LORD’s blessings: the grain, the wine, and the oil, flocks of sheep and cattle; they themselves shall be like watered gardens, never again neglected.}
All nations will see the glory of your holy One.
-All the kings of the earth will acknowledge your majesty.

\begin{flushleft}\normalsize VESPERS\\\end{flushleft}
\hangindent=\parindent \small{READING}   Rom 8:3-4 \textbf{  For what the law, weakened by the flesh, was powerless to do, this God has done: by sending his own Son in the likeness of sinful flesh and for the sake of sin, he condemned sin in the flesh, so that the righteous decree of the law might be fulfilled in us, who live not according to the flesh but according to the spirit.\\}

\hangindent=\parindent \small{MAGNIFICAT 	An angel warned the wise men in a dream to return to their own country by a different route.\\}

\begin{center}
\normalsize SATURDAY
\end{center}

\begin{flushleft}\normalsize LAUDS\\\end{flushleft}
\hangindent=\parindent \small{INVITATORY:}
\begin{center}
\textit{Christ is the true light.\\}
\textit{-He gives light to all people.\\}
\end{center}

\hangindent=\parindent \small{READING}   Wis 7:26-27 \textbf{  For she is the reflection of eternal light, the spotless mirror of the power of God, the image of his goodness. Although she is one, she can do all things, and she renews everything while herself perduring; passing into holy souls from age to age, she produces friends of God and prophets.\\}

\hangindent=\parindent \small{BENEDICTUS 	At Cana in Galilee Jesus worked the first of the signs which revealed his glory.\\}

\hangindent=\parindent \small{PRAYER 	Almighty ever-living God, who through your Only Begotten Son have made us a new creation for yourself, grant, we pray, that by your grace we may be found in the likeness of him, in whom our nature is united to you. Who lives and reigns with you in the unity of the Holy Spirit, one God, for ever and ever.}

\begin{flushleft}\normalsize SEXT\\\end{flushleft}
\hangindent=\parindent \small{READING}   Ez 34:11-12 \textbf{  For thus says the Lord GOD: Look! I myself will search for my sheep and examine them. As a shepherd examines his flock while he himself is among his scattered sheep, so will I examine my sheep. I will deliver them from every place where they were scattered on the day of dark clouds.}
All nations will see the glory of your holy One.
-All the kings of the earth will acknowledge your majesty.
-----
THE BAPTISM OF THE LORD
FEAST

\begin{flushleft}\normalsize FIRST VESPERS\\\end{flushleft}

