\begin{center}\normalsize CHRISTMAS\\
\footnotesize December 25\\
\footnotesize SOLEMNITY\\
\end{center}

\begin{flushleft}\normalsize FIRST VESPERS\\\end{flushleft}

\hangindent=\parindent \small{\uppercase{HYMN} p. \pageref{christmas:firstHymn}-\pageref{christmas:lastHymn}\\}

\hangindent=\parindent \small{PSALMODY:}\\
\hangindent=\parindent  PS 112 -- PS 147 -- PS 8 -- NT 5\vspace{0.5em}

\hangindent=\parindent \small{\uppercase{READING}}    Gal 4:4-5 \textbf{   But when the fullness of time had come, God sent his Son, born of a woman, born under the law, to ransom those under the law, so that we might receive adoption.\\}

\hangindent=\parindent \small{MAGNIFICAT 	When the sun rises in the morning sky, you will see the King of kings coming forth from the Father like a radiant bridegroom from the bridal chamber.\\}

\hangindent=\parindent \small{PRAYER 	O God, who gladden us year by year as we wait in hope for our redemption, grant that, just as we joyfully welcome your Only Begotten Son as our Redeemer, we may also merit to face him confidently when he comes again as our Judge. Who lives and reigns with you in the unity of the Holy Spirit, one God, for ever and ever.}

\begin{flushleft}\normalsize VIGILS\\\end{flushleft}

\hangindent=\parindent \small{PSALMODY:}\\
\hangindent=\parindent  PS 2 -- PS 18 -- PS 44 -- OT 20 -- OT 24 -- OT 32\vspace{0.5em}

\hangindent=\parindent \small{PRAYER 	O God, who wonderfully created the dignity of human nature and still more wonderfully restored it, grant, we pray, that we may share in the divinity of Christ, who humbled himself to share in our humanity. Who lives and reigns with you in the unity of the Holy Spirit, one God, for ever and ever.}

\begin{flushleft}\normalsize LAUDS\\\end{flushleft}

\hangindent=\parindent \small{INVITATORY}
\begin{center}
\textit{Christ is born for us; come, let us adore him.\\}
\end{center}

\hangindent=\parindent \small{PSALMODY:}\\
\hangindent=\parindent  PS 62 -- OT 41 -- PS 148 -- PS 149 -- PS 150 (Per.) \vspace{0.5em}

\hangindent=\parindent \small{\uppercase{READING}}    Heb 1:1-2 \textbf{   In times past, God spoke in partial and various ways to our ancestors through the prophets; in these last days, he spoke to us through a son, whom he made heir of all things and through whom he created the universe.\\}

\hangindent=\parindent \small{BENEDICTUS 	Glory to God in the highest, and peace to his people on earth, alleluia.\\}

\hangindent=\parindent \small{PRAYER 	Grant, we pray, almighty God, that, as we are bathed in the new radiance of your incarnate Word, the light of faith, which illumines our minds, may also shine through in our deeds. Through our Lord Jesus Christ, your Son, who lives and reigns with you in the unity of the Holy Spirit, one God, for ever and ever.}

\begin{flushleft}\normalsize SEXT\\\end{flushleft}

\hangindent=\parindent \small{PSALMODY:}\\
\hangindent=\parindent  PS 86 -- PS 95\vspace{0.5em}

\hangindent=\parindent \small{\uppercase{READING}}    1 Jn 4:9 \textbf{    In this way the love of God was revealed to us: God sent his only Son into the world so that we might have life through him.\\}

\begin{center}
\textit{All the ends of the earth, alleluia.\\
-Have seen the saving power of God, alleluia.}
\end{center}

(use prayer of Second Vespers)

\begin{flushleft}\normalsize SECOND VESPERS\\\end{flushleft}

\hangindent=\parindent \small{\uppercase{HYMN} p. \pageref{christmas:firstHymn}-\pageref{christmas:lastHymn}\\}

\hangindent=\parindent \small{PSALMODY:}\\
\hangindent=\parindent  PS 109 -- PS 129 -- PS 84 -- NT 6\vspace{0.5em}

\hangindent=\parindent \small{\uppercase{READING}}    1 Jn 1:1-3 \textbf{   What was from the beginning, what we have heard, what we have seen with our eyes, what we looked upon and touched with our hands concerns the Word of life for the life was made visible; we have seen it and testify to it and proclaim to you the eternal life that was with the Father and was made visible to us what we have seen and heard we proclaim now to you, so that you too may have fellowship with us; for our fellowship is with the Father and with his Son, Jesus Christ.\\}

\hangindent=\parindent \small{MAGNIFICAT 	Christ the Lord is born today; today, the Savior has appeared. Earth echoes songs of angel choirs, archangels' joyful praise. Today on earth his friends exult: Glory to God in the highest, alleluia.\\}

\hangindent=\parindent \small{PRAYER 	O God, who wonderfully created the dignity of human nature and still more wonderfully restored it, grant, we pray, that we may share in the divinity of Christ, who humbled himself to share in our humanity. Who lives and reigns with you in the unity of the Holy Spirit, one God, for ever and ever.}
