\begin{center}\normalsize DECEMBER 31\\
\footnotesize 7th day in the octave of Christmas\\
\end{center}

\begin{flushleft}\normalsize LAUDS\\\end{flushleft}

\hangindent=\parindent \small{READING}    Is 4:2-3 \textbf{   On that day, the branch of the LORD will be beauty and glory, and the fruit of the land will be honor and splendor for the survivors of Israel. Everyone who remains in Zion, everyone left in Jerusalem will be called holy: everyone inscribed for life in Jerusalem.\\}

\hangindent=\parindent \small BENEDICTUS
\begin{description}[labelindent=\parindent, noitemsep, leftmargin=*]
\item [(before the Epiphany):]   Suddenly there was with the angel a great company of the heavenly host, praising God and singing: Glory to God in the highest and peace to his people on earth, alleluia.
\item [(Tuesday after the Epiphany):]  The wise men offered gifts of gold, frankincense and myrrh to the Lord, the Son of God and King most high, alleluia.
\end{description}

\hangindent=\parindent \small{PRAYER  Almighty ever-living God, who in the Nativity of your Son established the beginning and fulfillment of all religion, grant, we pray, that we may be numbered among those who belong to him, in whom is the fullness of human salvation. Who lives and reigns with you in the unity of the Holy Spirit, one God, for ever and ever.}

\begin{flushleft}\normalsize SEXT\\\end{flushleft}

\hangindent=\parindent \small{READING}    Is 48:20 \textbf{   Go forth from Babylon, flee from Chaldea! With shouts of joy declare this, announce it; make it known to the ends of the earth, say: “The LORD has redeemed his servant Jacob.}

\begin{center}
\textit{All the ends of the earth, alleluia.\\
-Have seen the saving power of God, alleluia.}
\end{center}

