\begin{center}\normalsize DECEMBER 30\\
\footnotesize 6th day in the Octave of Christmas\\
\end{center}

\hangindent=\parindent \small{INVITATORY}
\begin{center}
\textit{Christ is born for us; come, let us adore him.\\}
\end{center}

\begin{flushleft}\normalsize LAUDS\\\end{flushleft}

\hangindent=\parindent \small{READING}    Is 9:6 \textbf{   His dominion is vast and forever peaceful, upon David’s throne, and over his kingdom, which he confirms and sustains by judgment and justice, both now and forever. The zeal of the LORD of hosts will do this!\\}

\hangindent=\parindent \small BENEDICTUS
\begin{description}[labelindent=\parindent, noitemsep, leftmargin=*]
\item [(before Epiphany):]  At the Lord's birth the choirs of angels sang: Blessed be our God enthroned as King and blessed be the Lamb.
\item [(Monday after Epiphany):]  The wise men came from the East to adore the Lord in Bethlehem. Opening their treasures, they offered him three precious gifts: gold for the great King, frankincense for the true God, and myrrh for his burial, alleluia.
\end{description}


\hangindent=\parindent \small{PRAYER  Grant, we pray, almighty God, that the newness of the Nativity in the flesh of your Only Begotten Son may set us free, for ancient servitude holds us bound beneath the yoke of sin. Through our Lord Jesus Christ, your Son, who lives and reigns with you in the unity of the Holy Spirit, one God, for ever and ever.}

\begin{flushleft}\normalsize SEXT\\\end{flushleft}

\hangindent=\parindent \small{READING}    Is 12:5-6 \textbf{   Sing praise to the LORD for he has done glorious things; let this be known throughout all the earth. Shout with exultation, City of Zion, for great in your midst is the Holy One of Israel!}

\begin{center}
\textit{All the ends of the earth, alleluia.\\
-Have seen the saving power of God, alleluia.}
\end{center}

\begin{flushleft}\normalsize VESPERS\\\end{flushleft}

\hangindent=\parindent \small{\uppercase{HYMN} p.  \pageref{christmas:firstHymn} - \pageref{christmas:lastHymn}\\}

\hangindent=\parindent \small{READING}    2 Pet 1:3-4 \textbf{   His divine power has bestowed on us everything that makes for life and devotion, through the knowledge of him who called us by his own glory and power. Through these, he has bestowed on us the precious and very great promises, so that through them you may come to share in the divine nature, after escaping from the corruption that is in the world because of evil desire.\\}

\hangindent=\parindent \small MAGNIFICAT
\begin{description}[labelindent=\parindent, noitemsep, leftmargin=*]
\item [(before the Epiphany):]  We sing your praises, holy Mother of God: you gave birth to our Savior, Jesus Christ; watch over all who honor you.
\item [(Monday after the Epiphany):]  When they saw the star the Magi were filled with great joy; entering the house, they offered their gifts to the Lord: gold, frankincense and myrrh.
\end{description}
