\begin{center}\normalsize HOLY FAMILY\\
\footnotesize Sunday in the Octave of Christmas*\\
\footnotesize FEAST\\
\end{center}

\begin{flushleft}\normalsize FIRST VESPERS\\\end{flushleft}

\hangindent=\parindent \small{\uppercase{HYMN} p. \pageref{christmas:firstHymn}-\pageref{christmas:lastHymn}\\}

\hangindent=\parindent \small{PSALMODY:}\\
\hangindent=\parindent  PS 112 -- PS 147 -- PS 8 -- NT 4\vspace{0.5em}


\hangindent=\parindent \small{\uppercase{READING}}    2 Cor 8:9 \textbf{   For you know the gracious act of our Lord Jesus Christ, that for your sake he became poor although he was rich, so that by his poverty you might become rich. \\}

\hangindent=\parindent \small{MAGNIFICAT 	The child Jesus remained in Jerusalem, and his parents did not know it. They thought he was in the group of travelers and looked for him among their relatives and friends.\\}

\hangindent=\parindent \small{PRAYER 	O God, who were please to give us the shining example of the Holy Family, graciously grant that we may imitate them in practicing the virtues of family life and in the bonds of charity, and so, in the joy of your house, delight one day in eternal rewards. Through our Lord Jesus Christ, your Son, who lives and reigns with you in the unity of the Holy Spirit, one God, for ever and ever.}

\begin{flushleft}\normalsize VIGILS\\\end{flushleft}

\hangindent=\parindent \small{PSALMODY:}\\
\hangindent=\parindent  PS 45 -- PS 86 -- PS 84 -- OT 18 -- OT 20 -- OT 32\vspace{0.5em}

\begin{flushleft}\normalsize LAUDS\\\end{flushleft}

\hangindent=\parindent \small{INVITATORY}
\begin{center}
\textit{Come, let us worship Christ, the Son of God,\\}
\textit{-Who was obedient to Mary and Joseph.\\}
\end{center}

\hangindent=\parindent \small{PSALMODY:}\\
\hangindent=\parindent  PS 62 -- PS 23 -- OT 41 -- PS 149 -- PS 150 (mode 7)\vspace{0.5em}

\hangindent=\parindent \small{\uppercase{READING}}    Dt 5:16 \textbf{   Honor your father and your mother, as the LORD, your God, has commanded you, that you may have a long life and that you may prosper in the land the LORD your God is giving you. \\}

\hangindent=\parindent \small{BENEDICTUS 	Lord, give us light through the example of your family and guide our feet into the way of peace.\\}

\begin{flushleft}\normalsize SEXT\\\end{flushleft}

\hangindent=\parindent \small{PSALMODY:}\\
\hangindent=\parindent  PS 117 -- PS 118 XIII--XIV\vspace{0.5em}

\hangindent=\parindent \small{\uppercase{READING}}    Col 3:14-15 \textbf{   And over all these put on love, that is, the bond of perfection. And let the peace of Christ control your hearts, the peace into which you were also called in one body. And be thankful.\\}

\begin{center}
\textit{I am a poor man. I have worked since my youth.\\
-I was raised up only to be brought low and left bewildered.}
\end{center}

\begin{flushleft}\normalsize SECOND VESPERS\\\end{flushleft}

\hangindent=\parindent \small{\uppercase{HYMN} p. \pageref{christmas:firstHymn}-\pageref{christmas:lastHymn}\\}

\hangindent=\parindent \small{PSALMODY:}\\
\hangindent=\parindent  PS 126 -- PS 127 -- PS 44 -- NT 4\vspace{0.5em}

\hangindent=\parindent \small{\uppercase{READING}}    Phil 2:6-7 \textbf{   Who, though he was in the form of God, did not regard equality with God something to be grasped. Rather, he emptied himself, taking the form of a slave, coming in human likeness; and found human in appearance.\\}

\hangindent=\parindent \small{MAGNIFICAT 	Son, why have you done this to us? Think what anguish your father and I have endured looking for you. But why did you look for me? Did you know know that I had to be in my Father's house?\\}

For the Benedictus between the 26th and 29th, see The Proper of Saints
