\begin{center}\normalsize FRIDAYS\\
\footnotesize and December 23rd\\
\end{center}

\begin{flushleft}\normalsize LAUDS\\\end{flushleft}

\hangindent=\parindent \small{\uppercase{READING}} Jer 30:21,22 \textbf{His leader shall be one of his own, and his ruler shall emerge from his ranks. He shall approach me when I summon him; why else would he dare approach me?—oracle of the LORD. You shall be my people, and I will be your God.\\}

\hangindent=\parindent \small{BENEDICTUS  (December 23rd) All that God promised to the virgin through the message of the angel has been accomplished.\\}

\hangindent=\parindent \small PRAYER
\begin{description}[labelindent=\parindent, leftmargin=*]
\item [Week 1:]  Stir up your power, we pray, O Lord, and come, that with you to protect us, we may find rescue from the pressing dangers of our sins, and with you to set us free, we may be found worthy of salvation. Who live and reign with God the Father in the unity of the Holy Spirit, one God, for ever and ever.
\item [Week 2:]  Grant that your people, we pray, almighty God, may be ever watchful for the coming of your Only Begotten Son, that, as the author of our salvation himself has taught us, we may hasten, alert and with lighted lamps, to meet him when he comes. Who lives and reigns with you in the unity of the Holy Spirit, one God, for ever and ever.
\item [Week 3:]  May your grace, almighty God, always go before us and follow after, so that we, who await with heartfelt desire the coming of your Only Begotten Son, may receive your help both now and in the life to come. Through our Lord Jesus Christ, your Son, who lives and reigns with you in the unity of the Holy Spirit, one God, for ever and ever.
\item [December 23rd:]  Almighty ever-living God, as we see how the Nativity of your Son according to the flesh draws near, we pray that to us, your unworthy servants, mercy may flow from your Word, who chose to become flesh of the Virgin Mary and establish among us his dwelling, Jesus Christ our Lord. Who lives and reigns with you in the unity of the Holy Spirit, one God, for ever and ever.
\end{description}

\begin{flushleft}\normalsize SEXT\\\end{flushleft}

\hangindent=\parindent \small{\uppercase{READING}} Jer 30:18a \textbf{Thus says the LORD: See! I will restore the fortunes of Jacob’s tents, on his dwellings I will have compassion.\\}

\begin{center}
\textit{Remember us, Lord, because of the love you have for your people.\\
-Come and bring us your salvation.}
\end{center}

\begin{flushleft}\normalsize VESPERS\\\end{flushleft}

\hangindent=\parindent \small{\uppercase{HYMN} p. \pageref{advent:firstHymn}-\pageref{advent:lastHymn}\\}

\hangindent=\parindent \small{\uppercase{READING}} 2 Pet 3:8b-9 \textbf{With the Lord one day is like a thousand years and a thousand years like one day. The Lord does not delay his promise, as some regard “delay,” but he is patient with you, not wishing that any should perish but that all should come to repentance.\\}

\hangindent=\parindent \small{MAGNIFICAT  (December 23rd) O Emmanuel, king and lawgiver, desire of the nations, Savior of all people, come and set us free, Lord our God.\\}
