\begin{center}
\normalsize \begin{center}\normalsize SATURDAYS\\
\end{center}
\footnotesize and December 17th\\
\end{center}

\begin{flushleft}\normalsize LAUDS\\\end{flushleft}

\hangindent=\parindent \small{READING} Is 11:1-2 \textbf{But a shoot shall sprout from the stump of Jesse, and from his roots a bud shall blossom. The spirit of the LORD shall rest upon him: a spirit of wisdom and of understanding, a spirit of counsel and of strength, a spirit of knowledge and of fear of the LORD.\\}

\hangindent=\parindent \small PRAYER
\begin{description}[labelindent=\parindent, noitemsep, leftmargin=*]
\item [Week 1:]  O God, who sent your Only Begotten Son into this world to free the human race from its ancient enslavement, bestow on those who devoutly await him the grace of your compassion from on high, that we may attain the prize of true freedom. Through our Lord Jesus Christ, your Son, who lives and reigns with you in the unity of the Holy Spirit, one God, for ever and ever.
\item [Week 2:]  May the splendor of your glory dawn in our hearts, we pray, almighty God, that all shadows of the night may be scattered and we may be shown to be children of light by the advent of your Only Begotten Son. Who lives and reigns with you in the unity of the Holy Spirit, one God, for ever and ever.
\item [December 17th:]  O God, Creator and Redeemer of human nature, who willed that your Word should take flesh in an ever-virgin womb, look with favor on our prayers, that your Only Begotten Son, having taken to himself our humanity, may be pleased to grant us a share in his divinity. Who lives and reigns with you in the unity of the Holy Spirit, one God, for ever and ever.
\end{description}

\begin{flushleft}\normalsize SEXT\\\end{flushleft}

\hangindent=\parindent \small{READING} Is 4:3 \textbf{Everyone who remains in Zion, everyone left in Jerusalem will be called holy: everyone inscribed for life in Jerusalem.}

\begin{center}
\textit{Remember us, Lord, because of the love you have for your people.\\
-Come and bring us your salvation.}
\end{center}

