\begin{center}
\normalsize \begin{center}\normalsize THURSDAYS\\
\end{center}
\footnotesize and December 22nd\\
\end{center}

\begin{flushleft}\normalsize LAUDS\\\end{flushleft}

\hangindent=\parindent \small{READING} Is 45:8 \textbf{Let justice descend, you heavens, like dew from above, like gentle rain let the clouds drop it down. Let the earth open and salvation bud forth; let righteousness spring up with them! I, the LORD, have created this.\\}

\hangindent=\parindent \small{BENEDICTUS  (December 22nd) The moment that your greeting reached my ears, the child within my womb leapt for joy. \\}


\hangindent=\parindent \small PRAYER
\begin{description}[labelindent=\parindent, noitemsep, leftmargin=*]
\item [Week 1:]  Stir up your power, O Lord, and come to ur help with mighty strength, that what our sins impede the grace of your mercy may hasten. Through our Lord Jesus Christ, your Son, who lives and reigns with you in the unity of the Holy Spirit, one God, for ever and ever.
\item [Week 2:]  Stir up our hearts, O Lord, to make ready the paths of your Only Begotten Son, that through his coming, we may be found worthy to serve you with minds made pure. Through our Lord Jesus Christ, your Son, who lives and reigns with you in the unity of the Holy Spirit, one God, for ever and ever.
\item [Week 3:]  Unworthy servants that we are, O Lord, grieved by the guilt of our deeds, we pray that you may gladden us by the saving advent of your Only Begotten Son. Who lives and reigns with you in the unity of the Holy Spirit, one God, for ever and ever.
\item [December 22nd:]  O God, who, seeing the human race fallen into death, willed to redeem it by the coming of your Only Begotten Son, grant, we pray, that those who confess his Incarnation with humble fervor may merit his company as their Redeemer. Who lives and reigns with you in the unity of the Holy Spirit, one God, for ever and ever.
\end{description}

\begin{flushleft}\normalsize SEXT\\\end{flushleft}

\hangindent=\parindent \small{READING} Hag 2:6b,9 \textbf{In just a little while, I will shake the heavens and the earth, the sea and the dry land. Greater will be the glory of this house the latter more than the former—says the LORD of hosts; and in this place I will give you peace— oracle of the LORD of hosts.}

\begin{center}
\textit{Remember us, Lord, because of the love you have for your people.\\
-Come and bring us your salvation.}
\end{center}

\begin{flushleft}\normalsize VESPERS\\\end{flushleft}

\hangindent=\parindent \small{\uppercase{HYMN} p.  \pageref{advent:firstHymn}\\}

\hangindent=\parindent \small{READING} Jas 5:7-8,9b \textbf{Be patient, therefore, brothers, until the coming of the Lord. See how the farmer waits for the precious fruit of the earth, being patient with it until it receives the early and the late rains. You, too, must be patient. Make your hearts firm, because the coming of the Lord is at hand. Behold, the Judge is standing before the gates.\\}

\hangindent=\parindent \small{MAGNIFICAT  (December 22nd) O King of all the nations, the only joy of every human heart; O Keystone of the mighty arch of man, come and save the creature you fashioned from the dust.\\}
