\begin{center}\normalsize WEDNESDAYS\\
\footnotesize and December 21st\\
\end{center}

\begin{flushleft}\normalsize LAUDS\\\end{flushleft}

\hangindent=\parindent \small{\uppercase{READING}} Is 7:14b-15 \textbf{The young woman, pregnant and about to bear a son, shall name him Emmanuel. Curds and honey he will eat so that he may learn to reject evil and choose good.\\}

\hangindent=\parindent \small{BENEDICTUS  (December 21st) There is no need to be afraid; in five days our Lord will come to us.\\}

\hangindent=\parindent \small PRAYER
\begin{description}[labelindent=\parindent, leftmargin=*]
\item [Week 1:]  Prepare our hearts, we pray, O Lord our God, by your divine power, so that at the coming of Christ your Son we may be found worthy of the banquet of eternal life and merit to receive heavenly nourishment from his hands. Who lives and reigns with you in the unity of the Holy Spirit, one God, for ever and ever.
\item [Week 2:]  Almighty God, who command us to prepare the way of Christ the Lord, grant in your kindness, we pray, that no infirmity may weary us as we long for the comforting pressence of our heavenly physician. Who lives and reigns with you in the unity of the Holy Spirit, one God, for ever and ever.
\item [Week 3:]  Grant, we pray, almighty God, that the coming solemnity of your Son may bestow healing upon us in this present life and bring us the rewards of life eternal. Through our Lord Jesus Christ, your Son, who lives and reigns with you in the unity of the Holy Spirit, one God, for ever and ever.
\item [December 21st:]  Hear in kindness, O Lord, the prayers of your people, that those who rejoice at the coming of your Only Begotten Son in our flesh may, when at last he comes in glory, gain the reward of eternal life. Through our Lord Jesus Christ, your Son, who lives and reigns with you in the unity of the Holy Spirit, one God, for ever and ever.
\end{description}

\begin{flushleft}\normalsize SEXT\\\end{flushleft}

\hangindent=\parindent \small{\uppercase{READING}} Is 12:2 \textbf{God indeed is my salvation; I am confident and unafraid. For the LORD is my strength and my might, and he has been my salvation.\\}

\begin{center}
\textit{Remember us, Lord, because of the love you have for your people.\\
-Come and bring us your salvation.}
\end{center}

\begin{flushleft}\normalsize VESPERS\\\end{flushleft}

\hangindent=\parindent \small{\uppercase{HYMN} p. \pageref{advent:firstHymn}-\pageref{advent:lastHymn}\\}

\hangindent=\parindent \small{\uppercase{READING}} 1 Cor 4:5 \textbf{Therefore, do not make any judgment before the appointed time, until the Lord comes, for he will bring to light what is hidden in darkness and will manifest the motives of our hearts, and then everyone will receive praise from God.\\}

\hangindent=\parindent \small{MAGNIFICAT  (December 21st) O Radiant Dawn, splendor of eternal light, sun of justice: come, shine on those who dwell in darkness and the shadow of death.\\}
