\begin{center}\normalsize COMMON OF THE DEDICATION OF A CHURCH\\
\end{center}

\noindent\small{\uppercase{Hymn}}\normalsize\label{commons:dedication}
\begin{cverse}
Blessed city Jerusalem,\\
Called “vision of peace,”\\
Built in heaven with living stones,\\
Escorted by the angels as a bride by her companions.\\!

New city coming down from heaven\\
For the Wedding Feast of the Lamb,\\
Beautiful as a bride adorned for her husband;\\
The glory of God illuminates it and the Lamb is its lighted torch!\\!

Its gates gleam with pearls;\\
The sanctuary is open wide;\\
Their suff ering over, all those may enter\\
Who are oppressed on earth for Christ’s sake.\\!

With blows and polishing,\\
The stones are refi ned,\\
Enshrined, each one in their place, by the Jeweler’s hand,\\
And arranged to dwell in the Temple of the Lord.\\!

Honor, glory and power\\
Praise to the Most High God,\\
To the Father and to the Son and to the Spirit Counselor,\\
Blessed be God forevermore! Amen.\\!
\end{cverse}

\begin{flushleft}\normalsize FIRST VESPERS\\\end{flushleft}

\hangindent=\parindent \small{PSALMODY:}\\
\hangindent=\parindent \vspace{0.5em}
ps 83 ant OT - ps 146 ant Chr - ps 147 ant Adv - NT 12

\hangindent=\parindent \small{READING} Eph 2:19-22 \textbf{You are no longer strangers and sojourners, but you are fellow citizens with the saints and members of the household of God, built upon the foundation of the apostles and prophets, Christ Jesus himself being the cornerstone, in whom the whole structure is joined together and grows into a holy temple in the Lord; in whom you also are built into it for a dwelling place of God in the Spirit.\\}

\hangindent=\parindent \small{MAGNIFICAT \\}
All you who love Jerusalem, rejoice with her for ever (alleluia).

\hangindent=\parindent \small PRAYER 
\begin{description}[labelindent=\parindent, noitemsep, leftmargin=*]
\item [1:]  Father, each year we recall the dedication of this church to your service. Let our worship always be sincere, and help us to fi nd your saving love in this church. Grant this...
\item [2:]  Outside dedicated church: God our Father, from living stones, your chosen people, you built an eternal temple to your glory. Increase the spiritual gifts you have given to your Church that your faithful people may continue to grow into the new and eternal Jerusalem. We ask this...
\item [3:]  Father, you called your people to be your Church. As we gather together in your name, may we love, honor, and follow you to eternal life in the kingdom you promise. Grant this...
\end{description}

\begin{flushleft}\normalsize VIGILS\\\end{flushleft}

\hangindent=\parindent \small{PSALMODY:}\\
\hangindent=\parindent \vspace{0.5em}
ps 23 ant E - ps 86 ant Lent - ps 47 ant E - OT 6 ant E - OT 17 ant OT - OT 33

\begin{flushleft}\normalsize LAUDS\\\end{flushleft}

\hangindent=\parindent \small{INVITATORY}
\begin{center}
\textit{Come, let us worship Christ, the Bridegroom of his Church (alleluia) .\\}
\textit{Come, let us worship Christ, who has shown his love for the Church (alleluia).\\}
\end{center}

\hangindent=\parindent \small{PSALMODY:}\\
\hangindent=\parindent  \vspace{0.5em}
ps 62 ant Adv - ps 96 ant Lent - OT 15 ant Lent - ps 150 ant E

\hangindent=\parindent \small{READING} Is 56:7 \textbf{These I will bring to my holy mountain, and make them joyful in my house of prayer; their burnt off erings and their sacrifi ces will be accepted on my altar; for my house shall be called a house of prayer for all peoples.\\}

\hangindent=\parindent \small{BENEDICTUS \\}
Zacchaeus, hurry down, I mean to stay with you today.  He hurried down and welcomed Christ with joy, for this day salvation had come to his house (alleluia).

\begin{flushleft}\normalsize SEXT\\\end{flushleft}

\hangindent=\parindent \small{PSALMODY}
\begin{center}
\begin{tabular}{ l l }
For solemnities: &  ps 120 ant Adv - ps 124 ant OT - ps 126 ant E\\
\end{tabular}
\end{center}		

\hangindent=\parindent \small{READING} 1 Cor 3:16-17 \textbf{Do you not know that you are God’s temple and that God’s Spirit dwells in you? If any one destroys God’s temple, God will destroy him. For God’s temple is holy, and that temple you are.}

\begin{center}
\textit{Lord, I love the beauty of your house (alleluia).\\
- The place where your glory dwells (alleluia).}
\end{center}

\begin{flushleft}\normalsize SECOND VESPERS\\\end{flushleft}

\hangindent=\parindent \small{PSALMODY:}\\
\hangindent=\parindent \vspace{0.5em}
ps 64 ant Lent - ps 45 ant E - ps 121 ant OT - NT 12

\hangindent=\parindent \small{READING} Rev 21:2-3: 22.27 \textbf{I saw the holy city, new Jerusalem, coming down out of heaven from God, prepared as a bride adorned for her husband; and I heard a loud voice from the throne saying, “Behold, the dwelling of God is with men. He will dwell with them, and they shall be his people, and God himself will be with them.” And I saw no temple in the city, for its temple is the Lord God the Almighty and the Lamb. But nothing unclean shall enter it, nor any one who practices abomination or falsehood, but only those who are written in the Lamb’s book of life.  \\}

\hangindent=\parindent \small{MAGNIFICAT  This is God’s dwelling place and he has made it holy; here we call on his name, for Scripture says: There you will find me (alleluia).\\}
